### 2020-01-26 assignment_1/article.tex
🎉 Add placeholder LaTeX .tex file.

\documentclass[12pt]{article}
\usepackage{setspace}
\setstretch{1.5}
\usepackage{amsmath,amssymb, amsthm}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[hang, flushmargin]{footmisc}
\usepackage[colorlinks=true]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{footnotebackref}
\usepackage{url}
\usepackage{listings}
\usepackage[most]{tcolorbox}
\usepackage{inconsolata}
\usepackage[papersize={8.5in,11in}, margin=1in]{geometry}
\usepackage{float}
\usepackage{caption}
\usepackage{esint}
\usepackage{url}
\usepackage{enumitem}
\usepackage{subfig}
\usepackage{wasysym}
\newcommand{\inlinecode}{\texttt}
\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

\begin{document}

\title{\textbf{EECS 340: Assignment 1}}

\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Bobby) Chen, \inlinecode{zxc325}}
\date{Due on 01/27/2020, submitted on 01/26/2020 \\ EECS 340, Dr. Koyuturk}
\maketitle

\section{Problem 1}

\section{Problem 2}

\section{Problem 3}

% \section{References}
%
% \nocite{*}
% \raggedright
% \bibliography{references.bib}
% \bibliographystyle{plain}

\end{document}

### 2020-01-26 assignment_1/article.tex
✨ Add sketch answer to Problem 1.

@@
 \usepackage{setspace}
-\setstretch{1.5}
+\setstretch{1.1}
 \usepackage{amsmath,amssymb, amsthm}
@@
 
-\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Bobby) Chen, \inlinecode{zxc325}}
+\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Bobby) CHEN, \inlinecode{zxc325}}
 \date{Due on 01/27/2020, submitted on 01/26/2020 \\ EECS 340, Dr. Koyuturk}
@@
 \section{Problem 1}
+\subsection{(a)}
+Without loss of generality, assume $x > y$ for $x, y \in \mathbb{Z^+}$. The loop invariant is:
+
+\begin{gather}
+    Euclidean(x, y) = Euclidean(x - y, y)
+\end{gather}
+
+\subsection{(b)}
+Without loss of generality, assume $x > y$ for $x, y \in \mathbb{Z^+}$.
+
+Let $d$ for $d \in \mathbb{Z^+}$ being the greatest common divisor of $x$ and $y$, a.k.a $d = gcd(x, y)$.
+As $d$ being a divisor of both $x$ and $y$, we may therefore have $x = kd$ and $y = jd$ for $k, j \in \mathbb{Z^+}$.
+Then we may infer:
+\begin{gather}
+    x - y = dk - dj = d(k - j)
+\end{gather}
+
+From \textit{Equation 2} and the known fact that $y = jd$, we may say that $d$ is also a common divisor of $x - y$ and $y$.
+By the defination of $gcd$, this means the upper bond of $d$ cannot be greater than $gcd(x-y, y)$.
+Thus we may conclude:
+\begin{gather}
+    gcd(x, y) = d \leq gcd(x-y, y) \nonumber \\
+    \Rightarrow gcd(x, y) \leq gcd(x-y, y)
+\end{gather}
+
+Now similarly, Let $e$ for $e \in \mathbb{Z^+}$ being the greatest common divisor of $x-y$ and $y$. We may therefore have $x - y = le$ and $y = me$ for $l, m \in \mathbb{Z^+}$. Then we may infer:
+\begin{gather}
+    x = (x - y) + y = le + me = e(l + m)
+\end{gather}
+
+From \textit{Equation 4} and the known fact that $y = me$, we may say that $e$ is also a common divisor of $x$ and $y$.
+By the defination of $gcd$, this means the upper bond of $e$ cannot be greater than $gcd(x, y)$.
+Thus we may conclude:
+\begin{gather}
+    gcd(x-y, y) = e \leq gcd(x, y) \nonumber  \\
+    \Rightarrow gcd(x-y, y) \leq gcd(x, y)
+\end{gather}
+
+By observing \textit{Equation 3} and \textit{Equation 5}, we may have a constraint of $gcd(x, y) = gcd(x-y, y)$.
+As the given method $Euclidean()$ is a $gcd$ finder, we may promote such constraint to $Euclidean(x, y) = Euclidean(x - y, y)$ due to the equivalency of $Euclidean(a, b)$ and $gcd(a, b)$.
+
+\subsection{(c)}
+
+The \inlinecode{while} loop always terminates as the condition $x = y$ will eventually be reached.
+Due to the fact that we have $x$ and $y$ for $x, y \in \mathbb{Z^+}$; without loss of generality, we assume $x > y$, therefore we must have $x' = x - y$ for $x' \in \mathbb{Z^+}$.
+
+As we have only a finte amount of $x'$, $x''$, $x'''$...
+to decrease for $x', x'', \text{and}\ x''' \in \mathbb{Z^+}$, the decremental calculation of $x_{k+1} = x_{k} - y_{k}$\footnote{for $k$ being the numbers of iteration went through in the \inlinecode{while} loop.} will eventually reaches a condition where $x = y$ due to the ``well ordering'' nature of the natural numbers.
+Thus, the \inlinecode{while} loop always terminates.
+
+\subsection{(d)}
+
+In \textbf{Section 1.2}, we have proven that $gcd(x, y) = gcd(x-y, y) \Rightarrow Euclidean(x, y) = Euclidean(x - y, y)$ assuming $x > y$ for $x, y \in \mathbb{Z^+}$.
+Following the principle of induction, we can generalize it as:
+
+\begin{gather}
+    Euclidean(x, y) = Euclidean(x_{k+1}, y_{k+1}) \\
+    \text{for $x', y' \in \mathbb{Z^+}$ while } \nonumber \\
+    \text{$x_{k+1} = x_{k} - y_{k}$ if $x_{k} > y_{k}$ and $y_{k+1} = y_{k} - x_{k}$ if $y_{k} > x_{k}$} \nonumber
+\end{gather}
+
+Where $Euclidean(x_{k+1}, y_{k+1})$ is the greatest common divisor of $(x, y)$.\newline
+
+As we haven proven in \textbf{Section 1.2}, that the \inlinecode{while} loop within the $Euclidean()$ method must terminate. Combined such finding with \textit{Equation 6}, we must have a:
+\begin{gather}
+    Euclidean(a, b) = Euclidean(a_{k+1}, b_{k+1}) = Euclidean(a_{k+2}, a_{k+2})
+    % without loss of generality
+\end{gather}
+
+As we know by calculation that $Euclidean(a_{k+2}, a_{k+2}) = a_{k+2}$, $a_{k+2}$ will be the greatest common divisor of $Euclidean(a, b)$.
 
 \section{Problem 2}
+\subsection{(a)}
+\subsection{(b)}
+\subsection{(c)}
+\subsection{(d)}
 

### 2020-01-26 assignment_1/article.tex
✨ Add pseudo-code for Problem 2(a).
✨ Add sketch answer to Problem 2(c) and Problem 2(d).

@@
 \usepackage{etoolbox}
+\usepackage{algorithm}
+% \usepackage{algorithmic}
+\usepackage[noend]{algpseudocode}
 \patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
@@
 
-\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Bobby) CHEN, \inlinecode{zxc325}}
+\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Robert) CHEN, \inlinecode{zxc325}}
 \date{Due on 01/27/2020, submitted on 01/26/2020 \\ EECS 340, Dr. Koyuturk}
@@
 \subsection{(a)}
+
+\begin{algorithm}
+\caption{TwoSum(A, B, n, x) with two pointers}\label{TwoSum}
+\begin{algorithmic}[1]
+\Procedure{}{}
+\State $j \gets n-1$
+\State $i \gets 0$
+\While {$i < n \textbf{ and } j \geq 0$}
+    \If {\textit{$A[i] + B[j] < x$}}
+        \State $i \gets i + 1$
+    \ElsIf {\textit{$A[i] + B[j] > x$}}
+        \State $j \gets j - 1$
+    \Else
+        \State \Return $i, j$
+    \EndIf
+\EndWhile
+\State \Return $False$
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+
 \subsection{(b)}
 \subsection{(c)}
+If $A[i] + B[j] \neq x$, then it is impossible to have any combination $(a, b)$ where \\ $a \in \{A[0], A[1], ..., A[i-1], A[i]\}$ and $b \in \{B[j], B[j+1], B[j+2], ..., B[n-1]\}$ to \\be $a + b = x$ for all \textbf{iterarted} $i, j$ within the \inlinecode{while} loop.
+
+Assume we get $A[i] + B[j] = k$ within an interation of the \inlinecode{while} loop, we either have $k < x$ or $k > x$ (assume $A[i] + B[j] \neq x$ because otherwise the loop will be terminated and the problem will be solved).
+Due to the sorted nature of array $A, B$, we must have:
+\begin{gather}
+    \underbrace{A[0] \leq A[1] \leq ... \leq A[i-1]}_{a} \leq A[i]  \ \ \ \Rightarrow a \leq A[i]\\
+    \underbrace{B[n-1] \geq ... \geq B[j+2] \geq B[j+1]}_{b} \geq B[j] \ \ \ \Rightarrow b \geq B[j]
+\end{gather}
+
+Thus, we may infer the followings from the above two \textit{Equations}:
+\begin{gather}
+    \text{if } k < x: \ a + B[j] \leq A[i] + B[j]  \ \ \ \Rightarrow a + B[j] < x\\
+    \text{if } k > x: \ A[i] + b \geq A[i] + B[j]  \ \ \ \Rightarrow A[i] + b > x
+\end{gather}
+
+It is a bit unintuitive about the case of $a' + b'$ for $a' \in \{A[0], A[1], ..., A[i-1]\}$ and $b' \in \{B[j+1], B[j+2], ..., B[n-1]\}$.
+But as the value of index $i$ ($j$) travels in an incremental (decremental) fashion in the bond of $\matthbb{Z+} \in [0, n)$; the index of $a'$ must be smaller than $i$, and the index of $b'$ must be greater than $j$.
+Thus, if there is any $a' + b' = x$, such loop would have been terminated immediately and we should not be able to reach to indexes $i, j$ in the \inlinecode{while} loop.
+Therefore, as we are now at the $i, j$ iteration of the \inlinecode{while} loop, this suggests there is no $(a', b')$ combination where $a' + b' = x$.
+
+This together with \textit{Equation 10, 11}, we have proven the loop invariant as there will be no combination of $(a, b)$ where $a \in \{A[0], A[1], ..., A[i-1], A[i]\}$ and $b \in \{B[j], B[j+1], B[j+2], ..., B[n-1]\}$ to be $a + b = x$ for all \textbf{iterarted} $i, j$ within the \inlinecode{while} loop.
+
 \subsection{(d)}
+The worst case of this algorithm is when it returns \inlinecode{False}.
+In such case we wil have $i$ and $j$ travel the entire bond of $\matthbb{Z+} \in [0, n)$.
+The loop will execute $2n$ times, thus the run time is $O(n)$.
 

### 2020-01-26 assignment_1/article.tex
🔨 Improve clarity on the induction-related arguments in Problem 1.

@@
 \begin{gather}
-    Euclidean(x, y) = Euclidean(x_{k+1}, y_{k+1}) \\
+    Euclidean(x_k, y_k) = Euclidean(x_{k+1}, y_{k+1}) \\
     \text{for $x', y' \in \mathbb{Z^+}$ while } \nonumber \\
-    \text{$x_{k+1} = x_{k} - y_{k}$ if $x_{k} > y_{k}$ and $y_{k+1} = y_{k} - x_{k}$ if $y_{k} > x_{k}$} \nonumber
+    \text{$x_{k+1} = x_{k} - y_{k}$, $y_{k+1} = y_{k}$ \ \ \  if $x_{k} > y_{k}$} \nonumber \\
+    \text{$y_{k+1} = y_{k} - x_{k}$, $x_{k+1} = x_{k}$ \ \ \  if $y_{k} > x_{k}$} \nonumber
 \end{gather}
@@
 
-As we haven proven in \textbf{Section 1.2}, that the \inlinecode{while} loop within the $Euclidean()$ method must terminate. Combined such finding with \textit{Equation 6}, we must have a:
+As we haven proven in \textbf{Section 1.2}, that the \inlinecode{while} loop within the $Euclidean()$ method must terminate. Combined such finding with \textit{Equation 6}, we must also have a:
 \begin{gather}
-    Euclidean(a, b) = Euclidean(a_{k+1}, b_{k+1}) = Euclidean(a_{k+2}, a_{k+2})
+    Euclidean(a, b) = Euclidean(a_{k}, b_{k}) = Euclidean(a_{k+1}, b_{k+1}) = ... \\ ... = Euclidean(a_{k+n}, b_{k+n}) = Euclidean(a_{k+n}, a_{k+n}) \nonumber
     % without loss of generality
@@
 
-As we know by calculation that $Euclidean(a_{k+2}, a_{k+2}) = a_{k+2}$, $a_{k+2}$ will be the greatest common divisor of $Euclidean(a, b)$.
+As we know by calculation that $Euclidean(a_{k+n}, a_{k+n}) = a_{k+n}$, $a_{k+n}$, this will be the greatest common divisor of $Euclidean(a, b)$.
 

### 2020-01-26 assignment_1/article.tex
✨ Add sketch answer to Problem 3.
Co-Authored-By: bobbyCZT <zxc325@users.noreply.github.com>

@@
 It is a bit unintuitive about the case of $a' + b'$ for $a' \in \{A[0], A[1], ..., A[i-1]\}$ and $b' \in \{B[j+1], B[j+2], ..., B[n-1]\}$.
-But as the value of index $i$ ($j$) travels in an incremental (decremental) fashion in the bond of $\matthbb{Z+} \in [0, n)$; the index of $a'$ must be smaller than $i$, and the index of $b'$ must be greater than $j$.
+But as the value of index $i$ ($j$) travels in an incremental (decremental) fashion in the bond of $\mathbb{Z^+} \in [0, n)$; the index of $a'$ must be smaller than $i$, and the index of $b'$ must be greater than $j$.
 Thus, if there is any $a' + b' = x$, such loop would have been terminated immediately and we should not be able to reach to indexes $i, j$ in the \inlinecode{while} loop.
@@
 The worst case of this algorithm is when it returns \inlinecode{False}.
-In such case we wil have $i$ and $j$ travel the entire bond of $\matthbb{Z+} \in [0, n)$.
+In such case we wil have $i$ and $j$ travel the entire bond of $\mathbb{Z^+} \in [0, n)$.
 The loop will execute $2n$ times, thus the run time is $O(n)$.
@@
 \section{Problem 3}
+\subsection{Describe the process using a loop: Pseudocode}
+
+% l = red, p = black
+\begin{algorithm}
+\caption{Kepler442b(m, n)}\label{Kepler442b}
+\begin{algorithmic}[1]
+\Procedure{}{}
+\State $l \gets m$
+\State $p \gets n$
+\While {$(l + p) > 1$}
+    \State \text{Let two individuals fight each other.}
+    \If {\text{Both individuals are Lydians}}
+        \State $l \gets l - 1$
+    \ElsIf {\text{Both individuals are Pisidians}}
+        \State $p \gets p - 2$
+        \State $l \gets l + 1$
+    \Else
+        \State $l \gets l - 1$
+    \EndIf
+\EndWhile
+\State \Return $l, p$
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+
+\subsection{Define loop invariant and termination}
+At the start of the $k^{th}$ iteration of the \inlinecode{while} loop, we must have
+\begin{gather}
+    l + p = m + n - (k - 1) \\
+    p\bmod 2 = n \bmod 2
+\end{gather}
+
+When the \inlinecode{while} loop terminates at $l + p = 1$ there can only be two cases:
+\begin{gather}
+    l = 1, \ p = 0 \ \ (n \bmod 2 = 0) \\
+    l = 0, \ p = 1 \ \ (n \bmod 2 = 1)
+\end{gather}
+
+Thus, we may infer that if $n$ is odd, a \textit{Pisidian} shall remain. Otherwise if $n$ is even, a \textit{Lydian} shall remain.
+
+\subsection{Proof of loop invariant}
+\subsubsection{Initialization}
+At the beginning it is known that $k = 1$ and $b = n$, thus we may have:
+
+\begin{gather}
+    l + p = m + n - (k - 1) = l + p = m + n - (1 - 1) \Rightarrow l + p = m + n \\
+    p\bmod 2 = n \bmod 2
+\end{gather}
+
+As the above two \textit{Equations} satisfy the assumption of the loop invariant, we may say that the scenario of $k = 1$ is true.
+
+\subsubsection{Maintenance}
+
+\paragraph{Case 1} As it is known that $l + p = (l - 1) + p$ and $k = k + 1$, we may conclude that $l + p + k$ must remain the same.
+
+\paragraph{Case 2} As it is known that $l + p = (l + 1) + (p - 2)$ and $k = k + 1$, we may conclude that $l + p + k$ must remain the same.
+
+\paragraph{Case 3} As it is known that $l + p = (l - 1) + p$ and $k = k + 1$, we may conclude that $l + p + k$ must remain the same.
+
+As all three cases satisfy the loop invariant of the algorithm, the induction is therefore proven to be valid.
 

### 2020-01-26 assignment_1/article.tex
✨ Add sketch answer to Problem 2(b).
Co-Authored-By: bobbyCZT <zxc325@users.noreply.github.com>

@@
 \usepackage[noend]{algpseudocode}
+\usepackage{tikz}
+\usetikzlibrary{matrix,positioning,arrows.meta,arrows}
 \patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
@@
 
+\newpage
+
 \subsection{(b)}
+
+The following is graphical demenstration of \textit{TwoSum(A, B, 5, 12)}:
+\tikzset{
+mymat/.style={
+  matrix of math nodes,
+  text height=2.5ex,
+  text depth=0.75ex,
+  text width=3.25ex,
+  align=center,
+  column sep=-\pgflinewidth
+  },
+mymats/.style={
+  mymat,
+  nodes={draw,fill=#1}
+  }
+}
+
+\begin{tikzpicture}[>=latex]
+
+\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
+at (0,0)
+(mat1)
+{
+0 & 1 & 2(i) & 3 & 4 \\
+1 & 3 & 5 & 7 & 9 \\
+};
+
+\matrix[mymat,right=of mat1,row 2/.style={nodes={draw,fill=gray!30}}]
+at (10,0)
+(mat2)
+{
+0 & 1 & 2 & 3(j) & 4 \\
+2 & 4 & 6 & 7 & 10 \\
+};
+
+\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
+at (0,2)
+(mat3)
+{
+0 & 1(i) & 2 & 3 & 4 \\
+1 & 3 & 5 & 7 & 9 \\
+};
+\matrix[mymat,right=of mat3,row 2/.style={nodes={draw,fill=gray!30}}]
+at (10,2)
+(mat4)
+{
+0 & 1 & 2 & 3(j) & 4 \\
+2 & 4 & 6 & 7 & 10 \\
+};
+
+\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
+at (0,4)
+(mat5)
+{
+0 & 1(i) & 2 & 3 & 4 \\
+1 & 3 & 5 & 7 & 9 \\
+};
+\matrix[mymat,right=of mat5,row 2/.style={nodes={draw,fill=gray!30}}]
+at (10,4)
+(mat6)
+{
+0 & 1 & 2 & 3 & 4(j) \\
+2 & 4 & 6 & 7 & 10 \\
+};
+
+\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
+at (0,6)
+(mat7)
+{
+0(i) & 1 & 2 & 3 & 4 \\
+1 & 3 & 5 & 7 & 9 \\
+};
+\matrix[mymat,right=of mat7,row 2/.style={nodes={draw,fill=gray!30}}]
+at (10,6)
+(mat8)
+{
+0 & 1 & 2 & 3 & 4(j) \\
+2 & 4 & 6 & 7 & 10 \\
+};
+
+\node[above=0pt of mat7]
+  (cella) {A};
+\node[above=0pt of mat8]
+  (cellb) {B};
+
+\end{tikzpicture}\newline
+
+Thus we have $A[i] + B[j] = 12$ for $(i, j)$ being $(2, 3)$.
+
 \subsection{(c)}

### 2020-01-27 assignment_1/article.tex
💄 Adjust format to have Problem 2(b) graph displayed continuously.
Co-Authored-By: bobbyCZT <zxc325@users.noreply.github.com>
♻️ Restructure Problem 2(d) with the loop invariant approach.

@@
 \usepackage{setspace}
-\setstretch{1.1}
+\setstretch{1}
 \usepackage{amsmath,amssymb, amsthm}
@@
 From \textit{Equation 2} and the known fact that $y = jd$, we may say that $d$ is also a common divisor of $x - y$ and $y$.
-By the defination of $gcd$, this means the upper bond of $d$ cannot be greater than $gcd(x-y, y)$.
+By the defination of $gcd$, this means the upper bound of $d$ cannot be greater than $gcd(x-y, y)$.
 Thus we may conclude:
@@
 From \textit{Equation 4} and the known fact that $y = me$, we may say that $e$ is also a common divisor of $x$ and $y$.
-By the defination of $gcd$, this means the upper bond of $e$ cannot be greater than $gcd(x, y)$.
+By the defination of $gcd$, this means the upper bound of $e$ cannot be greater than $gcd(x, y)$.
 Thus we may conclude:
@@
 
-\newpage
+% \newpage
 
@@
 \subsection{(c)}
-If $A[i] + B[j] \neq x$, then it is impossible to have any combination $(a, b)$ where \\ $a \in \{A[0], A[1], ..., A[i-1], A[i]\}$ and $b \in \{B[j], B[j+1], B[j+2], ..., B[n-1]\}$ to \\be $a + b = x$ for all \textbf{iterarted} $i, j$ within the \inlinecode{while} loop.
+\subsubsection{Loop invariant}
+To enter the \inlinecode{while} loop with indexes $i, j$, it is impossible to have any combination of $(a, b)$ where $a \in \{A[0], A[1], ..., A[i-1]\}$ and $b \in \{B[j+1], B[j+2], ..., B[n-1]\}$ to be $a + b = x$.
 
-Assume we get $A[i] + B[j] = k$ within an interation of the \inlinecode{while} loop, we either have $k < x$ or $k > x$ (assume $A[i] + B[j] \neq x$ because otherwise the loop will be terminated and the problem will be solved).
+\subsubsection{Initialization}
+The loop invariant is held true during the initialization, since for $i = 0$ and $j = n-1$, we must have $a = \emptyset$ and $b = \emptyset$.
+Thus, it is impossible to have a combination of $(a, b)$ to be $a + b = x$.
+
+\subsubsection{Maintenance}
+
 Due to the sorted nature of array $A, B$, we must have:
+
 \begin{gather}
@@
 
-Thus, we may infer the followings from the above two \textit{Equations}:
+Assume we get $A[i] + B[j] = k$ within an iteration of the \inlinecode{while} loop, we either have $k < x$ or $k > x$.
+In both cases, we may confidently say that there will be no $a + b = k$.
+As the index of $a$ must be smaller than $i$ and the index of $b$ must be greater than $j$.
+Thus, if there is any $a + b = x$, such loop would have been terminated immediately and we should not be able to reach to indexes $i, j$ in the \inlinecode{while} loop.
+Therefore, as we are now at the $i, j$ iteration of the \inlinecode{while} loop, this suggests there is no $(a, b)$ combination where $a + b = x$.
+By this, the loop invariant is held true for all cases within the \inlinecode{while} loop.\newline
+
+Then, to proceed the loop, we may infer the following from \textit{Equation 8} and \textit{9}:
+
 \begin{gather}
-    \text{if } k < x: \ a + B[j] \leq A[i] + B[j]  \ \ \ \Rightarrow a + B[j] < x\\
-    \text{if } k > x: \ A[i] + b \geq A[i] + B[j]  \ \ \ \Rightarrow A[i] + b > x
+    \text{if } k < x: \ a + B[j] \leq A[i] + B[j] = k  \ \ \ \Rightarrow a + B[j] < x\\
+    \text{if } k > x: \ A[i] + b \geq A[i] + B[j] = k  \ \ \ \Rightarrow A[i] + b > x
 \end{gather}
 
-It is a bit unintuitive about the case of $a' + b'$ for $a' \in \{A[0], A[1], ..., A[i-1]\}$ and $b' \in \{B[j+1], B[j+2], ..., B[n-1]\}$.
-But as the value of index $i$ ($j$) travels in an incremental (decremental) fashion in the bond of $\mathbb{Z^+} \in [0, n)$; the index of $a'$ must be smaller than $i$, and the index of $b'$ must be greater than $j$.
-Thus, if there is any $a' + b' = x$, such loop would have been terminated immediately and we should not be able to reach to indexes $i, j$ in the \inlinecode{while} loop.
-Therefore, as we are now at the $i, j$ iteration of the \inlinecode{while} loop, this suggests there is no $(a', b')$ combination where $a' + b' = x$.
-
-This together with \textit{Equation 10, 11}, we have proven the loop invariant as there will be no combination of $(a, b)$ where $a \in \{A[0], A[1], ..., A[i-1], A[i]\}$ and $b \in \{B[j], B[j+1], B[j+2], ..., B[n-1]\}$ to be $a + b = x$ for all \textbf{iterarted} $i, j$ within the \inlinecode{while} loop.
+As there is no $(a, b)$ combination available to form a $x$, we must increse the value of index $i$ in the case of $k < x$ to achieve a hopefully greather $k'$ in the next interation; and similarly, to decrese the value of index $j$ to achieve a hopefully lesser $k'$ in the next interation.
+Thus, the conditional statements in the pseudocode in \textbf{Section 2.1} are justified.
 
@@
 The worst case of this algorithm is when it returns \inlinecode{False}.
-In such case we wil have $i$ and $j$ travel the entire bond of $\mathbb{Z^+} \in [0, n)$.
+In such case we will have $i$ and $j$ traveling the entire bound of $\mathbb{Z^+} \in [0, n)$.
 The loop will execute $2n$ times, thus the run time is $O(n)$.

### 2020-01-28 assignment_1/article.tex
🐛 ♻️ Correct Problem 1's loop invariant statement and proof.

@@
 \subsection{(a)}
-Without loss of generality, assume $x > y$ for $x, y \in \mathbb{Z^+}$. The loop invariant is:
+With $gcd(a, b)$ giving the greatest common divisor of $(a, b)$, the loop invariant is:
 
 \begin{gather}
-    Euclidean(x, y) = Euclidean(x - y, y)
+    gcd(a, b) = gcd(x, y) \\
+    \text{for $a, b, x, y \in \mathbb{Z^+}$}\nonumber
 \end{gather}
@@
 \subsection{(b)}
-Without loss of generality, assume $x > y$ for $x, y \in \mathbb{Z^+}$.
+\subsubsection{Initialization}
+
+The loop invariant is held true during initialization of the \inlinecode{while} loop as we defined $x = a$ and $y = b$ in the algorithm, thus \textit{Equation 1} is perserved.
+
+\subsubsection{Maintenance}
+
+Assume we had $x, y$ in the pervious iteration, for this iteration we shall have $x', y'$. Without loss of generality, assume $x > y$, we must have the following according to the algorithm:
+\begin{gather}
+    x' = x - y \nonumber\\
+    y' = x \nonumber
+\end{gather}
 
@@
 
-By observing \textit{Equation 3} and \textit{Equation 5}, we may have a constraint of $gcd(x, y) = gcd(x-y, y)$.
-As the given method $Euclidean()$ is a $gcd$ finder, we may promote such constraint to $Euclidean(x, y) = Euclidean(x - y, y)$ due to the equivalency of $Euclidean(a, b)$ and $gcd(a, b)$.
+By observing \textit{Equation 3} and \textit{Equation 5}, we may conclude $gcd(x, y) = gcd(x-y, y)$.
+As we have discovered $x' = x - y$ and $y' = y$ earlier in this section, this means $gcd(x, y) = gcd(x-y, y) = gcd(x', y')$.
+Thus, the loop invariant is held true during the maintenance of the \inlinecode{while} loop.
 
@@
 The \inlinecode{while} loop always terminates as the condition $x = y$ will eventually be reached.
-Due to the fact that we have $x$ and $y$ for $x, y \in \mathbb{Z^+}$; without loss of generality, we assume $x > y$, therefore we must have $x' = x - y$ for $x' \in \mathbb{Z^+}$.
+Due to the fact that we have $x$ and $y$ for $x, y \in \mathbb{Z^+}$; without loss of generality, we assume $x > y$, therefore we must have $x' = x - y$  and for $x' \in \mathbb{Z^+}$.
 
 As we have only a finte amount of $x'$, $x''$, $x'''$...
-to decrease for $x', x'', \text{and}\ x''' \in \mathbb{Z^+}$, the decremental calculation of $x_{k+1} = x_{k} - y_{k}$\footnote{for $k$ being the numbers of iteration went through in the \inlinecode{while} loop.} will eventually reaches a condition where $x = y$ due to the ``well ordering'' nature of the natural numbers.
+to decrease in the bound of $\mathbb{Z^+} \in [0, x]$, the decremental calculation of $x_{k+1} = x_{k} - y_{k}$\footnote{for $k$ being the numbers of iteration went through in the \inlinecode{while} loop.} will eventually reaches a condition where $x = y$ due to the ``well ordering'' nature of the natural numbers.
 Thus, the \inlinecode{while} loop always terminates.
@@
 
-In \textbf{Section 1.2}, we have proven that $gcd(x, y) = gcd(x-y, y) \Rightarrow Euclidean(x, y) = Euclidean(x - y, y)$ assuming $x > y$ for $x, y \in \mathbb{Z^+}$.
-Following the principle of induction, we can generalize it as:
+In \textbf{Section 1.2}, we have proven that $gcd(x, y) = gcd(x-y, y)$ assuming $x > y$ for $x, y \in \mathbb{Z^+}$. Following the principle of induction, we can generalize it as:
 
 \begin{gather}
-    Euclidean(x_k, y_k) = Euclidean(x_{k+1}, y_{k+1}) \\
-    \text{for $x', y' \in \mathbb{Z^+}$ while } \nonumber \\
+    gcd(x_k, y_k) = gcd(x_{k+1}, y_{k+1}) \\
+    \text{for $x', y' \in \mathbb{Z^+}$,  while } \nonumber \\
     \text{$x_{k+1} = x_{k} - y_{k}$, $y_{k+1} = y_{k}$ \ \ \  if $x_{k} > y_{k}$} \nonumber \\
@@
 
-Where $Euclidean(x_{k+1}, y_{k+1})$ is the greatest common divisor of $(x, y)$.\newline
-
-As we haven proven in \textbf{Section 1.2}, that the \inlinecode{while} loop within the $Euclidean()$ method must terminate. Combined such finding with \textit{Equation 6}, we must also have a:
+As we have proven in \textbf{Section 1.2}, that the \inlinecode{while} loop within the algorithm must terminate. Combined such finding with \textit{Equation 6}, we must also have a:
 \begin{gather}
-    Euclidean(a, b) = Euclidean(a_{k}, b_{k}) = Euclidean(a_{k+1}, b_{k+1}) = ... \\ ... = Euclidean(a_{k+n}, b_{k+n}) = Euclidean(a_{k+n}, a_{k+n}) \nonumber
+    gcd(a, b) = gcd(a_{k}, b_{k}) = gcd(a_{k+1}, b_{k+1}) = ... \\ ... = gcd(a_{k+n}, b_{k+n}) = gcd(a_{k+n}, a_{k+n}) \nonumber
     % without loss of generality
@@
 
-As we know by calculation that $Euclidean(a_{k+n}, a_{k+n}) = a_{k+n}$, $a_{k+n}$, this will be the greatest common divisor of $Euclidean(a, b)$.
+As we known by calculation that $gcd(a_{k+n}, a_{k+n}) = a_{k+n}$, thus, $a_{k+n}$ will be the greatest common divisor of $(a, b)$.
+As the induction performed in \textit{Equation 7} according to constraints defined in \textit{Equation 6} is an exact mathematical mimic of the iterations of the given \inlinecode{Euclidean} algorithm, we may conclude that \inlinecode{Euclidean(a, b)} returns $gcd(a, b)$.
 

### 2020-01-28 assignment_1/article.tex
💄 Fix some expressions in Problem 2 for better reading continuity.

@@
 
-% \newpage
+\newpage
 
@@
 
-The following is graphical demenstration of \textit{TwoSum(A, B, 5, 12)}:
+The following is graphical demenstration of \inlinecode{TwoSum(A, B, 5, 12)}:
 \tikzset{
@@
 Assume we get $A[i] + B[j] = k$ within an iteration of the \inlinecode{while} loop, we either have $k < x$ or $k > x$.
-In both cases, we may confidently say that there will be no $a + b = k$.
-As the index of $a$ must be smaller than $i$ and the index of $b$ must be greater than $j$.
+In both cases, we may confidently say that there will be no $a + b = k$; as the index of $a$ must be smaller than $i$ and the index of $b$ must be greater than $j$.
 Thus, if there is any $a + b = x$, such loop would have been terminated immediately and we should not be able to reach to indexes $i, j$ in the \inlinecode{while} loop.
@@
 
-As there is no $(a, b)$ combination available to form a $x$, we must increse the value of index $i$ in the case of $k < x$ to achieve a hopefully greather $k'$ in the next interation; and similarly, to decrese the value of index $j$ to achieve a hopefully lesser $k'$ in the next interation.
-Thus, the conditional statements in the pseudocode in \textbf{Section 2.1} are justified.
+As there is no $(a, b)$ combination available to form $a+b = x$, we must increse the value of index $i$ in the case of $k < x$ to achieve a hopefully greather $k'$ in the next interation; and similarly, to decrese the value of index $j$ to achieve a hopefully lesser $k'$ in the case of $k > x$.
+Thus, the conditional statements in the pseudocode in \textbf{Section 2.1} are justified, and the algorithm is proven to be correct.
 
@@
 In such case we will have $i$ and $j$ traveling the entire bound of $\mathbb{Z^+} \in [0, n)$.
-The loop will execute $2n$ times, thus the run time is $O(n)$.
+The loop will execute $2n$ times, thus the run time is $\Theta(n)$.
 

### 2020-01-28 assignment_1/article.tex
💄 Polish language based on Grammly.

@@
 
-Assume we had $x, y$ in the pervious iteration, for this iteration we shall have $x', y'$. Without loss of generality, assume $x > y$, we must have the following according to the algorithm:
+Assume we had $x, y$ in the previous iteration, for this iteration we shall have $x', y'$. Without loss of generality, assume $x > y$, we must have the following according to the algorithm:
 \begin{gather}
@@
 
-As there is no $(a, b)$ combination available to form $a+b = x$, we must increse the value of index $i$ in the case of $k < x$ to achieve a hopefully greather $k'$ in the next interation; and similarly, to decrese the value of index $j$ to achieve a hopefully lesser $k'$ in the case of $k > x$.
+As there is no $(a, b)$ combination available to form $a+b = x$, we must increase the value of index $i$ in the case of $k < x$ to achieve a hopefully greater $k'$ in the next iteration; and similarly, to decrease the value of index $j$ to achieve a hopefully lesser $k'$ in the case of $k > x$.
 Thus, the conditional statements in the pseudocode in \textbf{Section 2.1} are justified, and the algorithm is proven to be correct.
@@
 The worst case of this algorithm is when it returns \inlinecode{False}.
-In such case we will have $i$ and $j$ traveling the entire bound of $\mathbb{Z^+} \in [0, n)$.
-The loop will execute $2n$ times, thus the run time is $\Theta(n)$.
+In such case, we will have $i$ and $j$ traveling the entire bound of $\mathbb{Z^+} \in [0, n)$.
+The loop will execute $2n$ times; thus the run time is $\Theta(n)$.
 
@@
 
-Thus, we may infer that if $n$ is odd, a \textit{Pisidian} shall remain. Otherwise if $n$ is even, a \textit{Lydian} shall remain.
+Thus, we may infer that if $n$ is odd, a \textit{Pisidian} shall remain. Otherwise, if $n$ is even, a \textit{Lydian} shall remain.
 

### 2020-01-28 assignment_1/article.tex
💄 Fix language after proofread.

@@
 \author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Robert) CHEN, \inlinecode{zxc325}}
-\date{Due on 01/27/2020, submitted on 01/26/2020 \\ EECS 340, Dr. Koyuturk}
+\date{Due and submitted on 01/27/2020 \\ EECS 340, Dr. Koyuturk}
 \maketitle
@@
 
-Now similarly, Let $e$ for $e \in \mathbb{Z^+}$ being the greatest common divisor of $x-y$ and $y$. We may therefore have $x - y = le$ and $y = me$ for $l, m \in \mathbb{Z^+}$. Then we may infer:
+Now similarly, let $e$ for $e \in \mathbb{Z^+}$ being the greatest common divisor of $x-y$ and $y$. We may therefore have $x - y = le$ and $y = me$ for $l, m \in \mathbb{Z^+}$. Then we may infer:
 \begin{gather}
@@
 \section{Problem 2}
+As suggested by Dr.
+Koyuturk, this is a kindly reminder to the grader that this problem is answered with the assumption of the first index of an array being $[0]$.
+If you'd prefer $[1]$, please let us know through Canvas comment section and we will adjust accordingly in our future submission.
 \subsection{(a)}
@@
 \begin{algorithm}
-\caption{Kepler442b(m, n)}\label{Kepler442b}
+\caption{Kepler442bArena(m, n)}\label{Kepler442b}
 \begin{algorithmic}[1]
@@
 
-When the \inlinecode{while} loop terminates at $l + p = 1$ there can only be two cases:
+When the \inlinecode{while} loop terminates at $l + p = 1$, there can only be two cases:
 \begin{gather}
@@
 
-As the above two \textit{Equations} satisfy the assumption of the loop invariant, we may say that the scenario of $k = 1$ is true.
+As the above two \textit{Equations} satisfy the assumption of the loop invariant, we may say that the scenario of $k = 1$ is held true.
 

### 2020-02-02 assignment_2/article.tex
🎉 Add placeholder Assignment 2 .tex file.

--- 2020-01-28 assignment_1/article.tex
@@
 
-\title{\textbf{EECS 340: Assignment 1}}
+\title{\textbf{EECS 340: Assignment 2}}
 
 \author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Robert) CHEN, \inlinecode{zxc325}}
-\date{Due on 01/27/2020, submitted on 01/26/2020 \\ EECS 340, Dr. Koyuturk}
+\date{Due and submitted on 02/03/2020 \\ EECS 340, Dr. Koyutürk}
 \maketitle
@@
 \section{Problem 1}
-\subsection{(a)}
-With $gcd(a, b)$ giving the greatest common divisor of $(a, b)$, the loop invariant is:
-
-\begin{gather}
-    gcd(a, b) = gcd(x, y) \\
-    \text{for $a, b, x, y \in \mathbb{Z^+}$}\nonumber
-\end{gather}
-
-\subsection{(b)}
-\subsubsection{Initialization}
-
-The loop invariant is held true during initialization of the \inlinecode{while} loop as we defined $x = a$ and $y = b$ in the algorithm, thus \textit{Equation 1} is perserved.
-
-\subsubsection{Maintenance}
-
-Assume we had $x, y$ in the pervious iteration, for this iteration we shall have $x', y'$. Without loss of generality, assume $x > y$, we must have the following according to the algorithm:
-\begin{gather}
-    x' = x - y \nonumber\\
-    y' = x \nonumber
-\end{gather}
-
-Let $d$ for $d \in \mathbb{Z^+}$ being the greatest common divisor of $x$ and $y$, a.k.a $d = gcd(x, y)$.
-As $d$ being a divisor of both $x$ and $y$, we may therefore have $x = kd$ and $y = jd$ for $k, j \in \mathbb{Z^+}$.
-Then we may infer:
-\begin{gather}
-    x - y = dk - dj = d(k - j)
-\end{gather}
-
-From \textit{Equation 2} and the known fact that $y = jd$, we may say that $d$ is also a common divisor of $x - y$ and $y$.
-By the defination of $gcd$, this means the upper bound of $d$ cannot be greater than $gcd(x-y, y)$.
-Thus we may conclude:
-\begin{gather}
-    gcd(x, y) = d \leq gcd(x-y, y) \nonumber \\
-    \Rightarrow gcd(x, y) \leq gcd(x-y, y)
-\end{gather}
-
-Now similarly, Let $e$ for $e \in \mathbb{Z^+}$ being the greatest common divisor of $x-y$ and $y$. We may therefore have $x - y = le$ and $y = me$ for $l, m \in \mathbb{Z^+}$. Then we may infer:
-\begin{gather}
-    x = (x - y) + y = le + me = e(l + m)
-\end{gather}
-
-From \textit{Equation 4} and the known fact that $y = me$, we may say that $e$ is also a common divisor of $x$ and $y$.
-By the defination of $gcd$, this means the upper bound of $e$ cannot be greater than $gcd(x, y)$.
-Thus we may conclude:
-\begin{gather}
-    gcd(x-y, y) = e \leq gcd(x, y) \nonumber  \\
-    \Rightarrow gcd(x-y, y) \leq gcd(x, y)
-\end{gather}
-
-By observing \textit{Equation 3} and \textit{Equation 5}, we may conclude $gcd(x, y) = gcd(x-y, y)$.
-As we have discovered $x' = x - y$ and $y' = y$ earlier in this section, this means $gcd(x, y) = gcd(x-y, y) = gcd(x', y')$.
-Thus, the loop invariant is held true during the maintenance of the \inlinecode{while} loop.
-
-\subsection{(c)}
-
-The \inlinecode{while} loop always terminates as the condition $x = y$ will eventually be reached.
-Due to the fact that we have $x$ and $y$ for $x, y \in \mathbb{Z^+}$; without loss of generality, we assume $x > y$, therefore we must have $x' = x - y$  and for $x' \in \mathbb{Z^+}$.
-
-As we have only a finte amount of $x'$, $x''$, $x'''$...
-to decrease in the bound of $\mathbb{Z^+} \in [0, x]$, the decremental calculation of $x_{k+1} = x_{k} - y_{k}$\footnote{for $k$ being the numbers of iteration went through in the \inlinecode{while} loop.} will eventually reaches a condition where $x = y$ due to the ``well ordering'' nature of the natural numbers.
-Thus, the \inlinecode{while} loop always terminates.
-
-\subsection{(d)}
-
-In \textbf{Section 1.2}, we have proven that $gcd(x, y) = gcd(x-y, y)$ assuming $x > y$ for $x, y \in \mathbb{Z^+}$. Following the principle of induction, we can generalize it as:
-
-\begin{gather}
-    gcd(x_k, y_k) = gcd(x_{k+1}, y_{k+1}) \\
-    \text{for $x', y' \in \mathbb{Z^+}$,  while } \nonumber \\
-    \text{$x_{k+1} = x_{k} - y_{k}$, $y_{k+1} = y_{k}$ \ \ \  if $x_{k} > y_{k}$} \nonumber \\
-    \text{$y_{k+1} = y_{k} - x_{k}$, $x_{k+1} = x_{k}$ \ \ \  if $y_{k} > x_{k}$} \nonumber
-\end{gather}
-
-As we have proven in \textbf{Section 1.2}, that the \inlinecode{while} loop within the algorithm must terminate. Combined such finding with \textit{Equation 6}, we must also have a:
-\begin{gather}
-    gcd(a, b) = gcd(a_{k}, b_{k}) = gcd(a_{k+1}, b_{k+1}) = ... \\ ... = gcd(a_{k+n}, b_{k+n}) = gcd(a_{k+n}, a_{k+n}) \nonumber
-    % without loss of generality
-\end{gather}
-
-As we known by calculation that $gcd(a_{k+n}, a_{k+n}) = a_{k+n}$, thus, $a_{k+n}$ will be the greatest common divisor of $(a, b)$.
-As the induction performed in \textit{Equation 7} according to constraints defined in \textit{Equation 6} is an exact mathematical mimic of the iterations of the given \inlinecode{Euclidean} algorithm, we may conclude that \inlinecode{Euclidean(a, b)} returns $gcd(a, b)$.
 
 \section{Problem 2}
-\subsection{(a)}
-
-\begin{algorithm}
-\caption{TwoSum(A, B, n, x) with two pointers}\label{TwoSum}
-\begin{algorithmic}[1]
-\Procedure{}{}
-\State $j \gets n-1$
-\State $i \gets 0$
-\While {$i < n \textbf{ and } j \geq 0$}
-    \If {\textit{$A[i] + B[j] < x$}}
-        \State $i \gets i + 1$
-    \ElsIf {\textit{$A[i] + B[j] > x$}}
-        \State $j \gets j - 1$
-    \Else
-        \State \Return $i, j$
-    \EndIf
-\EndWhile
-\State \Return $False$
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-\newpage
-
-\subsection{(b)}
-
-The following is graphical demenstration of \inlinecode{TwoSum(A, B, 5, 12)}:
-\tikzset{
-mymat/.style={
-  matrix of math nodes,
-  text height=2.5ex,
-  text depth=0.75ex,
-  text width=3.25ex,
-  align=center,
-  column sep=-\pgflinewidth
-  },
-mymats/.style={
-  mymat,
-  nodes={draw,fill=#1}
-  }
-}
-
-\begin{tikzpicture}[>=latex]
-
-\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
-at (0,0)
-(mat1)
-{
-0 & 1 & 2(i) & 3 & 4 \\
-1 & 3 & 5 & 7 & 9 \\
-};
-
-\matrix[mymat,right=of mat1,row 2/.style={nodes={draw,fill=gray!30}}]
-at (10,0)
-(mat2)
-{
-0 & 1 & 2 & 3(j) & 4 \\
-2 & 4 & 6 & 7 & 10 \\
-};
-
-\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
-at (0,2)
-(mat3)
-{
-0 & 1(i) & 2 & 3 & 4 \\
-1 & 3 & 5 & 7 & 9 \\
-};
-\matrix[mymat,right=of mat3,row 2/.style={nodes={draw,fill=gray!30}}]
-at (10,2)
-(mat4)
-{
-0 & 1 & 2 & 3(j) & 4 \\
-2 & 4 & 6 & 7 & 10 \\
-};
-
-\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
-at (0,4)
-(mat5)
-{
-0 & 1(i) & 2 & 3 & 4 \\
-1 & 3 & 5 & 7 & 9 \\
-};
-\matrix[mymat,right=of mat5,row 2/.style={nodes={draw,fill=gray!30}}]
-at (10,4)
-(mat6)
-{
-0 & 1 & 2 & 3 & 4(j) \\
-2 & 4 & 6 & 7 & 10 \\
-};
-
-\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
-at (0,6)
-(mat7)
-{
-0(i) & 1 & 2 & 3 & 4 \\
-1 & 3 & 5 & 7 & 9 \\
-};
-\matrix[mymat,right=of mat7,row 2/.style={nodes={draw,fill=gray!30}}]
-at (10,6)
-(mat8)
-{
-0 & 1 & 2 & 3 & 4(j) \\
-2 & 4 & 6 & 7 & 10 \\
-};
-
-\node[above=0pt of mat7]
-  (cella) {A};
-\node[above=0pt of mat8]
-  (cellb) {B};
-
-\end{tikzpicture}\newline
-
-Thus we have $A[i] + B[j] = 12$ for $(i, j)$ being $(2, 3)$.
-
-\subsection{(c)}
-\subsubsection{Loop invariant}
-To enter the \inlinecode{while} loop with indexes $i, j$, it is impossible to have any combination of $(a, b)$ where $a \in \{A[0], A[1], ..., A[i-1]\}$ and $b \in \{B[j+1], B[j+2], ..., B[n-1]\}$ to be $a + b = x$.
-
-\subsubsection{Initialization}
-The loop invariant is held true during the initialization, since for $i = 0$ and $j = n-1$, we must have $a = \emptyset$ and $b = \emptyset$.
-Thus, it is impossible to have a combination of $(a, b)$ to be $a + b = x$.
-
-\subsubsection{Maintenance}
-
-Due to the sorted nature of array $A, B$, we must have:
-
-\begin{gather}
-    \underbrace{A[0] \leq A[1] \leq ... \leq A[i-1]}_{a} \leq A[i]  \ \ \ \Rightarrow a \leq A[i]\\
-    \underbrace{B[n-1] \geq ... \geq B[j+2] \geq B[j+1]}_{b} \geq B[j] \ \ \ \Rightarrow b \geq B[j]
-\end{gather}
-
-Assume we get $A[i] + B[j] = k$ within an iteration of the \inlinecode{while} loop, we either have $k < x$ or $k > x$.
-In both cases, we may confidently say that there will be no $a + b = k$; as the index of $a$ must be smaller than $i$ and the index of $b$ must be greater than $j$.
-Thus, if there is any $a + b = x$, such loop would have been terminated immediately and we should not be able to reach to indexes $i, j$ in the \inlinecode{while} loop.
-Therefore, as we are now at the $i, j$ iteration of the \inlinecode{while} loop, this suggests there is no $(a, b)$ combination where $a + b = x$.
-By this, the loop invariant is held true for all cases within the \inlinecode{while} loop.\newline
-
-Then, to proceed the loop, we may infer the following from \textit{Equation 8} and \textit{9}:
-
-\begin{gather}
-    \text{if } k < x: \ a + B[j] \leq A[i] + B[j] = k  \ \ \ \Rightarrow a + B[j] < x\\
-    \text{if } k > x: \ A[i] + b \geq A[i] + B[j] = k  \ \ \ \Rightarrow A[i] + b > x
-\end{gather}
-
-As there is no $(a, b)$ combination available to form $a+b = x$, we must increse the value of index $i$ in the case of $k < x$ to achieve a hopefully greather $k'$ in the next interation; and similarly, to decrese the value of index $j$ to achieve a hopefully lesser $k'$ in the case of $k > x$.
-Thus, the conditional statements in the pseudocode in \textbf{Section 2.1} are justified, and the algorithm is proven to be correct.
-
-\subsection{(d)}
-The worst case of this algorithm is when it returns \inlinecode{False}.
-In such case we will have $i$ and $j$ traveling the entire bound of $\mathbb{Z^+} \in [0, n)$.
-The loop will execute $2n$ times, thus the run time is $\Theta(n)$.
-
-\section{Problem 3}
-\subsection{Describe the process using a loop: Pseudocode}
-
-% l = red, p = black
-\begin{algorithm}
-\caption{Kepler442b(m, n)}\label{Kepler442b}
-\begin{algorithmic}[1]
-\Procedure{}{}
-\State $l \gets m$
-\State $p \gets n$
-\While {$(l + p) > 1$}
-    \State \text{Let two individuals fight each other.}
-    \If {\text{Both individuals are Lydians}}
-        \State $l \gets l - 1$
-    \ElsIf {\text{Both individuals are Pisidians}}
-        \State $p \gets p - 2$
-        \State $l \gets l + 1$
-    \Else
-        \State $l \gets l - 1$
-    \EndIf
-\EndWhile
-\State \Return $l, p$
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Define loop invariant and termination}
-At the start of the $k^{th}$ iteration of the \inlinecode{while} loop, we must have
-\begin{gather}
-    l + p = m + n - (k - 1) \\
-    p\bmod 2 = n \bmod 2
-\end{gather}
-
-When the \inlinecode{while} loop terminates at $l + p = 1$ there can only be two cases:
-\begin{gather}
-    l = 1, \ p = 0 \ \ (n \bmod 2 = 0) \\
-    l = 0, \ p = 1 \ \ (n \bmod 2 = 1)
-\end{gather}
-
-Thus, we may infer that if $n$ is odd, a \textit{Pisidian} shall remain. Otherwise if $n$ is even, a \textit{Lydian} shall remain.
-
-\subsection{Proof of loop invariant}
-\subsubsection{Initialization}
-At the beginning it is known that $k = 1$ and $b = n$, thus we may have:
-
-\begin{gather}
-    l + p = m + n - (k - 1) = l + p = m + n - (1 - 1) \Rightarrow l + p = m + n \\
-    p\bmod 2 = n \bmod 2
-\end{gather}
-
-As the above two \textit{Equations} satisfy the assumption of the loop invariant, we may say that the scenario of $k = 1$ is true.
-
-\subsubsection{Maintenance}
-
-\paragraph{Case 1} As it is known that $l + p = (l - 1) + p$ and $k = k + 1$, we may conclude that $l + p + k$ must remain the same.
-
-\paragraph{Case 2} As it is known that $l + p = (l + 1) + (p - 2)$ and $k = k + 1$, we may conclude that $l + p + k$ must remain the same.
-
-\paragraph{Case 3} As it is known that $l + p = (l - 1) + p$ and $k = k + 1$, we may conclude that $l + p + k$ must remain the same.
-
-As all three cases satisfy the loop invariant of the algorithm, the induction is therefore proven to be valid.
 

### 2020-02-02 assignment_2/article.tex
✨ Add sketch answer to Problem 1(a).
✨ Add sketch answers to Problem 1(b1) and (b2).

@@
 
+\makeatletter
+\renewcommand{\@seccntformat}[1]{}
+\makeatother
+
 \begin{document}
@@
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(a) $max\{f(n), g(n)\} = \Theta (f(n) + g(n))$}
+
+Since it is known that $f(n) \geq 0$, $g(n) \geq 0$, and $c > 0$; we must have:
+
+\begin{gather}
+    f(n) \leq f(n) + g(n) \nonumber\\
+    g(n) \leq f(n) + g(n) \nonumber\\
+    \Rightarrow \max(f(n), g(n)) \in O(f(n) + g(n)) \ \ \ \text{for } \begin{cases}
+                    c = 1 \\
+                    \forall{n_{0}} \in \mathbb{R}
+                \end{cases}
+\end{gather}
+
+Since it is also known that $f(n) + g(n) \leq 2 \cdot \max(f(n),g(n))$, we may therefore infer:
+
+\begin{gather}
+    \max(f(n), g(n)) \in \Omega(f(n) + g(n)) \ \ \ \text{for } \begin{cases}
+        c = \frac{1}{2} \\
+        \forall{n_{0}} \in \mathbb{R}
+    \end{cases}
+\end{gather}
+
+Since both the $O$- and $\Omega$-notation are established, we may therefore conclude:
+
+\begin{gather}
+    \max(f(n), g(n)) \in \Theta (f(n) + g(n))
+\end{gather}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(b1) $f(n) + d = O(f(n))$.}
+
+For the seek of disambiguation, we rewrite the questioned equation as $f(n) + d = O(f(n))$ by $d$ replacing $c$ for $d > 0$.
+
+According to the defination of $O$-notation, we have:
+
+\begin{gather}
+    f(n) = O(f(n)) \nonumber\\
+    \exists c, n_{0} > 0 \ \text{ s.t.  $0 \leq f(n) \leq cf(n)$ \ \ \ for $n \geq n_{0}$} \\
+    \exists n' > 0 \ \text{ s.t.  $f(n) \geq f(n')$ \ \ \ for $n, n' \geq n_{0}$} \\
+    \Rightarrow 0 \leq f(n)+d \leq cf(n) + d \ \ \ \text{for $n \geq n_{0}$}
+\end{gather}
+
+Due to \textit{Equation 5}, we may rewrite \textit{Euqation 6} as:
+
+\begin{gather}
+    0 \leq f(n)+d \leq (c + \frac{d}{f(n)})f(n) \nonmumber\\
+    \Rightarrow 0 \leq f(n)+d \ \leq \ c'f(n) \ \ \ \text{for } \begin{cases}
+                    c' = c + \frac{d}{f(n')} \\
+                    n, n' \geq n_{0}
+                \end{cases}
+\end{gather}
+
+Based \textit{Euqation 8}, we may conclude $f(n) + d = O(f(n))$ via direct proof.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(b2) If $f(n) \geq 1$, then $f(n) + c = O(f(n))$.}
+
+Please refer to proof at \textbf{b1} as it provides a broader proof base on $f(n)$ regardless $f(n) \geq 1$ or not.
 \section{Problem 2}

### 2020-02-02 assignment_2/article.tex
✨ Add sketch answer to Problem 1(c1).

@@
 Please refer to proof at \textbf{b1} as it provides a broader proof base on $f(n)$ regardless $f(n) \geq 1$ or not.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(c1) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 0$, then $log(f(n)) = O(\log(g(n))$.}
+
+According to the defination of $O$-notation, we must have:
+
+\begin{gather}
+    \exists c, n_{0} > 0 \ \text{ s.t. } \ f(n) \leq cg(n) \ \ \ \text{for $n \geq n_{0}$}
+\end{gather}
+
+Since it is given that $\log(f(n)), \log(g(n)) \geq 0$, thus we must have:
+
+\begin{gather}
+    \log(f(n)) \leq \log(c(g(n))) \ \ \ \text{for $n \geq n_{0}$} \nonumber\\
+    \Rightarrow \log(f(n)) \leq \log c + \log(g(n)) \ \ \ \text{for $n \geq n_{0}$}
+\end{gather}
+
+As $c, n_{0}$ are constants, there must be a constant $c'$ s.t.
+
+\paragraph{Case 1} Assume $\log (g(n_{0})) \neq 0$:
+
+\begin{gather}
+    c' \geq \frac{\log c}{\log (g(n_{0}))} + 1 \\
+    \Rightarrow (c' -1)\log (g(n))  \ \geq \ (c' -1)\log (g(n_{0})) \ \geq \ \log c \ \ \ \text{for $n \geq n_{0}$} \\
+    \exists c, n_{0} > 0 \nonumber \ \text{ s.t. } \  \\
+    \log(f(n)) \ \leq \ \log c + \log(g(n)) \ \leq \  (c' -1)\log (g(n)) + \log(g(n))\ \ \ \text{for $n \geq n_{0}$} \\
+    \Rightarrow \log(f(n))  \leq c'\log (g(n))
+\end{gather}
+
+Thus we may conclude $log(f(n)) = O(\log(g(n))$ for this case.
+
+\paragraph{Case 2} Assume $\log (g(n_{0})) = 0$:
+
+Since $\log (g(n_{0})) = 0$, we shall infer that $g(n_{0}) = 1$. We may arbitrarily pick some constants $c, c'}$ where:
+
+\begin{gather}
+    \log c \leq 0 \nonumber\\
+    \log c \leq (c' - 1) \cdot 0 \nonumber\\
+    \log c \leq (c' - 1) \cdot \log(g(n_{0}))
+\end{gather}
+
+Since $n \geq n_{0}$ by defination, and known that $g(n) \geq 1$ due to $\log(g(n)) \geq 0$; therefore there must be $g(n) \geq g(n_{0})$.
+Putting this into the context of \textit{Equation 10}, we may have:
+
+\begin{gather}
+    \log(f(n)) \leq \log c + \log(g(n)) \ \ \ \text{for $n \geq n_{0}$} \nonumber \\
+    \Rightarrow \log(f(n)) \leq (c' - 1) \cdot \log(g(n_{0})) + \log(g(n)) \nonumber \\
+    \Rightarrow \log(f(n)) \leq (c' - 1) \cdot \log(g(n)) + \log(g(n)) \nonumber \\
+    \Rightarrow \log(f(n)) \leq c'\log(g(n))
+\end{gather}
+
+Thus we may conclude $log(f(n)) = O(\log(g(n))$ for this case.\newline
+
+Since both cases reach to the conclusion of $log(f(n)) = O(\log(g(n))$, we have proven the statement to be valid.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(c2) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 1$, then $log(f(n)) = O(\log(g(n))$.}
+
 \section{Problem 2}

### 2020-02-02 assignment_2/article.tex
✨ Add sketch answer to Problem 1(c2), a narrower version of (c1).
✨ Add sketch answer to Problem 1(d1).

@@
 
+According to the defination of $O$-notation, we must have:
+
+\begin{gather}
+    \exists c, n_{0} > 0 \ \text{ s.t. } \ f(n) \leq cg(n) \ \ \ \text{for $n \geq n_{0}$}
+\end{gather}
+
+Since it is given that $\log(f(n))\geq 0$, $\log(g(n)) \geq 1 $, thus we must have:
+
+\begin{gather}
+    \log(f(n)) \leq \log(c(g(n))) \ \ \ \text{for $n \geq n_{0}$} \nonumber\\
+    \Rightarrow \log(f(n)) \leq \log c + \log(g(n)) \ \ \ \text{for $n \geq n_{0}$}
+\end{gather}
+
+As $c, n_{0}$ are constants, there must be a constant $c'$ s.t.
+
+\begin{gather}
+    c' \geq \frac{\log c}{\log (g(n_{0}))} + 1 \\
+    \Rightarrow (c' -1)\log (g(n))  \ \geq \ (c' -1)\log (g(n_{0})) \ \geq \ \log c \ \ \ \text{for $n \geq n_{0}$} \\
+    \exists c, n_{0} > 0 \nonumber \ \text{ s.t. } \  \\
+    \log(f(n)) \ \leq \ \log c + \log(g(n)) \ \leq \  (c' -1)\log (g(n)) + \log(g(n))\ \ \ \text{for $n \geq n_{0}$} \\
+    \Rightarrow \log(f(n))  \leq c'\log (g(n))
+\end{gather}
+
+Thus we may conclude $log(f(n)) = O(\log(g(n))$, the statement is therefore proven to be valid.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(d1) $f(2n) = \Theta(f(n))$}
+
+Since it is known that $f(n) \geq 0$, $g(n) \geq 0$, and $c > 0$; we must have a constant $c' > 0$ which satisfy:
+
+\paragraph{Case 1} Assume $f(n) \neq 0$.
+
+\begin{gather}
+    c' \geq \frac{f(2n)}{f(n)} \\
+    \Rightarrow f(2n) \leq c'(f(n))
+\end{gather}
+
+Thus we may conclude $f(2n) = O(f(n))$.
+
+Similarly, we may also have a constant $c'' > 0$ which satisfy:
+
+\begin{gather}
+    c'' \leq \frac{f(2n)}{f(n)} \\
+    \Rightarrow f(2n) \geq c''(f(n))
+\end{gather}
+
+Thus we may conclude $f(2n) = \Omega(f(n))$.\newline
+
+Since both the $O$- and $\Omega$-notation are established, we may therefore conclude $f(2n) = \Theta(f(n))$ in this case.
+
+\paragraph{Case 1} Assume $f(n) = 0$ for $\all n$.
+
+Thus we must have two constants $k_{1}, k_{2}$ which satisfy:
+\begin{gather}
+    f(2n) = 0 \\
+    k_{1}(0) \leq f(2n) \leq k_{2}f(n)\Rightarrow k_{1}(0) \leq 0 \leq k_{2}(0), \ \forall k \in \mathbb{R^+}
+\end{gather}
+
+Thus we may conclude $f(2n) = \Theta(f(n))$.\newline
+
+Since both cases reach to the conclusion of $f(2n) = \Theta(f(n))$, we have proven the statement to be valid.
+
 \section{Problem 2}

### 2020-02-02 assignment_2/article.tex
✨ Add sketch answer to Problem 1(d2) and (d3).

@@
 
+\subsection{(d2) If $f(n) = O(n^c)$, then $f(2n) = O(n^c)$}
+
+As It is known from \textbf{d1} that $f(2n) = \Theta(f(n))$, which implies $f(2n) = O(f(n))$.
+Also it is given that $f(n) = O(n^c)$.
+Together, we shall infer $f(2n) = O(n^c)$ due to the transitivity property of $\Theta$- and $O$-notations.
+
+\subsection{(d3) If $f(n) = \Theta(n^c)$, then $f(2n) = \Theta(f(n))$}
+Please refer to proof at \textbf{d3} as it provides a broader proof base on $f(n)$ regardless $f(n) = \Theta(n^c)$ or not.
+
 \section{Problem 2}

### 2020-02-03 assignment_2/article.tex
✨ Add sketch answer to Problem 2.
Co-Authored-By: bobbyCZT <zxc325@users.noreply.github.com>
✨ Add sketch justifications for answer of Problem 2.
Co-Authored-By: bobbyCZT <zxc325@users.noreply.github.com>

@@
 
-Since $\log (g(n_{0})) = 0$, we shall infer that $g(n_{0}) = 1$. We may arbitrarily pick some constants $c, c'}$ where:
+Since $\log (g(n_{0})) = 0$, we shall infer that $g(n_{0}) = 1$. We may arbitrarily pick some constants $c, c'$ where:
 
@@
 
+\paragraph{Answer}
+
+\begin{gather}
+    \frac{1}{n^a} \ll \frac{1}{n^\epsilon} \ll \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $0 < \epsilon < \frac{1}{2}$)} \ll \log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \\
+    \equiv \log(n^b) \leq \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $\epsilon \geq \frac{1}{2}$)} \ll (\log n)^a \ll n^{\epsilon} \\
+    \ll a^{\log_a(n)} \equiv \epsilon n \equiv \frac{n}{a} \ll n^a \equiv (n+b)^a\\
+    \ll (n+a)^b \ll n^{a+b} \ll \epsilon^n \ll a^{\epsilon n} \equiv a^n \ll b^n
+\end{gather}
+
+\paragraph{Justification of $\log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \equiv \log(n^b)$\newline}
+
+The above equations can be rewrite as:
+
+\begin{gather}
+    \log(n^\epsilon) = \epsilon \log(n) \\
+    \log(n^a) = a \log(n) \\
+    \log(bn) = \log(b) + \log(n) \\
+    \log(n^b) = b \log(n)
+\end{gather}
+
+Where all of them can be generalized as $\Theta(\log(n))$, as it is known that $n^\epsilon \leq bn \leq n^a$ due to the decending of \textit{power(s)}.
+
+\paragraph{Justification of $ \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $0 < \epsilon < \frac{1}{2}$)} \equiv \log(n^b) \leq \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $\epsilon \geq \frac{1}{2}$)}$\newline}
+
+It is known that when $\epsilon < \frac{1}{2} \Rightarrow \frac{1}{\epsilon} \geq 2$; when $\epsilon \geq \frac{1}{2} \Rightarrow  \frac{1}{\epsilon} \leq 2$.
+Since it is observable that $\log_{x}(n) \gg \log_{x'}(n)$ for $x < x'$, such (in)equaility is valid.
+
+\paragraph{Justification of $a^{\log_a(n)} \equiv \epsilon n \equiv \frac{n}{a}$\newline}
+
+The above equations can be rewrite as:
+\begin{gather}
+    a^{\log_a(n)} = n^1 = \Theta(n) \\
+    \epsilon n = \Theta(n) \\
+    frac{n}{a} = \frac{1}{a}n =  \Theta(n)
+\end{gather}
+
+Thus, the above equality is justified.
+
+\paragraph{Justification of $a^{\epsilon n} \equiv a^n$\newline}
+
+We may rewrite $a^{\epsilon n}$ as the following, since there must be a $c$ for $c \in \mathbb{R^+}$ which satisfy the equality.
+
+\begin{gather}
+    a^{\epsilon} \cdot a^n = c \cdot a^n = \Theta(a^n)
+\end{gather}
+
+Since it is known that $a^n = \Theta(a^n)$, these two expressions are considered equivalent.
+
 % \section{References}

### 2020-02-03 assignment_2/article.tex
🐛 Correct Problem 1(b1).

@@
 
+\textbf{False}
+
 For the seek of disambiguation, we rewrite the questioned equation as $f(n) + d = O(f(n))$ by $d$ replacing $c$ for $d > 0$.
 
-According to the defination of $O$-notation, we have:
+To prove the statement to be valid, we need to show:
 
 \begin{gather}
-    f(n) = O(f(n)) \nonumber\\
-    \exists c, n_{0} > 0 \ \text{ s.t.  $0 \leq f(n) \leq cf(n)$ \ \ \ for $n \geq n_{0}$} \\
-    \exists n' > 0 \ \text{ s.t.  $f(n) \geq f(n')$ \ \ \ for $n, n' \geq n_{0}$} \\
-    \Rightarrow 0 \leq f(n)+d \leq cf(n) + d \ \ \ \text{for $n \geq n_{0}$}
+    0 \leq f(n) + d \leq cf(n)
 \end{gather}
 
-Due to \textit{Equation 5}, we may rewrite \textit{Euqation 6} as:
+For $f(n) = 0$, we cannot find any $c$ which satisfies the above equation since:
 
 \begin{gather}
-    0 \leq f(n)+d \leq (c + \frac{d}{f(n)})f(n) \nonmumber\\
-    \Rightarrow 0 \leq f(n)+d \ \leq \ c'f(n) \ \ \ \text{for } \begin{cases}
-                    c' = c + \frac{d}{f(n')} \\
-                    n, n' \geq n_{0}
-                \end{cases}
+    O(f(n)) = cf(n) = 0  \nonumber \\
+    \Rightarrow 0 \leq 0 + d \leq c(0) \ \ \ \text{for $d > 0$}
 \end{gather}
 
-Based \textit{Euqation 8}, we may conclude $f(n) + d = O(f(n))$ via direct proof.
+As the equation $0 + d \leq 0$ leads to a contradiction, the statement is invalid.
 

### 2020-02-03 assignment_2/article.tex
🐛 Correct Problem 1(b2).
🐛 Correct Problem 1(d1).

@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(b2) If $f(n) \geq 1$, then $f(n) + c = O(f(n))$.}
+\subsection{(b2) If $f(n) \geq 1$, then $f(n) + d = O(f(n))$.}
 
-Please refer to proof at \textbf{b1} as it provides a broader proof base on $f(n)$ regardless $f(n) \geq 1$ or not.
+For the seek of disambiguation, we rewrite the questioned equation as $f(n) + d = O(f(n))$ by $d$ replacing $c$ for $d > 0$.
+
+According to the defination of $O$-notation, we have:
+
+\begin{gather}
+ f(n) = O(f(n)) \nonumber\\
+ \exists c, n_{0} > 0 \ \text{ s.t.  $0 \leq f(n) \leq cf(n)$ \ \ \ for $n \geq n_{0}$} \\
+ \exists n' > 0 \ \text{ s.t.  $f(n) \geq f(n')$ \ \ \ for $n, n' \geq n_{0}$} \\
+ \Rightarrow 0 \leq f(n)+d \leq cf(n) + d \ \ \ \text{for $n \geq n_{0}$}
+\end{gather}
+
+Thus, we may rewrite the above equation as:
+
+\begin{gather}
+ 0 \leq f(n)+d \leq (c + \frac{d}{f(n)})f(n) \ \ \ \text{for $f(n) \geq 1$} \nonmumber\\
+ \Rightarrow 0 \leq f(n)+d \ \leq \ c'f(n) \ \ \ \text{for } \begin{cases}
+                 c' = c + \frac{d}{f(n')} \\
+                 n, n' \geq n_{0}
+             \end{cases}
+\end{gather}
+
+Therefore, we may conclude if $f(n) \geq 1$, then $f(n) + d = O(f(n))$ via direct proof.
 
@@
 Since $n \geq n_{0}$ by defination, and known that $g(n) \geq 1$ due to $\log(g(n)) \geq 0$; therefore there must be $g(n) \geq g(n_{0})$.
-Putting this into the context of \textit{Equation 10}, we may have:
+Putting this into the context of \textit{Equation 12}, we may have:
 
@@
 
-Since it is known that $f(n) \geq 0$, $g(n) \geq 0$, and $c > 0$; we must have a constant $c' > 0$ which satisfy:
+\textbf{False}
 
-\paragraph{Case 1} Assume $f(n) \neq 0$.
+For $f(n) = 2^n$, we have $f(2n) = 4^n$.
+Where $f(2n) \neq \Theta(f(n))$ due to the LHS has a higher asymptotic order, and therefore we can't find any constant $c_{1}, c_{2}$ to form a relation of $c_1 \cdot 2^n \leq 4^n \leq c_2 \cdot 2^n$.
+Thus, the statement is invalid.
 
-\begin{gather}
-    c' \geq \frac{f(2n)}{f(n)} \\
-    \Rightarrow f(2n) \leq c'(f(n))
-\end{gather}
-
-Thus we may conclude $f(2n) = O(f(n))$.
-
-Similarly, we may also have a constant $c'' > 0$ which satisfy:
-
-\begin{gather}
-    c'' \leq \frac{f(2n)}{f(n)} \\
-    \Rightarrow f(2n) \geq c''(f(n))
-\end{gather}
-
-Thus we may conclude $f(2n) = \Omega(f(n))$.\newline
-
-Since both the $O$- and $\Omega$-notation are established, we may therefore conclude $f(2n) = \Theta(f(n))$ in this case.
-
-\paragraph{Case 1} Assume $f(n) = 0$ for $\all n$.
-
-Thus we must have two constants $k_{1}, k_{2}$ which satisfy:
-\begin{gather}
-    f(2n) = 0 \\
-    k_{1}(0) \leq f(2n) \leq k_{2}f(n)\Rightarrow k_{1}(0) \leq 0 \leq k_{2}(0), \ \forall k \in \mathbb{R^+}
-\end{gather}
-
-Thus we may conclude $f(2n) = \Theta(f(n))$.\newline
-
-Since both cases reach to the conclusion of $f(2n) = \Theta(f(n))$, we have proven the statement to be valid.
-
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \subsection{(d2) If $f(n) = O(n^c)$, then $f(2n) = O(n^c)$}
@@
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \subsection{(d3) If $f(n) = \Theta(n^c)$, then $f(2n) = \Theta(f(n))$}

### 2020-02-03 assignment_2/article.tex
🐛 Correct Problem 1(d2).

@@
 Since $n \geq n_{0}$ by defination, and known that $g(n) \geq 1$ due to $\log(g(n)) \geq 0$; therefore there must be $g(n) \geq g(n_{0})$.
-Putting this into the context of \textit{Equation 12}, we may have:
+Putting this into the context of problem statement, we may have:
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(d2) If $f(n) = O(n^c)$, then $f(2n) = O(n^c)$}
+\subsection{(d2) If $f(n) = O(n^k)$, then $f(2n) = O(n^k)$}
 
-As It is known from \textbf{d1} that $f(2n) = \Theta(f(n))$, which implies $f(2n) = O(f(n))$.
-Also it is given that $f(n) = O(n^c)$.
-Together, we shall infer $f(2n) = O(n^c)$ due to the transitivity property of $\Theta$- and $O$-notations.
+For the seek of disambiguation, we rewrite the questioned equation as: if $f(n) = O(n^k)$, then $f(2n) = O(n^k)$ by $k$ replacing $c$ for $k > 0$.
+
+Since $f(n) = O(n^k)$, we must have $0 \leq f(n) \leq cn^k$ for $n \geq n_0$ and a $c$ for $c \in \mathbb{R^+}$. Now substitute $n$ as $2n$, we may have:
+
+\begin{gather}
+    0 \leq f(2n) \leq c(2n)^k \nonumber \\
+    \Rightarrow 0 \leq f(2n) \leq c\cdot (2)^k \cdot n^k \\
+    \Rightarrow 0 \leq f(2n) \leq c' \cdot n^k \ \ \ \text{where $c' = c\cdot (2)^k$}
+\end{gather}
+
+Thus we may conclude if $f(n) = O(n^k)$, then $f(2n) = O(n^k)$.
 

### 2020-02-03 assignment_2/article.tex
🐛 Correct Problem 1(d3).

@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(d3) If $f(n) = \Theta(n^c)$, then $f(2n) = \Theta(f(n))$}
-Please refer to proof at \textbf{d3} as it provides a broader proof base on $f(n)$ regardless $f(n) = \Theta(n^c)$ or not.
+\subsection{(d3) If $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$}
+
+For the seek of disambiguation, we rewrite the questioned equation as: if $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$.
+
+Since $f(n) = \Theta(n^k)$, we must have $0 \leq c_1 \cdot n^k \leq f(n) \leq c_2 \cdot n^k$ for $n \geq n_0$ and $c_1, c_2$ for $c_1, c_2 \in \mathbb{R^+}$. Now substitute $n$ as $2n$, we may have:
+
+\begin{gather}
+    0 \leq c_1 (2n)^k \leq f(2n) \leq c_2 (2n)^k \nonumber \\
+    \Rightarrow 0 \leq c_1 \cdot 2^k \cdot n^k \leq f(2n) \leq c_2 \cdot 2^k \cdot n^k
+\end{gather}
+
+From $0 \leq c_1 \cdot n^k \leq f(n) \leq c_2 \cdot n^k$ , we may also infer:
+
+\begin{gather}
+    \frac{f(n)}{c_1} \geq k \geq \frac{f(n)}{c_2} \\
+    \Rightarrow c_1 \cdot 2^k \cdot \frac{f(n)}{c_2} \leq f(2n) \leq c_2 \cdot 2^k \cdot \frac{f(n)}{c_1} \\
+    \Rightarrow 0\leq c^{'}_{1}\cdot f(n) \leq f(2n) \leq c^{'}_{2}\cdot f(2n) \ \ \ \text{for}\begin{cases}
+                    c^{'}_{1} = \frac{c_1 \cdot 2^k}{c_2} \\
+                    c^{'}_{2} = \frac{c_2 \cdot 2^k}{c_1}
+                \end{cases}
+\end{gather}
+
+Thus we may conclude if $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$.
 

### 2020-02-03 assignment_2/article.tex
🐛 Correct Problem 1(c1) with a lot of work goes to nothing :\ .

@@
 
-According to the defination of $O$-notation, we must have:
+\textbf{False}
+
+For $f(n) = 2$ and $g(n) = 1$, then $\log f(n) = 1$ and $\log g(n) = 0$. Since we cannot find any constant $c$ where:
 
 \begin{gather}
-    \exists c, n_{0} > 0 \ \text{ s.t. } \ f(n) \leq cg(n) \ \ \ \text{for $n \geq n_{0}$}
+    0 \leq 1 \leq c(0)
 \end{gather}
 
-Since it is given that $\log(f(n)), \log(g(n)) \geq 0$, thus we must have:
-
-\begin{gather}
-    \log(f(n)) \leq \log(c(g(n))) \ \ \ \text{for $n \geq n_{0}$} \nonumber\\
-    \Rightarrow \log(f(n)) \leq \log c + \log(g(n)) \ \ \ \text{for $n \geq n_{0}$}
-\end{gather}
-
-As $c, n_{0}$ are constants, there must be a constant $c'$ s.t.
-
-\paragraph{Case 1} Assume $\log (g(n_{0})) \neq 0$:
-
-\begin{gather}
-    c' \geq \frac{\log c}{\log (g(n_{0}))} + 1 \\
-    \Rightarrow (c' -1)\log (g(n))  \ \geq \ (c' -1)\log (g(n_{0})) \ \geq \ \log c \ \ \ \text{for $n \geq n_{0}$} \\
-    \exists c, n_{0} > 0 \nonumber \ \text{ s.t. } \  \\
-    \log(f(n)) \ \leq \ \log c + \log(g(n)) \ \leq \  (c' -1)\log (g(n)) + \log(g(n))\ \ \ \text{for $n \geq n_{0}$} \\
-    \Rightarrow \log(f(n))  \leq c'\log (g(n))
-\end{gather}
-
-Thus we may conclude $log(f(n)) = O(\log(g(n))$ for this case.
-
-\paragraph{Case 2} Assume $\log (g(n_{0})) = 0$:
-
-Since $\log (g(n_{0})) = 0$, we shall infer that $g(n_{0}) = 1$. We may arbitrarily pick some constants $c, c'$ where:
-
-\begin{gather}
-    \log c \leq 0 \nonumber\\
-    \log c \leq (c' - 1) \cdot 0 \nonumber\\
-    \log c \leq (c' - 1) \cdot \log(g(n_{0}))
-\end{gather}
-
-Since $n \geq n_{0}$ by defination, and known that $g(n) \geq 1$ due to $\log(g(n)) \geq 0$; therefore there must be $g(n) \geq g(n_{0})$.
-Putting this into the context of problem statement, we may have:
-
-\begin{gather}
-    \log(f(n)) \leq \log c + \log(g(n)) \ \ \ \text{for $n \geq n_{0}$} \nonumber \\
-    \Rightarrow \log(f(n)) \leq (c' - 1) \cdot \log(g(n_{0})) + \log(g(n)) \nonumber \\
-    \Rightarrow \log(f(n)) \leq (c' - 1) \cdot \log(g(n)) + \log(g(n)) \nonumber \\
-    \Rightarrow \log(f(n)) \leq c'\log(g(n))
-\end{gather}
-
-Thus we may conclude $log(f(n)) = O(\log(g(n))$ for this case.\newline
-
-Since both cases reach to the conclusion of $log(f(n)) = O(\log(g(n))$, we have proven the statement to be valid.
+Thus the statement is invalid.
 

### 2020-02-04 assignment_2/article.tex
🐛 Correct Problem 2 conclusion.
🔨 Update Problem 2 justifications i.c.w. the corrected conclusion.

@@
 
-\paragraph{Answer}
+\subsection{Conclusion}
 
 \begin{gather}
-    \frac{1}{n^a} \ll \frac{1}{n^\epsilon} \ll \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $0 < \epsilon < \frac{1}{2}$)} \ll \log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \\
-    \equiv \log(n^b) \leq \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $\epsilon \geq \frac{1}{2}$)} \ll (\log n)^a \ll n^{\epsilon} \\
-    \ll a^{\log_a(n)} \equiv \epsilon n \equiv \frac{n}{a} \ll n^a \equiv (n+b)^a\\
-    \ll (n+a)^b \ll n^{a+b} \ll \epsilon^n \ll a^{\epsilon n} \equiv a^n \ll b^n
+     n^{-a} \ll n^{-\epsilon} \ll \epsilon^n  \\
+    \ll \log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \equiv \log(n^b) \equiv \log_{\frac{1}{\epsilon}}(n)\\
+    \ll  (\log n)^a \ll n^{\epsilon} \ll a^{\log_a(n)} \\
+    \equiv \epsilon n \equiv \frac{n}{a} \\
+    \ll n^a \equiv (n+b)^a \ll (n+a)^b \ll n^{a+b} \\
+    \ll a^{\epsilon n} \equiv a^n \ll b^n
 \end{gather}
 
-\paragraph{Justification of $\log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \equiv \log(n^b)$\newline}
+\subsection{Justifications}
+
+\paragraph{Justification of $n^{-a} \ll n^{-\epsilon} \ll \epsilon^n$\newline}
+
+\begin{gather}
+    \lim\limits_{n \to \infty} \frac{\epsilon^n}{n^{-\epsilon}} = \lim\limits_{n \to \infty} \frac{n\log \epsilon}{-\epsilon \log n} = \lim\limits_{n \to \infty} \frac{\log \epsilon}{-\epsilon} \cdot \frac{n}{\log n} \\
+    \text{Since } \epsilon \in (0, 1) \Rightarrow \log \epsilon < 0 \Rightarrow \frac{\log \epsilon}{\epsilon} > 0 \nonumber\\
+    \lim\limits_{n \to \infty} \frac{\epsilon^n}{n^{-\epsilon}} = \lim\limits_{n \to \infty} c \cdot \frac{n}{\log n} = \infty \\
+    \Rightarrow \epsilon^n \gg n^{-\epsilon}
+\end{gather}
+
+\begin{gather}
+    \text{Since } 0 < \epsilon < 1 < a \\
+    \lim\limits_{n \to \infty} \frac{n^{-a}}{n^{-\epsilon}} = \lim\limits_{n \to \infty} n^{\epsilon - a} = 0 \\
+    \Longrightarrow n^{-a} \ll n^{-\epsilon}
+\end{gather}
+
+Combine the above two set of equations together, we have $n^{-a} \ll n^{-\epsilon} \ll \epsilon^n$.
+
+\paragraph{Justification of $\epsilon^n \ll \log(n^\epsilon)$\newline}
+
+Since $\lim\limits_{n \to \infty} \epsilon^n = 0$, where $0 < 1 < \log(n^\epsilon)$, we may say the above inequality if true.
+
+\paragraph{Justification of $\log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \equiv \log(n^b) \equiv \log_{\frac{1}{\epsilon}}(n)$\newline}
 
@@
     \log(bn) = \log(b) + \log(n) \\
-    \log(n^b) = b \log(n)
+    \log(n^b) = b \log(n) \\
 \end{gather}
@@
 
-\paragraph{Justification of $ \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $0 < \epsilon < \frac{1}{2}$)} \equiv \log(n^b) \leq \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $\epsilon \geq \frac{1}{2}$)}$\newline}
+The relationship of the above expressions with $\log_{\frac{1}{\epsilon}}(n)$ can be a bit unintuitive, we may show they are considered equivalent with:
+\begin{gather}
+    \lim\limits_{n \to \infty} \frac{\log(n^\epsilon)}{\log_{\frac{1}{\epsilon}}(n)} = \lim\limits_{n \to \infty} \frac{\epsilon \log_{2}n}{\frac{\log_{2}n}{\log_{2}(\frac{1}{\epsilon})}} = \lim\limits_{n \to \infty} \epsilon \log_2(\frac{1}{\epsilon}) = c \nonumber\\
+    \Rightarrow \log(n^\epsilon) \equiv \log_{\frac{1}{\epsilon}}(n)
+\end{gather}
 
-It is known that when $\epsilon < \frac{1}{2} \Rightarrow \frac{1}{\epsilon} \geq 2$; when $\epsilon \geq \frac{1}{2} \Rightarrow  \frac{1}{\epsilon} \leq 2$.
-Since it is observable that $\log_{x}(n) \gg \log_{x'}(n)$ for $x < x'$, such (in)equaility is valid.
+\paragraph{Justification of $ \log(n)\ll  (\log (n))^a $\newline}
+\begin{gather}
+    \lim\limits_{n \to \infty} \frac{(\log (n))^a}{\log (n)} = \lim\limits_{n \to \infty} (\log(n))^{a-1} = \infty \nonumber \\
+    \Rightarrow  \log(n)\ll  (\log (n))^a
+\end{gather}
+
+Considered $ \log(n)$ is a generalized form of the perivous group of functions,  $(\log (n))^a$ is proven to be greater than the perivous group.
+
+\paragraph{Justification of $  (\log n)^a \ll n^{\epsilon} \ll a^{\log_a(n)}$\newline}
+
+\begin{gather}
+    \lim\limits_{n \to \infty} \frac{\log((\log(n)^a))}{\log(n^\epsilon)} = \lim\limits_{n \to \infty} \frac{a \cdot \log((\log(n)))}{\epsilon \log(n)} = 0 \nonumber \\
+    \Rightarrow (\log n)^a \ll n^{\epsilon}
+\end{gather}
+
+And it is apparent to see $n^{\epsilon} \ll  a^{\log_a(n)}$ since $ a^{\log_a(n)} = n$; as $\epsilon \in (0, 1)$, there will always be $n^{\epsilon} \ll n$.
 
@@
     \epsilon n = \Theta(n) \\
-    frac{n}{a} = \frac{1}{a}n =  \Theta(n)
+    \frac{n}{a} = \frac{1}{a}n =  \Theta(n)
 \end{gather}
@@
 
-\paragraph{Justification of $a^{\epsilon n} \equiv a^n$\newline}
+\paragraph{Justification of $n^a \equiv (n+b)^a \ll (n+a)^b \ll n^{a+b}$\newline}
 
-We may rewrite $a^{\epsilon n}$ as the following, since there must be a $c$ for $c \in \mathbb{R^+}$ which satisfy the equality.
+These are all polynomial functions with greatest power $> 1$, thus they are considered greater than the previous group (functions with greatest power $= 1$), and ordered according to ascending of \textit{power(s)}.
+
+\paragraph{Justification of $n^{a+b} \ll a^{\epsilon n} $\newline}
+
+$n^{a+b}$ is considered much greater than $a^{\epsilon n}$ due to its nature of being an exponential function.
+
+\paragraph{Justification of $a^{\epsilon n} \equiv a^n \ll b^n$\newline}
 
 \begin{gather}
-    a^{\epsilon} \cdot a^n = c \cdot a^n = \Theta(a^n)
+    \lim\limits_{n \to \infty} \frac{a^{\epsilon n}}{a^n} = \lim\limits_{n \to \infty} a^{\epsilon} = c \nonumber \\
+    \Rightarrow a^{\epsilon n} \equiv a^n
 \end{gather}
 
-Since it is known that $a^n = \Theta(a^n)$, these two expressions are considered equivalent.
+Also it is apparent to see that $a^n \ll b^n$ due to $1 < a < b$. Thus, the inequality is justified.
 

### 2020-02-04 assignment_2/article.tex
💄 Fix language and expressions.

@@
 \author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Robert) CHEN, \inlinecode{zxc325}}
-\date{Due and submitted on 02/03/2020 \\ EECS 340, Dr. Koyutürk}
+\date{Due and submitted on 02/03/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
 \maketitle
@@
 \subsection{(a) $max\{f(n), g(n)\} = \Theta (f(n) + g(n))$}
+\textbf{True}
 
@@
 
-Since both the $O$- and $\Omega$-notation are established, we may therefore conclude:
+Since both the $O$- and $\Omega$-notations are established, we may therefore conclude:
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(b1) $f(n) + d = O(f(n))$.}
+\subsection{(b1) $f(n) + d = O(f(n))$}
 
@@
 
-For the seek of disambiguation, we rewrite the questioned equation as $f(n) + d = O(f(n))$ by $d$ replacing $c$ for $d > 0$.
+For the sake of disambiguation, we rewrite the questioned equation as $f(n) + d = O(f(n))$ by $d$ replacing $c$ for $d > 0$.
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(b2) If $f(n) \geq 1$, then $f(n) + d = O(f(n))$.}
+\subsection{(b2) If $f(n) \geq 1$, then $f(n) + d = O(f(n))$}
+\textbf{True}
 
-For the seek of disambiguation, we rewrite the questioned equation as $f(n) + d = O(f(n))$ by $d$ replacing $c$ for $d > 0$.
+For the sake of disambiguation, we rewrite the questioned equation as $f(n) + d = O(f(n))$ by $d$ replacing $c$ for $d > 0$.
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(c1) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 0$, then $log(f(n)) = O(\log(g(n))$.}
+\subsection{(c1) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 0$, then $log(f(n)) = O(\log(g(n))$}
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(c2) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 1$, then $log(f(n)) = O(\log(g(n))$.}
+\subsection{(c2) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 1$, then $log(f(n)) = O(\log(g(n))$}
+\textbf{True}
 
-According to the defination of $O$-notation, we must have:
+According to the definition of $O$-notation, we must have:
 
@@
 
-For the seek of disambiguation, we rewrite the questioned equation as: if $f(n) = O(n^k)$, then $f(2n) = O(n^k)$ by $k$ replacing $c$ for $k > 0$.
+\textbf{True}
+
+For the sake of disambiguation, we rewrite the questioned equation as: if $f(n) = O(n^k)$, then $f(2n) = O(n^k)$ by $k$ replacing $c$ for $k > 0$.
 
@@
 \subsection{(d3) If $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$}
-
-For the seek of disambiguation, we rewrite the questioned equation as: if $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$.
+\textbf{True}
+For the sake of disambiguation, we rewrite the questioned equation as: if $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$.
 
@@
 
-The above equations can be rewrite as:
+The above equations can be losely rewritten as:
 
@@
 
-Where all of them can be generalized as $\Theta(\log(n))$, as it is known that $n^\epsilon \leq bn \leq n^a$ due to the decending of \textit{power(s)}.
+Where all of them can be generalized as $\Theta(\log(n))$, as it is known that $n^\epsilon \leq bn \leq n^a$ due to the decending of \textit{power(s)}.\newline
 
-The relationship of the above expressions with $\log_{\frac{1}{\epsilon}}(n)$ can be a bit unintuitive, we may show they are considered equivalent with:
+Note the relationship of the above expressions with $\log_{\frac{1}{\epsilon}}(n)$ can be a bit unintuitive, we may show they are considered equivalent with:
 \begin{gather}
@@
 
-Considered $ \log(n)$ is a generalized form of the perivous group of functions,  $(\log (n))^a$ is proven to be greater than the perivous group.
+Considered $ \log(n)$ is a generalized form of the previous group of functions,  $(\log (n))^a$ is proven to be greater than the previous group.
 
@@
 
-The above equations can be rewrite as:
+The above equations can be losely rewritten as:
 \begin{gather}
@@
 
-These are all polynomial functions with greatest power $> 1$, thus they are considered greater than the previous group (functions with greatest power $= 1$), and ordered according to ascending of \textit{power(s)}.
+These are all polynomial functions with the greatest power $> 1$; thus they are considered greater than the previous group (functions with the greatest power $= 1$), and ordered according to ascending of \textit{power(s)}.
 

### 2020-02-16 assignment_3/article.tex
🎉 Add placeholder Assignment 3 .tex file.

--- 2020-02-03 assignment_2/article.tex
@@
 
-\title{\textbf{EECS 340: Assignment 2}}
+\title{\textbf{EECS 340: Assignment 3}}
 
-\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Robert) CHEN, \inlinecode{zxc325}}
-\date{Due and submitted on 02/03/2020 \\ EECS 340, Dr. Koyutürk}
+\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Yuhui ZHANG, \inlinecode{yxz2052}}
+\date{Due and submitted on 02/20/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
 \maketitle
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \section{Problem 1}
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(a) $max\{f(n), g(n)\} = \Theta (f(n) + g(n))$}
-
-Since it is known that $f(n) \geq 0$, $g(n) \geq 0$, and $c > 0$; we must have:
-
-\begin{gather}
-    f(n) \leq f(n) + g(n) \nonumber\\
-    g(n) \leq f(n) + g(n) \nonumber\\
-    \Rightarrow \max(f(n), g(n)) \in O(f(n) + g(n)) \ \ \ \text{for } \begin{cases}
-                    c = 1 \\
-                    \forall{n_{0}} \in \mathbb{R}
-                \end{cases}
-\end{gather}
-
-Since it is also known that $f(n) + g(n) \leq 2 \cdot \max(f(n),g(n))$, we may therefore infer:
-
-\begin{gather}
-    \max(f(n), g(n)) \in \Omega(f(n) + g(n)) \ \ \ \text{for } \begin{cases}
-        c = \frac{1}{2} \\
-        \forall{n_{0}} \in \mathbb{R}
-    \end{cases}
-\end{gather}
-
-Since both the $O$- and $\Omega$-notation are established, we may therefore conclude:
-
-\begin{gather}
-    \max(f(n), g(n)) \in \Theta (f(n) + g(n))
-\end{gather}
+\section{Problem 2}
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(b1) $f(n) + d = O(f(n))$.}
-
-\textbf{False}
-
-For the seek of disambiguation, we rewrite the questioned equation as $f(n) + d = O(f(n))$ by $d$ replacing $c$ for $d > 0$.
-
-To prove the statement to be valid, we need to show:
-
-\begin{gather}
-    0 \leq f(n) + d \leq cf(n)
-\end{gather}
-
-For $f(n) = 0$, we cannot find any $c$ which satisfies the above equation since:
-
-\begin{gather}
-    O(f(n)) = cf(n) = 0  \nonumber \\
-    \Rightarrow 0 \leq 0 + d \leq c(0) \ \ \ \text{for $d > 0$}
-\end{gather}
-
-As the equation $0 + d \leq 0$ leads to a contradiction, the statement is invalid.
+\section{Problem 3}
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(b2) If $f(n) \geq 1$, then $f(n) + d = O(f(n))$.}
-
-For the seek of disambiguation, we rewrite the questioned equation as $f(n) + d = O(f(n))$ by $d$ replacing $c$ for $d > 0$.
-
-According to the defination of $O$-notation, we have:
-
-\begin{gather}
- f(n) = O(f(n)) \nonumber\\
- \exists c, n_{0} > 0 \ \text{ s.t.  $0 \leq f(n) \leq cf(n)$ \ \ \ for $n \geq n_{0}$} \\
- \exists n' > 0 \ \text{ s.t.  $f(n) \geq f(n')$ \ \ \ for $n, n' \geq n_{0}$} \\
- \Rightarrow 0 \leq f(n)+d \leq cf(n) + d \ \ \ \text{for $n \geq n_{0}$}
-\end{gather}
-
-Thus, we may rewrite the above equation as:
-
-\begin{gather}
- 0 \leq f(n)+d \leq (c + \frac{d}{f(n)})f(n) \ \ \ \text{for $f(n) \geq 1$} \nonmumber\\
- \Rightarrow 0 \leq f(n)+d \ \leq \ c'f(n) \ \ \ \text{for } \begin{cases}
-                 c' = c + \frac{d}{f(n')} \\
-                 n, n' \geq n_{0}
-             \end{cases}
-\end{gather}
-
-Therefore, we may conclude if $f(n) \geq 1$, then $f(n) + d = O(f(n))$ via direct proof.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(c1) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 0$, then $log(f(n)) = O(\log(g(n))$.}
-
-\textbf{False}
-
-For $f(n) = 2$ and $g(n) = 1$, then $\log f(n) = 1$ and $\log g(n) = 0$. Since we cannot find any constant $c$ where:
-
-\begin{gather}
-    0 \leq 1 \leq c(0)
-\end{gather}
-
-Thus the statement is invalid.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(c2) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 1$, then $log(f(n)) = O(\log(g(n))$.}
-
-According to the defination of $O$-notation, we must have:
-
-\begin{gather}
-    \exists c, n_{0} > 0 \ \text{ s.t. } \ f(n) \leq cg(n) \ \ \ \text{for $n \geq n_{0}$}
-\end{gather}
-
-Since it is given that $\log(f(n))\geq 0$, $\log(g(n)) \geq 1 $, thus we must have:
-
-\begin{gather}
-    \log(f(n)) \leq \log(c(g(n))) \ \ \ \text{for $n \geq n_{0}$} \nonumber\\
-    \Rightarrow \log(f(n)) \leq \log c + \log(g(n)) \ \ \ \text{for $n \geq n_{0}$}
-\end{gather}
-
-As $c, n_{0}$ are constants, there must be a constant $c'$ s.t.
-
-\begin{gather}
-    c' \geq \frac{\log c}{\log (g(n_{0}))} + 1 \\
-    \Rightarrow (c' -1)\log (g(n))  \ \geq \ (c' -1)\log (g(n_{0})) \ \geq \ \log c \ \ \ \text{for $n \geq n_{0}$} \\
-    \exists c, n_{0} > 0 \nonumber \ \text{ s.t. } \  \\
-    \log(f(n)) \ \leq \ \log c + \log(g(n)) \ \leq \  (c' -1)\log (g(n)) + \log(g(n))\ \ \ \text{for $n \geq n_{0}$} \\
-    \Rightarrow \log(f(n))  \leq c'\log (g(n))
-\end{gather}
-
-Thus we may conclude $log(f(n)) = O(\log(g(n))$, the statement is therefore proven to be valid.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(d1) $f(2n) = \Theta(f(n))$}
-
-\textbf{False}
-
-For $f(n) = 2^n$, we have $f(2n) = 4^n$.
-Where $f(2n) \neq \Theta(f(n))$ due to the LHS has a higher asymptotic order, and therefore we can't find any constant $c_{1}, c_{2}$ to form a relation of $c_1 \cdot 2^n \leq 4^n \leq c_2 \cdot 2^n$.
-Thus, the statement is invalid.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(d2) If $f(n) = O(n^k)$, then $f(2n) = O(n^k)$}
-
-For the seek of disambiguation, we rewrite the questioned equation as: if $f(n) = O(n^k)$, then $f(2n) = O(n^k)$ by $k$ replacing $c$ for $k > 0$.
-
-Since $f(n) = O(n^k)$, we must have $0 \leq f(n) \leq cn^k$ for $n \geq n_0$ and a $c$ for $c \in \mathbb{R^+}$. Now substitute $n$ as $2n$, we may have:
-
-\begin{gather}
-    0 \leq f(2n) \leq c(2n)^k \nonumber \\
-    \Rightarrow 0 \leq f(2n) \leq c\cdot (2)^k \cdot n^k \\
-    \Rightarrow 0 \leq f(2n) \leq c' \cdot n^k \ \ \ \text{where $c' = c\cdot (2)^k$}
-\end{gather}
-
-Thus we may conclude if $f(n) = O(n^k)$, then $f(2n) = O(n^k)$.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(d3) If $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$}
-
-For the seek of disambiguation, we rewrite the questioned equation as: if $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$.
-
-Since $f(n) = \Theta(n^k)$, we must have $0 \leq c_1 \cdot n^k \leq f(n) \leq c_2 \cdot n^k$ for $n \geq n_0$ and $c_1, c_2$ for $c_1, c_2 \in \mathbb{R^+}$. Now substitute $n$ as $2n$, we may have:
-
-\begin{gather}
-    0 \leq c_1 (2n)^k \leq f(2n) \leq c_2 (2n)^k \nonumber \\
-    \Rightarrow 0 \leq c_1 \cdot 2^k \cdot n^k \leq f(2n) \leq c_2 \cdot 2^k \cdot n^k
-\end{gather}
-
-From $0 \leq c_1 \cdot n^k \leq f(n) \leq c_2 \cdot n^k$ , we may also infer:
-
-\begin{gather}
-    \frac{f(n)}{c_1} \geq k \geq \frac{f(n)}{c_2} \\
-    \Rightarrow c_1 \cdot 2^k \cdot \frac{f(n)}{c_2} \leq f(2n) \leq c_2 \cdot 2^k \cdot \frac{f(n)}{c_1} \\
-    \Rightarrow 0\leq c^{'}_{1}\cdot f(n) \leq f(2n) \leq c^{'}_{2}\cdot f(2n) \ \ \ \text{for}\begin{cases}
-                    c^{'}_{1} = \frac{c_1 \cdot 2^k}{c_2} \\
-                    c^{'}_{2} = \frac{c_2 \cdot 2^k}{c_1}
-                \end{cases}
-\end{gather}
-
-Thus we may conclude if $f(n) = \Theta(n^k)$, then $f(2n) = \Theta(f(n))$.
-
-\section{Problem 2}
-
-\paragraph{Answer}
-
-\begin{gather}
-    \frac{1}{n^a} \ll \frac{1}{n^\epsilon} \ll \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $0 < \epsilon < \frac{1}{2}$)} \ll \log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \\
-    \equiv \log(n^b) \leq \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $\epsilon \geq \frac{1}{2}$)} \ll (\log n)^a \ll n^{\epsilon} \\
-    \ll a^{\log_a(n)} \equiv \epsilon n \equiv \frac{n}{a} \ll n^a \equiv (n+b)^a\\
-    \ll (n+a)^b \ll n^{a+b} \ll \epsilon^n \ll a^{\epsilon n} \equiv a^n \ll b^n
-\end{gather}
-
-\paragraph{Justification of $\log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \equiv \log(n^b)$\newline}
-
-The above equations can be rewrite as:
-
-\begin{gather}
-    \log(n^\epsilon) = \epsilon \log(n) \\
-    \log(n^a) = a \log(n) \\
-    \log(bn) = \log(b) + \log(n) \\
-    \log(n^b) = b \log(n)
-\end{gather}
-
-Where all of them can be generalized as $\Theta(\log(n))$, as it is known that $n^\epsilon \leq bn \leq n^a$ due to the decending of \textit{power(s)}.
-
-\paragraph{Justification of $ \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $0 < \epsilon < \frac{1}{2}$)} \equiv \log(n^b) \leq \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $\epsilon \geq \frac{1}{2}$)}$\newline}
-
-It is known that when $\epsilon < \frac{1}{2} \Rightarrow \frac{1}{\epsilon} \geq 2$; when $\epsilon \geq \frac{1}{2} \Rightarrow  \frac{1}{\epsilon} \leq 2$.
-Since it is observable that $\log_{x}(n) \gg \log_{x'}(n)$ for $x < x'$, such (in)equaility is valid.
-
-\paragraph{Justification of $a^{\log_a(n)} \equiv \epsilon n \equiv \frac{n}{a}$\newline}
-
-The above equations can be rewrite as:
-\begin{gather}
-    a^{\log_a(n)} = n^1 = \Theta(n) \\
-    \epsilon n = \Theta(n) \\
-    frac{n}{a} = \frac{1}{a}n =  \Theta(n)
-\end{gather}
-
-Thus, the above equality is justified.
-
-\paragraph{Justification of $a^{\epsilon n} \equiv a^n$\newline}
-
-We may rewrite $a^{\epsilon n}$ as the following, since there must be a $c$ for $c \in \mathbb{R^+}$ which satisfy the equality.
-
-\begin{gather}
-    a^{\epsilon} \cdot a^n = c \cdot a^n = \Theta(a^n)
-\end{gather}
-
-Since it is known that $a^n = \Theta(a^n)$, these two expressions are considered equivalent.
+\section{Problem 4}
 

### 2020-02-20 assignment_3/article.tex
✨ Add Question 1 response.

@@
-\documentclass[12pt]{article}
+\documentclass[11pt]{article}
 \usepackage{setspace}
@@
 
+\section{(a) $T(n) = bT(n/a) + \Theta(n)$}
+
+For this recurrance, we have a comparsion between $n^{\log_a b}$ and $n$.
+Since it is given that $1 < a < b$, there must be $\log_a b > 1$.
+Therefore we may say that there must be a $n^\epsilon = \frac{n^{\log_a b}}{n}$ where $0 < \epsilon = \log_a b - 1$.
+
+Now we have $f(n) = n = O(n^{(\log_a b) - \epsilon})$, where $0 < \epsilon = \log_a b - 1$, we can apply \textit{case 1} of the master theorem and conclude that the solution is $T(n) = \Theta(n)$.
+
+\section{(b) $T(n) = a^2 T(n/a) + \Theta(n^2)$}
+For this recurrance, we have a comparsion between $n^{\log_a a^2}$ and $n^2$, thus $n^2$ and $n^2$.
+As now we have $f(n) = \Theta(n^2)$, we can apply \textit{case 2} of the master theorem and conclude that the solution is $T(n) = \Theta(n \cdot \log n)$
+
+\section{(c) $T(n) = T(\lambda n) + n^{\lambda}$}
+
+We may rewrite it as $T(n) = T\Big(\frac{n}{\frac{1}{\lambda}}\Big) + n^{\lambda}$.
+Thus, we have a comparsion between $n^{\log_{\frac{1}{\lambda}} 1}$ and $n^{\lambda}$, which is equivalent as $n^0$ and $n^{\lambda}$, then we have $f(n) = \Omega(n^{\log_b a + \epsilon})$ for $\epsilon = \lambda$.
+We may also show $af(\frac{n}{b}) \leq cf(n)$ for $1 \cdot f\Big(\frac{n}{\frac{1}{\lambda}}\Big) = f(\lambda n)$.
+Combined, together, we can apply \textit{case 3} of the master theorem and conclude that the solution is $T(n) = \Theta(n^\lambda)$.
+
+\section{(d) $T(n) = aT(\frac{n}{a}) + \Theta(n^{\lambda}(\log n)^b)$}
+For this recurrance, we have a comparsion between $n^{\log_a a}$ and $n^{\lambda}(\log n)^b)$, which is equivalent to comparing $n$ and $n^{\lambda}(\log n)^b)$.
+We may prove that $n$ is polynomially larger than $n^{\lambda}(\log n)^b)$ by analyzing:
+
+\begin{align}
+    \text{W.T.S. \ }\lim_{n \to \infty} \frac{n^\epsilon \cdot n^\lambda (\log n)^b}{n} &= 0\\
+    \lim_{n \to \infty} \frac{n^\lambda (\log n)^b}{n^{1-\epsilon - \lambda}} &= 0 \nonumber\\
+    % \text{Since $n^x$ for any $x > 0$ grows much faster than anything with a base of $\log n$, we must have the following} \nonumber \\
+    \Longrightarrow 1-\epsilon - \lambda > 0 &\Rightarrow \epsilon < 1 - \lambda
+\end{align}
+
+Thus, we have $f(n) = O(n^{\log_b a - \epsilon})$ for $\epsilon < 1 - \lambda$. Then, we can apply \textit{case 1} of the master theorem and conclude that the solution is $T(n) = \Theta(n)$.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 
+\begin{algorithm}
+\caption{QuickMiss(C, D, start, end)}\label{QuickMiss}
+    \begin{algorithmic}[1]
+        \Procedure{QuickMiss}{C, D, start, end}
+        % \State $l \gets m$
+        % \State $p \gets n$
+        \If {$p < r$}
+            \State $left, q, right \gets \textsc{Partition}(C, D, start, end)$
+            \If {$left < right$}
+                \State $\textsc{Partition}(C, q+1, r)$
+            \ElsIf {$right > left$}
+                \State $\textsc{Partition}(C, p, q-1)$
+            \Else
+                \State \Return $D[q]$
+            \EndIf
+        \EndIf
+        \EndProcedure
+    \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{Partition(C, D, p, r)}\label{Partition}
+    \begin{algorithmic}[1]
+        \Procedure{Partition}{C, D, p, r}
+        \State $r \gets r+1$
+        \State $C[r] \gets D[\frac{p+r}{2}]$
+        \State $q \gets p$
+        \For {$i \gets p$ \textbf{to} $r-1$}
+            \If {$\textsc{Compare-Strings}(C[i], C[r])$}
+                \State $\textsc{Swap}(C[i], C[q])$
+                \State $q \gets q+1$
+            \EndIf
+        \EndFor
+        \State $\textsc{Swap}(C[q], C[r])$
+        \State \Return $q$
+        \EndProcedure
+    \end{algorithmic}
+\end{algorithm}
+
 % \section{References}

### 2020-02-20 assignment_3/article.tex
✨ Add Question 2 response.

@@
 
+\subsection{(a) For any constant $0 < \alpha < 1$, if $T(n) = T(\alpha n) + T((1-\alpha)n) + \Theta(n)$, then $T(n) = O(n \log n)$}
+
+\paragraph{Guess $T(n) = O(n \log n)$\newline}
+Thus there must be constants $c, c'$ for $c, c'\in \mathbb{Z^+}$ s.t. $T(n) \leq cn \log n - c'n$.
+
+\paragraph{Given $T(n) = T(\alpha n) + T((1-\alpha)n) + \Theta(n)$\newline}
+\begin{proof}
+We may rewrite it as $T(n) = T(\alpha n) + T((1-\alpha)n) + dn$ for $d \in \mathbb{Z^+}$.
+Assume the claim $T(k) = ck \log k - c'k$ holds true for $T(k)$ for $k \in [1, n)$, and without loss of generality assume that $\alpha \geq 0.5$, we have:
+
+\begin{align}
+    T(k + 1) &= T(\alpha(k + 1)) + T((1-\alpha)(k+1)) + d(k + 1) \\
+    &\leq [c \cdot \alpha (k + 1) \log(\alpha(k + 1)) - c'(k+1)] + \nonumber\\
+    & \ \ \ \ [c \cdot ((1- \alpha)(k + 1))\log((1-\alpha)(k + 1)) - c'(k+1)]+ d(k + 1) \nonumber \\
+    &\leq c \cdot \alpha (k + 1) \log(\alpha(k + 1)) + c(1-\alpha)(k + 1)\log(\alpha(k+1)) + d(k + 1) - 2c'(k+1) \nonumber \\
+    &\leq (c \alpha + c(k + 1) -  c \alpha) \cdot \log(\alpha(k + 1)) +  d(k + 1) - 2c'(k+1)\nonumber \\
+    &\leq c(k + 1) \cdot \log(\alpha(k + 1)) +  (d-2c')(k + 1)\nonumber \\
+    &\leq c(k + 1) \cdot \log(k + 1)+  (d-2c')(k + 1)\nonumber \\
+    \Longrightarrow T(k + 1) &\leq c(k + 1) \cdot \log(k + 1) \ \ \ \text{for $c'= \frac{1}{2}d$}
+\end{align}
+
+As now we have $T(k + 1) \leq c(k + 1) \cdot \log(k + 1)$ for $c'= \frac{1}{2}d$, we may say it is true for $T(k)$ for all $k \in [1, n)$.
+\end{proof}
+
+\subsubsection{(b) For any constant $k > 0$, if $T(n) = \Theta(n) + \sum^{k}_{i = 1} T(\frac{n}{2^i})$, then $T(n) = O(n)$}
+
+\paragraph{Guess $T(n) = O(n \log n)$\newline}
+Thus, there must be a constant $c$ for $c \in \mathbb{Z^+}$ s.t. $T(n) \leq cn$.
+
+\paragraph{Given $T(n) = \Theta(n) + \sum^{k}_{i = 1} T(\frac{n}{2^i})$\newline}
+\begin{proof}
+As there must be a constant $d$ for $d \in \mathbb{Z^+}$ s.t.
+$\Theta(n) \leq dn$ -- and therefore causes $T(n) \leq dn + \sum^{k}_{i = 1} T(\frac{n}{2^i})$ -- with $d$ for $0 < d \leq c - \sum^{k}_{i = 1} c(\frac{1}{2^i})$.
+Now we may connect the two equations and get
+
+\begin{align}
+    T(n) &\leq dn + \sum^{k}_{i = 1} T(\frac{n}{2^i}) \leq cn \\
+    &\leq dn + \sum^{k}_{i = 1} c \cdot (\frac{n}{2^i}) \leq cn \nonumber
+\end{align}
+
+Assume the claim $T(n) \leq dn + \sum^{k}_{i = 1} T(\frac{n}{2^i}) \leq cn$ holds true for $T(m)$ for $m \in [1, n)$, consider:
+
+\begin{align}
+    T(m+1) &\leq d(m + 1) + \sum^{k}_{i = 1} T(\frac{m+1}{2^i}) \\
+    &\leq d(m + 1) + \sum^{k}_{i = 1} c \cdot (\frac{m+1}{2^i}) \nonumber \\
+    &\leq \underbrace{dm + \sum^{k}_{i = 1} c \cdot (\frac{m}{2^i})}_{= T(m) \leq cm} + \underbrace{d + \sum^{k}_{i = 1} c \cdot (\frac{1}{2^i})}_{= T(1) \leq c(1)} \\
+    \Longrightarrow T(m+1) &\leq c(m+1)
+\end{align}
+
+As now we have $T(m+1) \leq c(m+1)$ for $c \in \mathbb{Z^+}$, we may say it is true for $T(m)$ for all $m \in [1, n)$.
+\end{proof}
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

### 2020-02-20 assignment_3/quick_miss.py
✨ Add quick_miss in runnable python code.

@@ -1,0 +1,42 @@
+def quick_miss(C, D, p, r, miss_left=None):
+    if p < r:
+        q = partition(C, p, r)
+        if C[q] == D[q]:
+            print(f'{C[q]} == {D[q]}, q = {q}, p = {p}, r = {r}')
+            print(f'quick_miss(C, D, {q+1}, {r}, False)')
+            return quick_miss(C, D, q+1, r, False)
+        else:
+            print(f'{C[q]} != {D[q]}, q = {q}, p = {p}, r = {r}')
+            print(f'quick_miss(C, D, {p}, {q-1}, True)')
+            return quick_miss(C, D, p, q-1, True)
+    # else:
+    if miss_left:
+        print(f'\nmiss_left = {miss_left}, p = {p}, r = {r}, D {D}')
+        print(f'D[p] = {D[p]}')
+        return D[p]
+    else:
+        print(f'\nmiss_left = {miss_left}, p = {p}, r = {r}, D {D}')
+        print(f'D[r+1] = {D[r+1]}')
+        return D[r+1]
+
+def partition(A, p, r):
+    print(f'\n\nbefore: C {A}, p = {p}, r = {r}')
+    q = p
+    for i in range(p, r):
+        if A[i] < A[r]:
+            A[i], A[q] = A[q], A[i]
+            q += 1
+    A[q], A[r] = A[r], A[q]
+    print(f'after : C {A}, q = {q}, C[q] = {A[q]}')
+    return q
+
+
+# C = [1, 2, 3, 6, 5]
+# D = [1, 2, 3, 4, 5, 6]
+
+C = [1, 2, 3, 6, 5]
+D = [1, 2, 3, 4, 5, 6]
+
+result = quick_miss(C, D, 0, 4)
+
+print(f'result is: {result}')

### 2020-02-20 assignment_3/article.tex
✨ Add Question 4 response.
🐛 Bugfix on Question 4 with out_of_index pivot init.
🐛 Bugfix on Q4 to do recrusion with return to avoid output discarding.
✨ Add Question 4(b) sketch response.

@@
 \usepackage{wasysym}
-\newcommand{\inlinecode}{\texttt}
+\newcommand{\ilc}{\texttt}
 \usepackage{etoolbox}
@@
 
-\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Yuhui ZHANG, \inlinecode{yxz2052}}
+\author{Shaochen (Henry) ZHONG, \ilc{sxz517} \\ Yuhui ZHANG, \ilc{yxz2052}}
 \date{Due and submitted on 02/20/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\newpage
 \section{Problem 4}
 
+\subsubsection{(a)}
+
 \begin{algorithm}
-\caption{QuickMiss(C, D, start, end)}\label{QuickMiss}
+\caption{QuickMiss(C, D, p, r, missLeft)}\label{QuickMiss}
     \begin{algorithmic}[1]
-        \Procedure{QuickMiss}{C, D, start, end}
-        % \State $l \gets m$
-        % \State $p \gets n$
+        \Procedure{QuickMiss}{C, D, p, r, missLeft}
         \If {$p < r$}
-            \State $left, q, right \gets \textsc{Partition}(C, D, start, end)$
-            \If {$left < right$}
-                \State $\textsc{Partition}(C, q+1, r)$
-            \ElsIf {$right > left$}
-                \State $\textsc{Partition}(C, p, q-1)$
+            \State $q \gets \textsc{Partition}(C, p, r)$
+            \If {$C[q] == D[q]$}
+                \State \Return $\textsc{QuickMiss}(C, D, q+1, r, False)$
             \Else
-                \State \Return $D[q]$
+                \State \Return $\textsc{QuickMiss}(C, D, p, q-1, True)$
             \EndIf
+        \EndIf
+        \If {$missLeft == True$}
+            \State \Return $D[p]$
+        \Else
+            \State \Return $D[r+1]$
         \EndIf
@@
 \begin{algorithm}
-\caption{Partition(C, D, p, r)}\label{Partition}
+\caption{Partition(A, p, r)}\label{Partition}
     \begin{algorithmic}[1]
-        \Procedure{Partition}{C, D, p, r}
-        \State $r \gets r+1$
-        \State $C[r] \gets D[\frac{p+r}{2}]$
+        \Procedure{Partition}{A, p, r}
         \State $q \gets p$
-        \For {$i \gets p$ \textbf{to} $r-1$}
-            \If {$\textsc{Compare-Strings}(C[i], C[r])$}
-                \State $\textsc{Swap}(C[i], C[q])$
+        \For {$i \gets p$ \textbf{to} $r$}
+            \If {$\textsc{Compare-Strings}(A[i], A[r])$}
+                \State $\textsc{Swap}(A[i], A[q])$ \Comment{Exchange the two elements.}
                 \State $q \gets q+1$
@@
         \EndFor
-        \State $\textsc{Swap}(C[q], C[r])$
+        \State $\textsc{Swap}(A[q], A[r])$
         \State \Return $q$
@@
 \end{algorithm}
+
+\subsubsection{(b)}
+
+It is known that \textsc{QuickSort} has an average runtime of $O(n\log n)$ due to the fact that it is considered \textit{case 2} of the master theorem: as it has $n$ nodes on each level and with a depth of $\log n$, thus $O(n\log n)$.
+Our \textsc{QuickMiss} algorithm has a runtime of $O(n)$ due to it only calls \textsc{Partition} on either left portion or right portion to the \ilc{pivot}, but never both.
+Thus, on each level it will always has less than $n$ nodes, therefore forming a \textit{case 3} of the master theorem.
+The master theorem suggest, in \textit{case 3} the roots dominate the leaves and therefore determine the runtime of the algorithm -- as \textsc{QuickSort} has $n$ roots at the beginning, we may conclude it has a runtime of $\Theta(n)$.
 

### 2020-02-20 assignment_3/article.tex
🐛 Fix conclusion typo in Question 1(a).

@@
 
-Now we have $f(n) = n = O(n^{(\log_a b) - \epsilon})$, where $0 < \epsilon = \log_a b - 1$, we can apply \textit{case 1} of the master theorem and conclude that the solution is $T(n) = \Theta(n)$.
+Now we have $f(n) = n = O(n^{(\log_a b) - \epsilon})$, where $0 < \epsilon = \log_a b - 1$, we can apply \textit{case 1} of the master theorem and conclude that the solution is $T(n) = \Theta(n^{\log_a b})$.
 

### 2020-02-20 assignment_3/article.tex
💄 Polish Question 1(d) math expression.

@@
 \section{(d) $T(n) = aT(\frac{n}{a}) + \Theta(n^{\lambda}(\log n)^b)$}
-For this recurrance, we have a comparsion between $n^{\log_a a}$ and $n^{\lambda}(\log n)^b)$, which is equivalent to comparing $n$ and $n^{\lambda}(\log n)^b)$.
-We may prove that $n$ is polynomially larger than $n^{\lambda}(\log n)^b)$ by analyzing:
+For this recurrance, we have a comparsion between $n^{\log_a a}$ and $n^{\lambda}(\log n)^b$, which is equivalent to comparing $n$ and $n^{\lambda}(\log n)^b$.
+We may prove that $n$ is polynomially larger than $n^{\lambda}(\log n)^b$ by analyzing:
 

### 2020-02-21 assignment_3/article.tex
✨ Add Question 3 response.

@@
 
+% \begin{tikzpicture}
+%
+% \matrix [matrix of nodes,
+%          nodes = {draw,  minimum size = 2ex},
+%          column sep=1ex, row sep=1ex,
+%          row 1/.style={execute at begin cell= {|[label=\pgfmathparse{int(\the\pgfmatrixcurrentcolumn-1)}\pgfmathresult]|}}
+%          ]
+% {
+% 9 & 2 & 4 & 4 & 5   \\
+% 8 & 3 & 3 & 5 & 5   \\
+% 7 & 4 & 2 & 7 & 5   \\
+% 6 & 5 & 1 & 1 & 5   \\
+% 5 & 6 & 0 & 2 & 5   \\
+% };
+% \end{tikzpicture}
+
+\tikzset{
+mymat/.style={
+  matrix of math nodes,
+  text height=2.5ex,
+  text depth=0.75ex,
+  text width=3.25ex,
+  align=center,
+  column sep=-\pgflinewidth
+  },
+mymats/.style={
+  mymat,
+  nodes={draw,fill=#1}
+  }
+}
+
+\begin{tikzpicture}[>=latex]
+
+\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
+at (0,4.5)
+(mat1)
+{
+1 & 2 & 3 & 4 & 5\\
+> & > & > & > & ..\\
+};
+
+\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
+at (0,3)
+(mat2)
+{
+> & > & > & > & ..\\
+};
+
+\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
+at (0,2)
+(mat3)
+{
+> & > & > & > & ..\\
+};
+
+\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
+at (0,1)
+(mat4)
+{
+> & > & > & > & ..\\
+};
+
+\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
+at (0,0)
+(mat5)
+{
+> & > & > & > & ..\\
+};
+
+\matrix[mymat,right=of mat1,row 2/.style={nodes=draw}]
+at (4.5,4.5)
+(mat11)
+{
+1 & 2 & 3 & 4 & 5\\
+> & > & > & > & ..\\
+};
+
+\matrix[mymat,right=of mat2,row 1/.style={nodes=draw}]
+at (4.5,3)
+(mat22)
+{
+> & > & > & > & ..\\
+};
+
+\matrix[mymat,right=of mat3,row 1/.style={nodes=draw}]
+at (4.5,2)
+(mat33)
+{
+> & > & > & > & ..\\
+};
+
+\matrix[mymat,right=of mat4,row 1/.style={nodes=draw}]
+at (4.5,1)
+(mat44)
+{
+> & > & > & > & ..\\
+};
+
+\matrix[mymat,right=of mat5,row 1/.style={nodes=draw}]
+at (4.5,0)
+(mat55)
+{
+> & > & > & > & ..\\
+};
+
+\matrix[mymat,right=of mat11,row 2/.style={nodes=draw}]
+at (10,4.5)
+(mat111)
+{
+1 & 2 & 3 & 4 & 5\\
+M & X & X & > & ..\\
+};
+
+\matrix[mymat,right=of mat22,row 1/.style={nodes=draw}]
+at (10,3)
+(mat222)
+{
+X & X & > & > & ..\\
+};
+
+\matrix[mymat,right=of mat33,row 1/.style={nodes=draw}]
+at (10,2)
+(mat333)
+{
+X & > & > & > & ..\\
+};
+
+%
+% \matrix[mymat,right=of mat44,row 1/.style={nodes=draw}]
+% at (10,1)
+% (mat444)
+% {
+% \geq & \geq & \geq & \geq & ..\\
+% };
+%
+% \matrix[mymat,right=of mat55,row 1/.style={nodes=draw}]
+% at (10,0)
+% (mat555)
+% {
+% \geq & \geq & \geq & \geq & ..\\
+% };
+
+\node[above=20pt of mat1]
+    (cella) {\textbf{Step 1:} $T(5)$};
+\node[above=0pt of mat1]
+    (cella) {$L[1] > L[2] > ... > L[5]$};
+
+\node[above=20pt of mat11]
+    (cella) {\textbf{Step 2:} $T(1)$};
+\node[above=0pt of mat11]
+    (cella) {$A[1] > B[1] > ... > E[1]$};
+
+\node[above=20pt of mat111]
+    (cella) {\textbf{Step 3:} $T(1)$};
+\node[above=0pt of mat111]
+    (cella) {Sort $A[2], A[3], B[1], B[2], C[1]$};
+
+\node[left=0pt of mat1]
+  (cella) {B};
+\node[left=0pt of mat2]
+  (cellb) {A};
+\node[left=0pt of mat3]
+  (cellb) {D};
+\node[left=0pt of mat4]
+  (cellb) {C};
+\node[left=0pt of mat5]
+  (cellb) {E};
+
+\node[left=0pt of mat11]
+(cella) {A};
+\node[left=0pt of mat22]
+(cellb) {B};
+\node[left=0pt of mat33]
+(cellb) {C};
+\node[left=0pt of mat44]
+(cellb) {D};
+\node[left=0pt of mat55]
+(cellb) {E};
+
+\node[left=0pt of mat111]
+(cella) {A};
+\node[left=0pt of mat222]
+(cellb) {B};
+\node[left=0pt of mat333]
+(cellb) {C};
+% \node[left=0pt of mat444]
+% (cellb) {D};
+% \node[left=0pt of mat555]
+% (cellb) {E};
+\end{tikzpicture}\newline
+
+\paragraph{Step 1: Divide\newline}
+Divide the 25 elements into groups of 5, and sort each group internally. By that we may have five sorted lists, we denote them as $A, B, C, D, E$, with the relationship of
+
+\begin{equation}
+    L[1] > L[2] > L[3] > L[4] > L[5] \label{eq:divide_group}
+\end{equation}
+
+for $L \in \{A, B, C, D, E\}$. This step shall cost five experiments and thus carries a $T(5)$ runtime, assuming each experiment will take $T(1)$ to conduct.
+
+\paragraph{Step 2: Sort front and find max candidate\newline}
+Sort the 5 groups according to their first elements, in the demonstrated case, we have
+\begin{equation}
+    A[1] > B[1] > C[1] > D[1] > E[1] \label{eq:sort_front}
+\end{equation}
+This step shall cost one experiment and thus carries a $T(1)$ runtime.
+
+According to \textit{Equation (\ref{eq:divide_group})} and \textit{Equation (\ref{eq:sort_front})}, we must have $A[1]$ being the material with maximum effectiveness amount all candidates.
+We may therefore add $A[1]$ into the result list.
+
+\paragraph{Step 2: Find rest two candidates\newline}
+
+According to \textit{Equation (\ref{eq:divide_group})} and \textit{Equation (\ref{eq:sort_front})}, we may safely claim the rest two candidates with top effetiveness must be among $A[2], A[3], B[1], B[2], C[1]$.
+Since it is known that $B[1] > C[1] > D[1] > E[1]$, we may discard $D[1], E[1]$ -- as there are always less effective in comparsion with $B[1], C[1]$ -- and therefore discarding group $D, E$, once again according to \textit{Equation (\ref{eq:divide_group})}.
+
+However, we cannot determine the expicit relationship between  $A[2], A[3], B[1], B[2], C[1]$, thus we conduct another experiment and add the top two candidates to the result list.
+This step shall cost one experiment and thus carries a $T(1)$ runtime.
+
+\paragraph{Total Runtime}
+
+\begin{equation}
+    T_{\text{total}} = T(5) + T(1) + T(1) = T(7) \label{eq:q4_runtime}
+\end{equation}
+
+As \textit{Equation (\ref{eq:q4_runtime})} is a sum of runtime cost from each step, we may conclude that our algoritm has a runtime of $T(4)$.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

### 2020-02-21 assignment_3/article.tex
🔨 Update Question 4(b) proof with a mathematical approach.

@@
 
-\subsubsection{(a)}
+\subsubsection{(a)}\label{sec:4.a}
 
@@
             \If {$\textsc{Compare-Strings}(A[i], A[r])$}
-                \State $\textsc{Swap}(A[i], A[q])$ \Comment{Exchange the two elements.}
+                \State $\textsc{Swap}(A[i], A[q])$ \Comment{Exchange two elements.}
                 \State $q \gets q+1$
@@
 
-It is known that \textsc{QuickSort} has an average runtime of $O(n\log n)$ due to the fact that it is considered \textit{case 2} of the master theorem: as it has $n$ nodes on each level and with a depth of $\log n$, thus $O(n\log n)$.
-Our \textsc{QuickMiss} algorithm has a runtime of $O(n)$ due to it only calls \textsc{Partition} on either left portion or right portion to the \ilc{pivot}, but never both.
-Thus, on each level it will always has less than $n$ nodes, therefore forming a \textit{case 3} of the master theorem.
-The master theorem suggest, in \textit{case 3} the roots dominate the leaves and therefore determine the runtime of the algorithm -- as \textsc{QuickSort} has $n$ roots at the beginning, we may conclude it has a runtime of $\Theta(n)$.
+It is known that \textsc{QuickSort} has an average runtime of $\Theta(n\log n)$ due to the fact that it is considered \textit{case 2} of the master theorem: as it has $n$ nodes on each level and with a depth of $\log n$, thus $\Theta(n\log n)$.
+Our \textsc{QuickMiss} algorithm has a runtime of $\Theta(n)$ due to it only calls \textsc{Partition} on either left portion or right portion to the \ilc{pivot}, but never both (indicated in \ilc{line 4-7} of \textsc{QuickMiss}).
+Thus, on each level it will always have less than $n$ nodes, therefore forming a \textit{case 3} of the master theorem.
+The master theorem suggests, in \textit{case 3} the roots dominate the leaves and therefore determines the runtime of the algorithm -- as \textsc{QuickSort} has $n$ roots at the beginning, we may conclude it has a runtime of $\Theta(n)$.\newline
+
+To demonstrate it mathmatically, we have \textsc{QuickSort} being $T(n) = 2T(n/2) + \Theta(n)$ where  the leading $2T(n/2)$ indicates it will recursively handle both parts of the partition.
+Since \textsc{QuickMiss} only needs to handle one part, we have \textsc{QuickMiss} being $T(n) = T(n/2) + \Theta(n)$.
+This means we have a comparsion between $n^{\log_2 1}$ and $n$, which is equivalent to $n^0 \Rightarrow 1$ and $n$.
+Then we may have $f(n) = \Omega(n^{\log_2 1 + \epsilon}) = \Omega(n^{0 + \epsilon})$ for $\epsilon = 1$, and we may prove that $T(n) = \Theta(n)$ for \textsc{QuickMiss}.
 

### 2020-02-21 assignment_3/article.tex
🔨 Update Question 4(1) with explanatory comments.

@@
     \begin{algorithmic}[1]
-        \Procedure{QuickMiss}{C, D, p, r, missLeft}
-        \If {$p < r$}
-            \State $q \gets \textsc{Partition}(C, p, r)$
-            \If {$C[q] == D[q]$}
-                \State \Return $\textsc{QuickMiss}(C, D, q+1, r, False)$
-            \Else
-                \State \Return $\textsc{QuickMiss}(C, D, p, q-1, True)$
+        \Procedure{QuickMiss}{C, D, p, r, missLeft} \Comment{Set any value to $missLeft$ for initial call.}
+        \If {$p < r$} \Comment{Base case, terminates when $p = r$.}
+            \State $q \gets \textsc{Partition}(C, p, r)$ \Comment{Get pivot index from inclusive $C[p, r]$.}
+            \If {$C[q] == D[q]$} \Comment{If no missing element on left portion to $q$.}
+                \State \Return $\textsc{QuickMiss}(C, D, q+1, r, False)$ \Comment{Thus check right partition.}
+            \Else \Comment{If no missing element on right portion to $q$.}
+                \State \Return $\textsc{QuickMiss}(C, D, p, q-1, True)$ \Comment{Thus check left partition.}
             \EndIf
@@
         \If {$missLeft == True$}
-            \State \Return $D[p]$
+            \State \Return $D[p]$ \Comment{Missing element index within range of $C$, simply return.}
         \Else
-            \State \Return $D[r+1]$
+            \State \Return $D[r+1]$ \Comment{Missing element $> r$, $+1$ to retrive from $D$.}
         \EndIf
@@
         \For {$i \gets p$ \textbf{to} $r$}
-            \If {$\textsc{Compare-Strings}(A[i], A[r])$}
+            \If {$\textsc{Compare-Strings}(A[i], A[r])$} \Comment{if $A[i] < A[r]$ alphabetically.}
                 \State $\textsc{Swap}(A[i], A[q])$ \Comment{Exchange two elements.}

### 2020-02-21 assignment_3/article.tex
🔨 Update Q1(c) w/ proof on af(n/b)<=cf(n) to concur with case 3 prereq.

@@
 We may rewrite it as $T(n) = T\Big(\frac{n}{\frac{1}{\lambda}}\Big) + n^{\lambda}$.
-Thus, we have a comparsion between $n^{\log_{\frac{1}{\lambda}} 1}$ and $n^{\lambda}$, which is equivalent as $n^0$ and $n^{\lambda}$, then we have $f(n) = \Omega(n^{\log_b a + \epsilon})$ for $\epsilon = \lambda$.
-We may also show $af(\frac{n}{b}) \leq cf(n)$ for $1 \cdot f\Big(\frac{n}{\frac{1}{\lambda}}\Big) = f(\lambda n)$.
-Combined, together, we can apply \textit{case 3} of the master theorem and conclude that the solution is $T(n) = \Theta(n^\lambda)$.
+Thus, we have a comparsion between $n^{\log_{\frac{1}{\lambda}} 1}$ and $n^{\lambda}$, which is equivalent as $n^0$ and $n^{\lambda}$, then we have $f(n) = \Omega(n^{\log_b a + \epsilon}) = \Omega(n^{0 + \epsilon})$ for $\epsilon = \lambda$.
+
+We may also show $af(\frac{n}{b}) \leq cf(n)$ for $c = \lambda^\lambda$; as $af(\frac{n}{b})  = 1 \cdot f\Big(\frac{n}{\frac{1}{\lambda}}\Big) = f(\lambda n) = (\lambda n)^{\lambda}$, where $(\lambda n)^{\lambda} \leq cf(n) =  \lambda^\lambda \cdot n^{\lambda}$.
+Combined the above two proofs together, we can apply \textit{case 3} of the master theorem and conclude that the solution is $T(n) = \Theta(n^\lambda)$.
 

### 2020-02-21 assignment_3/article.tex
💄 Fix language and expressions.

@@
 
-However, we cannot determine the expicit relationship between  $A[2], A[3], B[1], B[2], C[1]$, thus we conduct another experiment and add the top two candidates to the result list.
+However, we cannot determine the explicit relationship between  $A[2], A[3], B[1], B[2], C[1]$.
+Thus we conduct another experiment and add the top two candidates to the result list.
 This step shall cost one experiment and thus carries a $T(1)$ runtime.

### 2020-02-21 assignment_3/article.tex
✨ Add ref in Q4(a) about Python implementation of quick_miss on Gists.
🐛 Fix Q2(a) incorrect substitution on T((1 − α)(k + 1)) in equation 3.

@@
     &\leq [c \cdot \alpha (k + 1) \log(\alpha(k + 1)) - c'(k+1)] + \nonumber\\
-    & \ \ \ \ [c \cdot ((1- \alpha)(k + 1))\log((1-\alpha)(k + 1)) - c'(k+1)]+ d(k + 1) \nonumber \\
-    &\leq c \cdot \alpha (k + 1) \log(\alpha(k + 1)) + c(1-\alpha)(k + 1)\log(\alpha(k+1)) + d(k + 1) - 2c'(k+1) \nonumber \\
-    &\leq (c \alpha + c(k + 1) -  c \alpha) \cdot \log(\alpha(k + 1)) +  d(k + 1) - 2c'(k+1)\nonumber \\
-    &\leq c(k + 1) \cdot \log(\alpha(k + 1)) +  (d-2c')(k + 1)\nonumber \\
-    &\leq c(k + 1) \cdot \log(k + 1)+  (d-2c')(k + 1)\nonumber \\
-    \Longrightarrow T(k + 1) &\leq c(k + 1) \cdot \log(k + 1) \ \ \ \text{for $c'= \frac{1}{2}d$}
+    & \ \ \ \ [c \cdot ((1- \alpha)(k + 1))\log((1-\alpha)(k + 1)) - c'(1-\alpha)(k + 1)]+ d(k + 1) \nonumber \\
+    &\leq c \cdot \alpha (k + 1) \log(\alpha(k + 1)) + c(1-\alpha)(k + 1)\log(\alpha(k+1)) +\nonumber \\
+    & \ \ \ \  d(k + 1) - c'(k+1)- c'(1-\alpha)(k + 1) \nonumber \\
+    &\leq (c \alpha + c(k + 1) -  c \alpha) \cdot \log(\alpha(k + 1)) +  d(k + 1) -  c'(1-\alpha + 1)(k + 1)\nonumber \\
+    &\leq c(k + 1) \cdot \log(\alpha(k + 1)) +  (d-c'\alpha)(k + 1)\nonumber \\
+    &\leq c(k + 1) \cdot \log(k + 1)+  (d-c'\alpha)(k + 1)\nonumber \\
+    \Longrightarrow T(k + 1) &\leq c(k + 1) \cdot \log(k + 1) \ \ \ \text{for $c'= \frac{d}{\alpha}$}
 \end{align}
 
-As now we have $T(k + 1) \leq c(k + 1) \cdot \log(k + 1)$ for $c'= \frac{1}{2}d$, we may say it is true for $T(k)$ for all $k \in [1, n)$.
+As now we have $T(k + 1) \leq c(k + 1) \cdot \log(k + 1)$ for $c'= \frac{d}{\alpha}$, we may say it is true for $T(k)$ for all $k \in [1, n)$.
 \end{proof}
@@
 
+We also provide a runnable \ilc{Python} implenetation of the pseudo-code with real-time outputs. Please checkout
+\href{https://gist.github.com/choH/aa6ef8d549216ca1aa47a2aedab8dfa8}{\ilc{quick\_miss.py}} if needed.
+
 \subsubsection{(b)}

### 2020-02-21 assignment_3/article.tex
🐛 💄 Fix Q2(a) sign typo on induction W.T.S. (from = to <=).

@@
 We may rewrite it as $T(n) = T(\alpha n) + T((1-\alpha)n) + dn$ for $d \in \mathbb{Z^+}$.
-Assume the claim $T(k) = ck \log k - c'k$ holds true for $T(k)$ for $k \in [1, n)$, and without loss of generality assume that $\alpha \geq 0.5$, we have:
+Assume the claim $T(k) \leq ck \log k - c'k$ holds true for $T(k)$ for $k \in [1, n)$, and without loss of generality assume that $\alpha \geq 0.5$, we have:
 

### 2020-03-16 assignment_4/article.tex
🎉 Add placeholder .tex file for Assignment 4.

--- 2020-02-21 assignment_3/article.tex
@@
 
-\title{\textbf{EECS 340: Assignment 3}}
+\title{\textbf{EECS 340: Assignment 4}}
 
 \author{Shaochen (Henry) ZHONG, \ilc{sxz517} \\ Yuhui ZHANG, \ilc{yxz2052}}
-\date{Due and submitted on 02/20/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
+\date{Due and submitted on 03/19/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
 \maketitle
@@
 
-\section{(a) $T(n) = bT(n/a) + \Theta(n)$}
-
-For this recurrance, we have a comparsion between $n^{\log_a b}$ and $n$.
-Since it is given that $1 < a < b$, there must be $\log_a b > 1$.
-Therefore we may say that there must be a $n^\epsilon = \frac{n^{\log_a b}}{n}$ where $0 < \epsilon = \log_a b - 1$.
-
-Now we have $f(n) = n = O(n^{(\log_a b) - \epsilon})$, where $0 < \epsilon = \log_a b - 1$, we can apply \textit{case 1} of the master theorem and conclude that the solution is $T(n) = \Theta(n^{\log_a b})$.
-
-\section{(b) $T(n) = a^2 T(n/a) + \Theta(n^2)$}
-For this recurrance, we have a comparsion between $n^{\log_a a^2}$ and $n^2$, thus $n^2$ and $n^2$.
-As now we have $f(n) = \Theta(n^2)$, we can apply \textit{case 2} of the master theorem and conclude that the solution is $T(n) = \Theta(n \cdot \log n)$
-
-\section{(c) $T(n) = T(\lambda n) + n^{\lambda}$}
-
-We may rewrite it as $T(n) = T\Big(\frac{n}{\frac{1}{\lambda}}\Big) + n^{\lambda}$.
-Thus, we have a comparsion between $n^{\log_{\frac{1}{\lambda}} 1}$ and $n^{\lambda}$, which is equivalent as $n^0$ and $n^{\lambda}$, then we have $f(n) = \Omega(n^{\log_b a + \epsilon}) = \Omega(n^{0 + \epsilon})$ for $\epsilon = \lambda$.
-
-We may also show $af(\frac{n}{b}) \leq cf(n)$ for $c = \lambda^\lambda$; as $af(\frac{n}{b})  = 1 \cdot f\Big(\frac{n}{\frac{1}{\lambda}}\Big) = f(\lambda n) = (\lambda n)^{\lambda}$, where $(\lambda n)^{\lambda} \leq cf(n) =  \lambda^\lambda \cdot n^{\lambda}$.
-Combined the above two proofs together, we can apply \textit{case 3} of the master theorem and conclude that the solution is $T(n) = \Theta(n^\lambda)$.
-
-\section{(d) $T(n) = aT(\frac{n}{a}) + \Theta(n^{\lambda}(\log n)^b)$}
-For this recurrance, we have a comparsion between $n^{\log_a a}$ and $n^{\lambda}(\log n)^b$, which is equivalent to comparing $n$ and $n^{\lambda}(\log n)^b$.
-We may prove that $n$ is polynomially larger than $n^{\lambda}(\log n)^b$ by analyzing:
-
-\begin{align}
-    \text{W.T.S. \ }\lim_{n \to \infty} \frac{n^\epsilon \cdot n^\lambda (\log n)^b}{n} &= 0\\
-    \lim_{n \to \infty} \frac{n^\lambda (\log n)^b}{n^{1-\epsilon - \lambda}} &= 0 \nonumber\\
-    % \text{Since $n^x$ for any $x > 0$ grows much faster than anything with a base of $\log n$, we must have the following} \nonumber \\
-    \Longrightarrow 1-\epsilon - \lambda > 0 &\Rightarrow \epsilon < 1 - \lambda
-\end{align}
-
-Thus, we have $f(n) = O(n^{\log_b a - \epsilon})$ for $\epsilon < 1 - \lambda$. Then, we can apply \textit{case 1} of the master theorem and conclude that the solution is $T(n) = \Theta(n)$.
-
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 
-\subsection{(a) For any constant $0 < \alpha < 1$, if $T(n) = T(\alpha n) + T((1-\alpha)n) + \Theta(n)$, then $T(n) = O(n \log n)$}
-
-\paragraph{Guess $T(n) = O(n \log n)$\newline}
-Thus there must be constants $c, c'$ for $c, c'\in \mathbb{Z^+}$ s.t. $T(n) \leq cn \log n - c'n$.
-
-\paragraph{Given $T(n) = T(\alpha n) + T((1-\alpha)n) + \Theta(n)$\newline}
-\begin{proof}
-We may rewrite it as $T(n) = T(\alpha n) + T((1-\alpha)n) + dn$ for $d \in \mathbb{Z^+}$.
-Assume the claim $T(k) = ck \log k - c'k$ holds true for $T(k)$ for $k \in [1, n)$, and without loss of generality assume that $\alpha \geq 0.5$, we have:
-
-\begin{align}
-    T(k + 1) &= T(\alpha(k + 1)) + T((1-\alpha)(k+1)) + d(k + 1) \\
-    &\leq [c \cdot \alpha (k + 1) \log(\alpha(k + 1)) - c'(k+1)] + \nonumber\\
-    & \ \ \ \ [c \cdot ((1- \alpha)(k + 1))\log((1-\alpha)(k + 1)) - c'(k+1)]+ d(k + 1) \nonumber \\
-    &\leq c \cdot \alpha (k + 1) \log(\alpha(k + 1)) + c(1-\alpha)(k + 1)\log(\alpha(k+1)) + d(k + 1) - 2c'(k+1) \nonumber \\
-    &\leq (c \alpha + c(k + 1) -  c \alpha) \cdot \log(\alpha(k + 1)) +  d(k + 1) - 2c'(k+1)\nonumber \\
-    &\leq c(k + 1) \cdot \log(\alpha(k + 1)) +  (d-2c')(k + 1)\nonumber \\
-    &\leq c(k + 1) \cdot \log(k + 1)+  (d-2c')(k + 1)\nonumber \\
-    \Longrightarrow T(k + 1) &\leq c(k + 1) \cdot \log(k + 1) \ \ \ \text{for $c'= \frac{1}{2}d$}
-\end{align}
-
-As now we have $T(k + 1) \leq c(k + 1) \cdot \log(k + 1)$ for $c'= \frac{1}{2}d$, we may say it is true for $T(k)$ for all $k \in [1, n)$.
-\end{proof}
-
-\subsubsection{(b) For any constant $k > 0$, if $T(n) = \Theta(n) + \sum^{k}_{i = 1} T(\frac{n}{2^i})$, then $T(n) = O(n)$}
-
-\paragraph{Guess $T(n) = O(n \log n)$\newline}
-Thus, there must be a constant $c$ for $c \in \mathbb{Z^+}$ s.t. $T(n) \leq cn$.
-
-\paragraph{Given $T(n) = \Theta(n) + \sum^{k}_{i = 1} T(\frac{n}{2^i})$\newline}
-\begin{proof}
-As there must be a constant $d$ for $d \in \mathbb{Z^+}$ s.t.
-$\Theta(n) \leq dn$ -- and therefore causes $T(n) \leq dn + \sum^{k}_{i = 1} T(\frac{n}{2^i})$ -- with $d$ for $0 < d \leq c - \sum^{k}_{i = 1} c(\frac{1}{2^i})$.
-Now we may connect the two equations and get
-
-\begin{align}
-    T(n) &\leq dn + \sum^{k}_{i = 1} T(\frac{n}{2^i}) \leq cn \\
-    &\leq dn + \sum^{k}_{i = 1} c \cdot (\frac{n}{2^i}) \leq cn \nonumber
-\end{align}
-
-Assume the claim $T(n) \leq dn + \sum^{k}_{i = 1} T(\frac{n}{2^i}) \leq cn$ holds true for $T(m)$ for $m \in [1, n)$, consider:
-
-\begin{align}
-    T(m+1) &\leq d(m + 1) + \sum^{k}_{i = 1} T(\frac{m+1}{2^i}) \\
-    &\leq d(m + 1) + \sum^{k}_{i = 1} c \cdot (\frac{m+1}{2^i}) \nonumber \\
-    &\leq \underbrace{dm + \sum^{k}_{i = 1} c \cdot (\frac{m}{2^i})}_{= T(m) \leq cm} + \underbrace{d + \sum^{k}_{i = 1} c \cdot (\frac{1}{2^i})}_{= T(1) \leq c(1)} \\
-    \Longrightarrow T(m+1) &\leq c(m+1)
-\end{align}
-
-As now we have $T(m+1) \leq c(m+1)$ for $c \in \mathbb{Z^+}$, we may say it is true for $T(m)$ for all $m \in [1, n)$.
-\end{proof}
-
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 \section{Problem 3}
-
-% \begin{tikzpicture}
-%
-% \matrix [matrix of nodes,
-%          nodes = {draw,  minimum size = 2ex},
-%          column sep=1ex, row sep=1ex,
-%          row 1/.style={execute at begin cell= {|[label=\pgfmathparse{int(\the\pgfmatrixcurrentcolumn-1)}\pgfmathresult]|}}
-%          ]
-% {
-% 9 & 2 & 4 & 4 & 5   \\
-% 8 & 3 & 3 & 5 & 5   \\
-% 7 & 4 & 2 & 7 & 5   \\
-% 6 & 5 & 1 & 1 & 5   \\
-% 5 & 6 & 0 & 2 & 5   \\
-% };
-% \end{tikzpicture}
-
-\tikzset{
-mymat/.style={
-  matrix of math nodes,
-  text height=2.5ex,
-  text depth=0.75ex,
-  text width=3.25ex,
-  align=center,
-  column sep=-\pgflinewidth
-  },
-mymats/.style={
-  mymat,
-  nodes={draw,fill=#1}
-  }
-}
-
-\begin{tikzpicture}[>=latex]
-
-\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
-at (0,4.5)
-(mat1)
-{
-1 & 2 & 3 & 4 & 5\\
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
-at (0,3)
-(mat2)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
-at (0,2)
-(mat3)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
-at (0,1)
-(mat4)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
-at (0,0)
-(mat5)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat1,row 2/.style={nodes=draw}]
-at (4.5,4.5)
-(mat11)
-{
-1 & 2 & 3 & 4 & 5\\
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat2,row 1/.style={nodes=draw}]
-at (4.5,3)
-(mat22)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat3,row 1/.style={nodes=draw}]
-at (4.5,2)
-(mat33)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat4,row 1/.style={nodes=draw}]
-at (4.5,1)
-(mat44)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat5,row 1/.style={nodes=draw}]
-at (4.5,0)
-(mat55)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat11,row 2/.style={nodes=draw}]
-at (10,4.5)
-(mat111)
-{
-1 & 2 & 3 & 4 & 5\\
-M & X & X & > & ..\\
-};
-
-\matrix[mymat,right=of mat22,row 1/.style={nodes=draw}]
-at (10,3)
-(mat222)
-{
-X & X & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat33,row 1/.style={nodes=draw}]
-at (10,2)
-(mat333)
-{
-X & > & > & > & ..\\
-};
-
-%
-% \matrix[mymat,right=of mat44,row 1/.style={nodes=draw}]
-% at (10,1)
-% (mat444)
-% {
-% \geq & \geq & \geq & \geq & ..\\
-% };
-%
-% \matrix[mymat,right=of mat55,row 1/.style={nodes=draw}]
-% at (10,0)
-% (mat555)
-% {
-% \geq & \geq & \geq & \geq & ..\\
-% };
-
-\node[above=20pt of mat1]
-    (cella) {\textbf{Step 1:} $T(5)$};
-\node[above=0pt of mat1]
-    (cella) {$L[1] > L[2] > ... > L[5]$};
-
-\node[above=20pt of mat11]
-    (cella) {\textbf{Step 2:} $T(1)$};
-\node[above=0pt of mat11]
-    (cella) {$A[1] > B[1] > ... > E[1]$};
-
-\node[above=20pt of mat111]
-    (cella) {\textbf{Step 3:} $T(1)$};
-\node[above=0pt of mat111]
-    (cella) {Sort $A[2], A[3], B[1], B[2], C[1]$};
-
-\node[left=0pt of mat1]
-  (cella) {B};
-\node[left=0pt of mat2]
-  (cellb) {A};
-\node[left=0pt of mat3]
-  (cellb) {D};
-\node[left=0pt of mat4]
-  (cellb) {C};
-\node[left=0pt of mat5]
-  (cellb) {E};
-
-\node[left=0pt of mat11]
-(cella) {A};
-\node[left=0pt of mat22]
-(cellb) {B};
-\node[left=0pt of mat33]
-(cellb) {C};
-\node[left=0pt of mat44]
-(cellb) {D};
-\node[left=0pt of mat55]
-(cellb) {E};
-
-\node[left=0pt of mat111]
-(cella) {A};
-\node[left=0pt of mat222]
-(cellb) {B};
-\node[left=0pt of mat333]
-(cellb) {C};
-% \node[left=0pt of mat444]
-% (cellb) {D};
-% \node[left=0pt of mat555]
-% (cellb) {E};
-\end{tikzpicture}\newline
-
-\paragraph{Step 1: Divide\newline}
-Divide the 25 elements into groups of 5, and sort each group internally. By that we may have five sorted lists, we denote them as $A, B, C, D, E$, with the relationship of
-
-\begin{equation}
-    L[1] > L[2] > L[3] > L[4] > L[5] \label{eq:divide_group}
-\end{equation}
-
-for $L \in \{A, B, C, D, E\}$. This step shall cost five experiments and thus carries a $T(5)$ runtime, assuming each experiment will take $T(1)$ to conduct.
-
-\paragraph{Step 2: Sort front and find max candidate\newline}
-Sort the 5 groups according to their first elements, in the demonstrated case, we have
-\begin{equation}
-    A[1] > B[1] > C[1] > D[1] > E[1] \label{eq:sort_front}
-\end{equation}
-This step shall cost one experiment and thus carries a $T(1)$ runtime.
-
-According to \textit{Equation (\ref{eq:divide_group})} and \textit{Equation (\ref{eq:sort_front})}, we must have $A[1]$ being the material with maximum effectiveness amount all candidates.
-We may therefore add $A[1]$ into the result list.
-
-\paragraph{Step 2: Find rest two candidates\newline}
-
-According to \textit{Equation (\ref{eq:divide_group})} and \textit{Equation (\ref{eq:sort_front})}, we may safely claim the rest two candidates with top effetiveness must be among $A[2], A[3], B[1], B[2], C[1]$.
-Since it is known that $B[1] > C[1] > D[1] > E[1]$, we may discard $D[1], E[1]$ -- as there are always less effective in comparsion with $B[1], C[1]$ -- and therefore discarding group $D, E$, once again according to \textit{Equation (\ref{eq:divide_group})}.
-
-However, we cannot determine the explicit relationship between  $A[2], A[3], B[1], B[2], C[1]$.
-Thus we conduct another experiment and add the top two candidates to the result list.
-This step shall cost one experiment and thus carries a $T(1)$ runtime.
-
-\paragraph{Total Runtime}
-
-\begin{equation}
-    T_{\text{total}} = T(5) + T(1) + T(1) = T(7) \label{eq:q4_runtime}
-\end{equation}
-
-As \textit{Equation (\ref{eq:q4_runtime})} is a sum of runtime cost from each step, we may conclude that our algoritm has a runtime of $T(4)$.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\newpage
-\section{Problem 4}
-
-\subsubsection{(a)}\label{sec:4.a}
-
-\begin{algorithm}
-\caption{QuickMiss(C, D, p, r, missLeft)}\label{QuickMiss}
-    \begin{algorithmic}[1]
-        \Procedure{QuickMiss}{C, D, p, r, missLeft} \Comment{Set any value to $missLeft$ for initial call.}
-        \If {$p < r$} \Comment{Base case, terminates when $p = r$.}
-            \State $q \gets \textsc{Partition}(C, p, r)$ \Comment{Get pivot index from inclusive $C[p, r]$.}
-            \If {$C[q] == D[q]$} \Comment{If no missing element on left portion to $q$.}
-                \State \Return $\textsc{QuickMiss}(C, D, q+1, r, False)$ \Comment{Thus check right partition.}
-            \Else \Comment{If no missing element on right portion to $q$.}
-                \State \Return $\textsc{QuickMiss}(C, D, p, q-1, True)$ \Comment{Thus check left partition.}
-            \EndIf
-        \EndIf
-        \If {$missLeft == True$}
-            \State \Return $D[p]$ \Comment{Missing element index within range of $C$, simply return.}
-        \Else
-            \State \Return $D[r+1]$ \Comment{Missing element $> r$, $+1$ to retrive from $D$.}
-        \EndIf
-        \EndProcedure
-    \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{Partition(A, p, r)}\label{Partition}
-    \begin{algorithmic}[1]
-        \Procedure{Partition}{A, p, r}
-        \State $q \gets p$
-        \For {$i \gets p$ \textbf{to} $r$}
-            \If {$\textsc{Compare-Strings}(A[i], A[r])$} \Comment{if $A[i] < A[r]$ alphabetically.}
-                \State $\textsc{Swap}(A[i], A[q])$ \Comment{Exchange two elements.}
-                \State $q \gets q+1$
-            \EndIf
-        \EndFor
-        \State $\textsc{Swap}(A[q], A[r])$
-        \State \Return $q$
-        \EndProcedure
-    \end{algorithmic}
-\end{algorithm}
-
-\subsubsection{(b)}
-
-It is known that \textsc{QuickSort} has an average runtime of $\Theta(n\log n)$ due to the fact that it is considered \textit{case 2} of the master theorem: as it has $n$ nodes on each level and with a depth of $\log n$, thus $\Theta(n\log n)$.
-Our \textsc{QuickMiss} algorithm has a runtime of $\Theta(n)$ due to it only calls \textsc{Partition} on either left portion or right portion to the \ilc{pivot}, but never both (indicated in \ilc{line 4-7} of \textsc{QuickMiss}).
-Thus, on each level it will always have less than $n$ nodes, therefore forming a \textit{case 3} of the master theorem.
-The master theorem suggests, in \textit{case 3} the roots dominate the leaves and therefore determines the runtime of the algorithm -- as \textsc{QuickSort} has $n$ roots at the beginning, we may conclude it has a runtime of $\Theta(n)$.\newline
-
-To demonstrate it mathmatically, we have \textsc{QuickSort} being $T(n) = 2T(n/2) + \Theta(n)$ where  the leading $2T(n/2)$ indicates it will recursively handle both parts of the partition.
-Since \textsc{QuickMiss} only needs to handle one part, we have \textsc{QuickMiss} being $T(n) = T(n/2) + \Theta(n)$.
-This means we have a comparsion between $n^{\log_2 1}$ and $n$, which is equivalent to $n^0 \Rightarrow 1$ and $n$.
-Then we may have $f(n) = \Omega(n^{\log_2 1 + \epsilon}) = \Omega(n^{0 + \epsilon})$ for $\epsilon = 1$, and we may prove that $T(n) = \Theta(n)$ for \textsc{QuickMiss}.
 

### 2020-03-20 assignment_4/article.tex
✨ Add Problem 1 response.
Co-Authored-By: null <yuhuizhang0221@users.noreply.github.com>
✨ Add Problem 2 responses.
Co-Authored-By: null <yuhuizhang0221@users.noreply.github.com>
✨ Add Problem 3 sketch response (w/o comments).
🔨 Update Problem 3 with explanatory comments.

@@
 \setstretch{1}
+\usepackage[T1]{fontenc}
 \usepackage{amsmath,amssymb, amsthm}
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\linewidth]{{fig/fig_1.png}}
+    \caption{Decision Tree of \textsc{Quicksort}}
+    \label{fig:1}
+\end{figure}
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 \section{Problem 2}
+
+\subsection{Procedure \textsc{PreProcess}(A)}
+
+\begin{algorithm}[H]
+\caption{PreProcess(A)}\label{PreProcess}
+    \begin{algorithmic}[1]
+        \Procedure{PreProcess}{A, p, r}
+        \State \text{Let $C[0, 1, ..., k]$ be an arry of $0$.}
+        \For {$i \gets 0$ \textbf{to} $n$}
+            \State $C[A[i]] = C[A[i]] + 1$
+        \EndFor
+        \For {$j \gets 1$ \textbf{to} $k$}
+            \State $C[j] = C[j] + C[j-1]$
+        \EndFor
+        \State \Return $C$
+        \EndProcedure
+    \end{algorithmic}
+\end{algorithm}
+
+\subsection{Procedure \textsc{Query}(A, a, b)}
+
+\begin{algorithm}[H]
+\caption{Query(A, a, b)}\label{Query}
+    \begin{algorithmic}[1]
+        \Procedure{Query}{A, a, b}
+        \If {$a == 0$}
+            \State \Return $A[b]$
+        \Else
+            \State \Return $A[b] - A[a-1]$
+        \EndIf
+        \EndProcedure
+    \end{algorithmic}
+\end{algorithm}
 
@@
 
+This probably not the most reader-friendly pseudocode you'd see, but the idea behind it is very intuitive.
+Thus, I'd like to keep this design, and I'll give many comments to navigate you through my train-of-logic.
+
+\begin{algorithm}[H]
+\caption{Sparse-Transpose(R, C, V, m, n, k)}\label{transpose}
+    \begin{algorithmic}[1]
+        \Procedure{Sparse-Transpose}{A, a, b}
+        \State \text{Let $CH[0, 1, ..., n]$ be an arry of $0$.} \Comment{Value holder array.}
+        \State \text{Let $VH[0, 1, ..., n]$ be an arry of $0$.} \Comment{Column index holder array.}
+        \For {$i \gets 0$ \textbf{to} $n$}
+            \State $start \gets R[i]$ \Comment{Calculate the row index of element in C}
+            \State $end \gets R[i+1]-1$
+            \State \text{Let $CPR[\ ]$ be an empty array.}
+            \State \text{Let $VPR[\ ]$ be an empty array.}
+            \For {$j \gets start$ \textbf{to} $end$}
+                \State $CPR[i].append(C[j])$ \Comment{Holds column indexs according to their row index.}
+                \State $VPR[i].append(V[j])$ \Comment{Holds values according to their row index.}
+            \EndFor
+            \State $CH[i].append(CPR)$ \Comment{$CH[i]$ represents the column index of elements on i-th row.}
+            \State $VH[i].append(VPR)$ \Comment{$VH[i]$ represents the value of elements on i-th row.}
+        \EndFor
+        \State \text{Let $R'[\ ]$ be an empty array.}
+        \State \text{Let $C'[\ ]$ be an empty array.}
+        \State \text{Let $V'[\ ]$ be an empty array.}
+        \State $R'.append(0)$ \Comment{To fill-in the extra element as $len(R') = m + 1$.}
+        \State \text{Let $len\_max$ to be the max len of all elements in $CH$}. \Comment{Row with most elements.}
+        \For {$i \gets 0$ \textbf{to} $len\_max$}
+            \State $\textsc{Pop-Smallest}(R', C', V', CH, VH, len\_max)$ \Comment{Pop the original row index/value to $C'/V'$ of an element with smallest column index.}
+        \EndFor
+        \For {$i \gets 1$ \textbf{to} $n$}
+            \State $R'[i] = R'[i] + R'[i-1]$
+        \EndFor
+        \State \Return $R', C', V'$
+        \EndProcedure
+    \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[H]
+\caption{Pop-Smallest(R, C, V, CH, VH, len\_max)}\label{pop}
+    \begin{algorithmic}[1]
+        \Procedure{Pop-Smallest}{R, C, V, CH, VH, len\_max}
+        \State $min\_value \gets CH[0][0]$ \Comment{Assume 1st element on row 1 is the one with smallest column index.}
+        \State $min\_i \gets 0$
+        \State $min\_j \gets 0$
+        \For {$i \gets 0$ \textbf{to} $len\_max$} \Comment{Iterate all elements' column index on a particular row.}
+            \State $R\_counter \gets 0$ \Comment{Check if elements with same column index on multiple rows.}
+            \For {$j \gets 0$ \textbf{to} $n$} \Comment{Interate all rows registered in $CH$}
+                \If {$CH[j][i] == min\_value$} \Comment{If current element has the same column index}
+                    \State $R\_counter \gets R\_counter + 1$ \Comment{Update R'.}
+                    \If {$j < min\_j$} \Comment{If current element also has smaller row index than the holder.}
+                        \State $min\_value \gets CH[j][i]$ \Comment{Update holders.}
+                        \State $min\_i \gets i$
+                        \State $min\_j \gets j$
+                    \EndIf
+                \EndIf
+                \If {$CH[j][i] < min\_value$}  \Comment{If current elements column index is smaller than the holder.}
+                    \State $R\_counter \gets R\_counter + 1$
+                    \State $min\_value \gets CH[j][i]$ \Comment{Update holders.}
+                    \State $min\_i \gets i$
+                    \State $min\_j \gets j$
+                    \State \text{continue}
+                \EndIf
+
+            \EndFor
+            \State $CH[min\_j].remove(min\_i)$ \Comment{Pop the element with smallest column index.}
+            \State $C.append(min\_j)$ \Comment{Append element with smallest column index's row index.}
+            \State $V.append(VH[min\_j][min\_i])$ \Comment{Append element's corresponding value.}
+            \State $VH[min\_j].remove(min\_i)$ \Comment{Pop such value.}
+            \State $R.append(R\_counter)$ \Comment{Register how many elements on each column.}
+        \EndFor
+    \end{algorithmic}
+\end{algorithm}
+
+The algorithm is considered $O(m + n + k)$ as the \ilcode{line 4-6} in \textsc{Sparse-Transpose} needs $O(m)$, loop through of C, V needs $O(k)$, and loop through of $R'$ needs $O(n)$.
 % \section{References}

### 2020-04-07 assignment_5/article.tex
🎉 Add placeholder .tex file for Assignment 5.
✨ Add Problem 1(a) responses, except 1(a)(vi).

--- 2020-03-16 assignment_4/article.tex
@@
 
-\title{\textbf{EECS 340: Assignment 4}}
+\title{\textbf{EECS 340: Assignment 5}}
 
-\author{Shaochen (Henry) ZHONG, \ilc{sxz517} \\ Yuhui ZHANG, \ilc{yxz2052}}
-\date{Due and submitted on 03/19/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
+\author{Shaochen (Henry) ZHONG, \ilc{sxz517}}
+\date{Due and submitted on 04/06/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
 \maketitle
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(a)}
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\section{Problem 2}
+\paragraph{(i)}
+
+The last operation base on operator $o_{\text{last}}$ for $o_{\text{last}} \in \{o_1, o_2, o_3, ..., o_{n-1}\}$.
+
+\paragraph{(ii)} Assuming the last operation will be $T[i, j] \ o_{\text{last}} \ T[j+1, k] = T_{\text{final}}$, where $T_{\text{final}}$ provides the optimal output for $x_1 o_1 x_2 o_2 ...
+x_{n-1} o_{n-1} x_n$.
+There must be:
+
+\begin{itemize}
+    \item $T[i, j]$ provides the optimal output for $x_i o_i x_{i+1} o_{i+1} ... x_{j}$.
+    \item $T[j+1, k]$ provides the optimal output for $x_{j+1} o_{j+1} x_{j+2} o_{j+2} ... x_{k}$.
+\end{itemize}
+
+\begin{proof}
+    Without lost of generality, assume $T[i, j]$ is not optimal for $x_i o_i x_{i+1} o_{i+1} ...
+x_{j}$, there must be an $T'[i, j]$ where $T'[i, j] > T[i,j]$.
+Then we may have $T'[i, j] \ o_{\text{last}} \ T[j+1, k] > T_{\text{final}}$.
+\\
+    However, it is known that $T[i, j]$ provides the optimal output for $x_i o_i x_{i+1} o_{i+1} ...
+x_{j}$, for $T'[i, j] > T[i,j]$ to exist,  $T[i, j]$ is no longer optimal.
+Thus we may say $T[i, j]$ is optimal by contradiction.
+\end{proof}
+
+\paragraph{(iii)}
+
+\begin{itemize}
+    \item Subproblem: $T[i, j]$ for the optimal output of $x_i o_i x_{i+1} o_{i+1} ... x_{j}$.
+    \item Overall problem: $T[1, n]$ for the optimal output of $x_1 o_1 x_2 o_2 ... x_{n-1} o_{n-1} x_n$.
+\end{itemize}
+
+\paragraph{(iv)}
+
+\begin{equation}
+    T[i,k] =
+    \begin{cases}
+        x_i & \text{if \ } i = k \\
+        max\{T[i,j] \ o_j \ T[j+1, k]\} &\text{for \ } i \leq j \leq k \\
+    \end{cases}\nonumber
+\end{equation}
+
+\paragraph{(v)}
+
+We have $T(n) = \Theta(n^3)$.
+As there are $\Theta(n^2)$ subproblems and for each subproblem of $T[i,k]$, there are $\Theta(k-i)$ choices (which is essential $\Theta(n)$).
+Also each choice takes $\Theta(1)$ too execute.
+\\
+$\Longrightarrow T(n) =  \Theta(n^2) \cdot  \Theta(n) \cdot \Theta(1) =  \Theta(n^3)$
+
+\paragraph{(vi)}
+
+\begin{algorithm}[H]
+\caption{Largest-Output(T, n)}
+    \begin{algorithmic}[1]
+        \Procedure{Largest-Output}{T, n}
+        \For {$i \gets 1$ \textbf{to} $n$}
+        \EndFor
+    \end{algorithmic}
+\end{algorithm}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(b)}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(c)}
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\section{Problem 3}
+\section{Problem 2}
 

### 2020-04-07 assignment_5/article.tex
✨ Add Problem 1(b) responses.

@@
 
+I did \textbf{(ii)} and \textbf{(vi)} on \textbf{Problem 1(a)}.
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 
+\paragraph{(i)} Determine the last coin $c_{\text{last}}$ which will be added to the change set $\{c_1, c_2, c_3, ..., c_{\text{last}-1}\}$.
+Where the sum of elements of such set plus $c_{\text{last}}$ should be equal to $t$.
+
+\paragraph{(iii)}
+
+\begin{itemize}
+    \item Subproblem: $f(v)$ provides the minimum number of coins to make change for $v$, given $n$ types of coin denominations are available.
+There must be  $v \in [0, t]$ and $v$ must be equal to the sum of some coins from the given $n$ types of coin denominations, to represent a value that is achievable by given coins.
+    \item Overall problem: $f(t)$ provides the minimum number of coins to make change for $t$, given $n$ types of coin denominations are available.
+\end{itemize}
+
+\paragraph{(iv)}
+
+Let $n_c$ be a type of coin from the provided $n$ types of coins, which means $n_c$ can potentially hold $n$ types of values. We will try all $n_c$(s) as we don't know which coin to use for the $c_1$.
+
+\begin{equation}
+    f(v) =
+    \begin{cases}
+        0 & \text{if \ } v = 0 \\
+        min\{f(v - n_c) + 1\} & \text{if \ } v > 0 \\
+    \end{cases}\nonumber
+\end{equation}
+
+\paragraph{(v)}
+
+We have $T(n) = \Theta(nt)$.
+There are $\Theta(t)$ subproblems, as we can divide at most $t$ groups of coin(s) for a total value of $t$ (as for all coins being value $1$), and for each group there are at most $n$ possible choices to iterate (thus $\Theta(n)$).
+Each choice takes $\Theta(1)$ to execute.
+\\
+$\Longrightarrow T(n) =  \Theta(t) \cdot \Theta(n) \cdot \Theta(1) =  \Theta(nt)$
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

### 2020-04-07 assignment_5/article.tex
✨ Add Problem 1(c) responses.

@@
 
+\paragraph{(i)} Determine what edit to make (or not making any edit) when reached the last character of $X$.
+
+\paragraph{(iii)}
+Let $X_k = x_1x_2...x_k$ and likewise for $Y_k$.
+
+\begin{itemize}
+    \item Subproblem: $D(i, j)$ provides the shortest edit distance between $X_i$ and $Y_j$.
+    \item Overall problem: $D(m, n)$ provides the shortest edit distance between $X_m$ and $Y_n$.
+\end{itemize}
+
+\paragraph{(iv)}
+
+\begin{equation}
+    D(i, j) =
+    \begin{cases}
+        j & \text{if \ } i = 0 \\
+        i & \text{if \ } j = 0 \\
+        D(i-1, j-1) & \text{if \ } x_i = y_j \\
+        min\{D(i, j-1) + 1, D(i-1, j) + 1, D(i-1, j-1) + 1  \} & \text{otherwise}\\
+    \end{cases}\nonumber
+\end{equation}
+
+\paragraph{(v)}
+We have $T(n) = \Theta(mn)$.
+A matrix of $m \cdot n$ is filled when two strings are listing their possible reductions of chars, thus there are $\Theta(mn)$ subproblems.
+Each subproblem takes $\Theta(1)$ to execute.\\
+$\Longrightarrow T(n) =  \Theta(mn) \cdot \Theta(1) =  \Theta(mn)$
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

### 2020-04-07 assignment_5/article.tex
✨ Add Problem 2(a) response.

@@
 A matrix of $m \cdot n$ is filled when two strings are listing their possible reductions of chars, thus there are $\Theta(mn)$ subproblems.
-Each subproblem takes $\Theta(1)$ to execute.\\
+Each subproblem takes $\Theta(1)$ to execute as all edit options cost the same.\\
 $\Longrightarrow T(n) =  \Theta(mn) \cdot \Theta(1) =  \Theta(mn)$
@@
 \section{Problem 2}
+
+\subsection{(a)}
+\begin{proof}
+Suppose we have $r_{ij}$ for the optimal exchange between currencies $i \to j$, with an substructure of $r_{ij} = r_{ik} \cdot r_{kj}$ (for $k \in [i,j]$).
+We want to show both $r_{ik}$ and $r_{kj}$ must be the optimal exchange between currencies $i \to k$ and $k \to j$.
+
+Without lost of generality, assume we have $r'_{ik}$ where $r'_{ik} > r_{ik}$, then there must be $r'_{ik} \cdot r_{kj} > r_{ij}$.
+Which suggest $r_{ij}$ is no longer optimal for the exchange between currencies $i \to j$ and the assumption is void.
+Thus, we proved substructure $r_{ik}$ must be at its optimal structure by contradiction.
+And an optimal $r_{ij}$ is only obtainable with optimal substcutures.
+\end{proof}
 

### 2020-04-07 assignment_5/article.tex
✨ Add Problem 2(b) response.

@@
 
+\subsection{(b)}
+
+It is certainly possible.
+Assume the optimal exchange path found by the abovementioned procedure is a long path with a tiny amount of gain after each exchange, e.g., for $r_{az}$ we have to do $ r_{ab} \cdot r_{bc} \cdot ...
+\cdot r_{yz}$, where after each exchange the accumlated value become $1.0001$ times of before, and an direct exchange rate between currencies $a \to z$ is $1.0001$ as well.
+
+Supposely the best exchange path with no exchange fee is to do as many of positive exchanges as possible, as the accumlated values will only be larger and larger, result in a maximum amount of currency $z$ at the end.
+But if we set $f(k) = 0.5$ for all exchanges, the more exchange we do, the more money we lost -- since the tiny amount of gain of one exchange cannot cover the high exchange fee.
+In this case, the best exchange path would be a direct exchange between currencies $a \to z$ is $1$.
+
+Since the optimal exchange path with $f(k) = 0.5$ is not the same as the optimal path produced by the abovementioned procedure, we have proven the statement.
+
 % \section{References}

### 2020-04-19 assignment_6/article.tex
🎉 Add placeholder .tex file for Assignment 6.

--- 2020-02-21 assignment_3/article.tex
@@
 
-\title{\textbf{EECS 340: Assignment 3}}
+\title{\textbf{EECS 340: Assignment 6}}
 
 \author{Shaochen (Henry) ZHONG, \ilc{sxz517} \\ Yuhui ZHANG, \ilc{yxz2052}}
-\date{Due and submitted on 02/20/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
+\date{Due and submitted on 04/20/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
 \maketitle
@@
 
-\section{(a) $T(n) = bT(n/a) + \Theta(n)$}
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(a)}
 
-For this recurrance, we have a comparsion between $n^{\log_a b}$ and $n$.
-Since it is given that $1 < a < b$, there must be $\log_a b > 1$.
-Therefore we may say that there must be a $n^\epsilon = \frac{n^{\log_a b}}{n}$ where $0 < \epsilon = \log_a b - 1$.
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(b)}
 
-Now we have $f(n) = n = O(n^{(\log_a b) - \epsilon})$, where $0 < \epsilon = \log_a b - 1$, we can apply \textit{case 1} of the master theorem and conclude that the solution is $T(n) = \Theta(n^{\log_a b})$.
-
-\section{(b) $T(n) = a^2 T(n/a) + \Theta(n^2)$}
-For this recurrance, we have a comparsion between $n^{\log_a a^2}$ and $n^2$, thus $n^2$ and $n^2$.
-As now we have $f(n) = \Theta(n^2)$, we can apply \textit{case 2} of the master theorem and conclude that the solution is $T(n) = \Theta(n \cdot \log n)$
-
-\section{(c) $T(n) = T(\lambda n) + n^{\lambda}$}
-
-We may rewrite it as $T(n) = T\Big(\frac{n}{\frac{1}{\lambda}}\Big) + n^{\lambda}$.
-Thus, we have a comparsion between $n^{\log_{\frac{1}{\lambda}} 1}$ and $n^{\lambda}$, which is equivalent as $n^0$ and $n^{\lambda}$, then we have $f(n) = \Omega(n^{\log_b a + \epsilon}) = \Omega(n^{0 + \epsilon})$ for $\epsilon = \lambda$.
-
-We may also show $af(\frac{n}{b}) \leq cf(n)$ for $c = \lambda^\lambda$; as $af(\frac{n}{b})  = 1 \cdot f\Big(\frac{n}{\frac{1}{\lambda}}\Big) = f(\lambda n) = (\lambda n)^{\lambda}$, where $(\lambda n)^{\lambda} \leq cf(n) =  \lambda^\lambda \cdot n^{\lambda}$.
-Combined the above two proofs together, we can apply \textit{case 3} of the master theorem and conclude that the solution is $T(n) = \Theta(n^\lambda)$.
-
-\section{(d) $T(n) = aT(\frac{n}{a}) + \Theta(n^{\lambda}(\log n)^b)$}
-For this recurrance, we have a comparsion between $n^{\log_a a}$ and $n^{\lambda}(\log n)^b$, which is equivalent to comparing $n$ and $n^{\lambda}(\log n)^b$.
-We may prove that $n$ is polynomially larger than $n^{\lambda}(\log n)^b$ by analyzing:
-
-\begin{align}
-    \text{W.T.S. \ }\lim_{n \to \infty} \frac{n^\epsilon \cdot n^\lambda (\log n)^b}{n} &= 0\\
-    \lim_{n \to \infty} \frac{n^\lambda (\log n)^b}{n^{1-\epsilon - \lambda}} &= 0 \nonumber\\
-    % \text{Since $n^x$ for any $x > 0$ grows much faster than anything with a base of $\log n$, we must have the following} \nonumber \\
-    \Longrightarrow 1-\epsilon - \lambda > 0 &\Rightarrow \epsilon < 1 - \lambda
-\end{align}
-
-Thus, we have $f(n) = O(n^{\log_b a - \epsilon})$ for $\epsilon < 1 - \lambda$. Then, we can apply \textit{case 1} of the master theorem and conclude that the solution is $T(n) = \Theta(n)$.
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(c)}
 
@@
 
-% \begin{tikzpicture}
-%
-% \matrix [matrix of nodes,
-%          nodes = {draw,  minimum size = 2ex},
-%          column sep=1ex, row sep=1ex,
-%          row 1/.style={execute at begin cell= {|[label=\pgfmathparse{int(\the\pgfmatrixcurrentcolumn-1)}\pgfmathresult]|}}
-%          ]
-% {
-% 9 & 2 & 4 & 4 & 5   \\
-% 8 & 3 & 3 & 5 & 5   \\
-% 7 & 4 & 2 & 7 & 5   \\
-% 6 & 5 & 1 & 1 & 5   \\
-% 5 & 6 & 0 & 2 & 5   \\
-% };
-% \end{tikzpicture}
-
-\tikzset{
-mymat/.style={
-  matrix of math nodes,
-  text height=2.5ex,
-  text depth=0.75ex,
-  text width=3.25ex,
-  align=center,
-  column sep=-\pgflinewidth
-  },
-mymats/.style={
-  mymat,
-  nodes={draw,fill=#1}
-  }
-}
-
-\begin{tikzpicture}[>=latex]
-
-\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
-at (0,4.5)
-(mat1)
-{
-1 & 2 & 3 & 4 & 5\\
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
-at (0,3)
-(mat2)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
-at (0,2)
-(mat3)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
-at (0,1)
-(mat4)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
-at (0,0)
-(mat5)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat1,row 2/.style={nodes=draw}]
-at (4.5,4.5)
-(mat11)
-{
-1 & 2 & 3 & 4 & 5\\
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat2,row 1/.style={nodes=draw}]
-at (4.5,3)
-(mat22)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat3,row 1/.style={nodes=draw}]
-at (4.5,2)
-(mat33)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat4,row 1/.style={nodes=draw}]
-at (4.5,1)
-(mat44)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat5,row 1/.style={nodes=draw}]
-at (4.5,0)
-(mat55)
-{
-> & > & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat11,row 2/.style={nodes=draw}]
-at (10,4.5)
-(mat111)
-{
-1 & 2 & 3 & 4 & 5\\
-M & X & X & > & ..\\
-};
-
-\matrix[mymat,right=of mat22,row 1/.style={nodes=draw}]
-at (10,3)
-(mat222)
-{
-X & X & > & > & ..\\
-};
-
-\matrix[mymat,right=of mat33,row 1/.style={nodes=draw}]
-at (10,2)
-(mat333)
-{
-X & > & > & > & ..\\
-};
-
-%
-% \matrix[mymat,right=of mat44,row 1/.style={nodes=draw}]
-% at (10,1)
-% (mat444)
-% {
-% \geq & \geq & \geq & \geq & ..\\
-% };
-%
-% \matrix[mymat,right=of mat55,row 1/.style={nodes=draw}]
-% at (10,0)
-% (mat555)
-% {
-% \geq & \geq & \geq & \geq & ..\\
-% };
-
-\node[above=20pt of mat1]
-    (cella) {\textbf{Step 1:} $T(5)$};
-\node[above=0pt of mat1]
-    (cella) {$L[1] > L[2] > ... > L[5]$};
-
-\node[above=20pt of mat11]
-    (cella) {\textbf{Step 2:} $T(1)$};
-\node[above=0pt of mat11]
-    (cella) {$A[1] > B[1] > ... > E[1]$};
-
-\node[above=20pt of mat111]
-    (cella) {\textbf{Step 3:} $T(1)$};
-\node[above=0pt of mat111]
-    (cella) {Sort $A[2], A[3], B[1], B[2], C[1]$};
-
-\node[left=0pt of mat1]
-  (cella) {B};
-\node[left=0pt of mat2]
-  (cellb) {A};
-\node[left=0pt of mat3]
-  (cellb) {D};
-\node[left=0pt of mat4]
-  (cellb) {C};
-\node[left=0pt of mat5]
-  (cellb) {E};
-
-\node[left=0pt of mat11]
-(cella) {A};
-\node[left=0pt of mat22]
-(cellb) {B};
-\node[left=0pt of mat33]
-(cellb) {C};
-\node[left=0pt of mat44]
-(cellb) {D};
-\node[left=0pt of mat55]
-(cellb) {E};
-
-\node[left=0pt of mat111]
-(cella) {A};
-\node[left=0pt of mat222]
-(cellb) {B};
-\node[left=0pt of mat333]
-(cellb) {C};
-% \node[left=0pt of mat444]
-% (cellb) {D};
-% \node[left=0pt of mat555]
-% (cellb) {E};
-\end{tikzpicture}\newline
-
-\paragraph{Step 1: Divide\newline}
-Divide the 25 elements into groups of 5, and sort each group internally. By that we may have five sorted lists, we denote them as $A, B, C, D, E$, with the relationship of
-
-\begin{equation}
-    L[1] > L[2] > L[3] > L[4] > L[5] \label{eq:divide_group}
-\end{equation}
-
-for $L \in \{A, B, C, D, E\}$. This step shall cost five experiments and thus carries a $T(5)$ runtime, assuming each experiment will take $T(1)$ to conduct.
-
-\paragraph{Step 2: Sort front and find max candidate\newline}
-Sort the 5 groups according to their first elements, in the demonstrated case, we have
-\begin{equation}
-    A[1] > B[1] > C[1] > D[1] > E[1] \label{eq:sort_front}
-\end{equation}
-This step shall cost one experiment and thus carries a $T(1)$ runtime.
-
-According to \textit{Equation (\ref{eq:divide_group})} and \textit{Equation (\ref{eq:sort_front})}, we must have $A[1]$ being the material with maximum effectiveness amount all candidates.
-We may therefore add $A[1]$ into the result list.
-
-\paragraph{Step 2: Find rest two candidates\newline}
-
-According to \textit{Equation (\ref{eq:divide_group})} and \textit{Equation (\ref{eq:sort_front})}, we may safely claim the rest two candidates with top effetiveness must be among $A[2], A[3], B[1], B[2], C[1]$.
-Since it is known that $B[1] > C[1] > D[1] > E[1]$, we may discard $D[1], E[1]$ -- as there are always less effective in comparsion with $B[1], C[1]$ -- and therefore discarding group $D, E$, once again according to \textit{Equation (\ref{eq:divide_group})}.
-
-However, we cannot determine the explicit relationship between  $A[2], A[3], B[1], B[2], C[1]$.
-Thus we conduct another experiment and add the top two candidates to the result list.
-This step shall cost one experiment and thus carries a $T(1)$ runtime.
-
-\paragraph{Total Runtime}
-
-\begin{equation}
-    T_{\text{total}} = T(5) + T(1) + T(1) = T(7) \label{eq:q4_runtime}
-\end{equation}
-
-As \textit{Equation (\ref{eq:q4_runtime})} is a sum of runtime cost from each step, we may conclude that our algoritm has a runtime of $T(4)$.
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(a)}
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\newpage
-\section{Problem 4}
-
-\subsubsection{(a)}\label{sec:4.a}
-
-\begin{algorithm}
-\caption{QuickMiss(C, D, p, r, missLeft)}\label{QuickMiss}
-    \begin{algorithmic}[1]
-        \Procedure{QuickMiss}{C, D, p, r, missLeft} \Comment{Set any value to $missLeft$ for initial call.}
-        \If {$p < r$} \Comment{Base case, terminates when $p = r$.}
-            \State $q \gets \textsc{Partition}(C, p, r)$ \Comment{Get pivot index from inclusive $C[p, r]$.}
-            \If {$C[q] == D[q]$} \Comment{If no missing element on left portion to $q$.}
-                \State \Return $\textsc{QuickMiss}(C, D, q+1, r, False)$ \Comment{Thus check right partition.}
-            \Else \Comment{If no missing element on right portion to $q$.}
-                \State \Return $\textsc{QuickMiss}(C, D, p, q-1, True)$ \Comment{Thus check left partition.}
-            \EndIf
-        \EndIf
-        \If {$missLeft == True$}
-            \State \Return $D[p]$ \Comment{Missing element index within range of $C$, simply return.}
-        \Else
-            \State \Return $D[r+1]$ \Comment{Missing element $> r$, $+1$ to retrive from $D$.}
-        \EndIf
-        \EndProcedure
-    \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{Partition(A, p, r)}\label{Partition}
-    \begin{algorithmic}[1]
-        \Procedure{Partition}{A, p, r}
-        \State $q \gets p$
-        \For {$i \gets p$ \textbf{to} $r$}
-            \If {$\textsc{Compare-Strings}(A[i], A[r])$} \Comment{if $A[i] < A[r]$ alphabetically.}
-                \State $\textsc{Swap}(A[i], A[q])$ \Comment{Exchange two elements.}
-                \State $q \gets q+1$
-            \EndIf
-        \EndFor
-        \State $\textsc{Swap}(A[q], A[r])$
-        \State \Return $q$
-        \EndProcedure
-    \end{algorithmic}
-\end{algorithm}
-
-\subsubsection{(b)}
-
-It is known that \textsc{QuickSort} has an average runtime of $\Theta(n\log n)$ due to the fact that it is considered \textit{case 2} of the master theorem: as it has $n$ nodes on each level and with a depth of $\log n$, thus $\Theta(n\log n)$.
-Our \textsc{QuickMiss} algorithm has a runtime of $\Theta(n)$ due to it only calls \textsc{Partition} on either left portion or right portion to the \ilc{pivot}, but never both (indicated in \ilc{line 4-7} of \textsc{QuickMiss}).
-Thus, on each level it will always have less than $n$ nodes, therefore forming a \textit{case 3} of the master theorem.
-The master theorem suggests, in \textit{case 3} the roots dominate the leaves and therefore determines the runtime of the algorithm -- as \textsc{QuickSort} has $n$ roots at the beginning, we may conclude it has a runtime of $\Theta(n)$.\newline
-
-To demonstrate it mathmatically, we have \textsc{QuickSort} being $T(n) = 2T(n/2) + \Theta(n)$ where  the leading $2T(n/2)$ indicates it will recursively handle both parts of the partition.
-Since \textsc{QuickMiss} only needs to handle one part, we have \textsc{QuickMiss} being $T(n) = T(n/2) + \Theta(n)$.
-This means we have a comparsion between $n^{\log_2 1}$ and $n$, which is equivalent to $n^0 \Rightarrow 1$ and $n$.
-Then we may have $f(n) = \Omega(n^{\log_2 1 + \epsilon}) = \Omega(n^{0 + \epsilon})$ for $\epsilon = 1$, and we may prove that $T(n) = \Theta(n)$ for \textsc{QuickMiss}.
+\subsection{(b)}
 

### 2020-04-20 assignment_6/article.tex
✨ Add Problem 1 responses.
✨ Add Problem 3(a) response.

@@
 
+Hi Grader! Please note the boxes in following diagrams are merely provided for visualization purposes, they are not propertionaly graphed. Thanks.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 \subsection{(a)}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.4\linewidth]{{fig/fig_1_a.png}}
+    \label{fig:1_a}
+\end{figure}
+
+\begin{itemize}
+    \item Greedy Choice: \ilc{(a1)}
+    \item Optimal Choice: \ilc{(a2, a3)}
+\end{itemize}
 
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.4\linewidth]{{fig/fig_1_b.png}}
+    \label{fig:1_a}
+\end{figure}
+
+\begin{itemize}
+    \item Greedy Choice: \ilc{(a1)}
+    \item Optimal Choice: \ilc{(a2, a3)}
+\end{itemize}
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 \subsection{(c)}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.4\linewidth]{{fig/fig_1_c.png}}
+    \label{fig:1_a}
+\end{figure}
+
+\begin{itemize}
+    \item Greedy Choice: \ilc{(a1)}
+    \item Optimal Choice: Any combination between one of \ilc{\{a2, a4, a5, a6\}} and one of \ilc{\{a3, a7, a8, a9\}}.
+\end{itemize}
 
@@
 
+Assume we have a set of coins with value of $\{\$1, \$5, \$8\}$ and we are looking to exchange $n = 20$.\newline
+
+The greedy chioce will lead to a solution $\{2 \times \$8, 4 \times \$1\}$ for a totle of $6$ coins, however the optimal solution should be $\{4 \times \$5\}$ for total of $4$ coins.
+$4 < 6$ and thus disprove the greedy choice property.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

### 2020-04-20 assignment_6/article.tex
✨ Add Problem 3(b) response.

@@
 
+Assuming we have an optimal solution of $S = <x_o, x_1, x_2, ..., x_k>$, where each $x_i$ respectively represent the amount of $c_i$ coin in the avalivable coin denominations $\{c_1, c_2, ..., c_k\}$ for $1 \leq i \leq k$.
+
+We may observe that there must be $x_i < \frac{c_{i+1}}{c_i}$ for all $1 \leq i \leq k$; as otherwise we may have solution $S' = <x'_o, x'_1, x'_2, ..., x'_k>$ with $x'_i = x_i - \frac{c_{i+1}}{c_i}$ and $x'_{i+1} = x_{i+1} + 1$\footnote{This increment might have to be repeatedly done until the condition of $x_i < \frac{c_{i+1}}{c_i}$ is reached.}.
+Due to the fact that $\frac{c_{i+1}}{c_i}$ is at least $2$, $S'$ will be a more optimal solution than $S'$ and therefore voids the optimal assumption of $S$.
+Thus, the property of $x_i < \frac{c_{i+1}}{c_i}$ must be held in the optimal solution.
+
+Knowing this property, we may safely reach the optimal solution $S$ by keep greedily picking the coins with largest $c$ value possible ($c_{\text{max}} \leq n$).
+Since if we don't pick -- or don't pick the largest amount possible of -- $c_i$ coin(s) at one point, we will have to pick more $c_j$ coins after (for $1 \leq j < i \leq n$), and that will result in a less optimal solution.
+
 % \section{References}

### 2020-04-21 assignment_6/article.tex
✨ Add Problem 2 response.

@@
 
+\textbf{Greedy choice property}: In some optimal solutions, the activity with the earliest deadline is scheduled first.
+
+Let $S$ be an arbitrarily picked optimal solution, let event $E$ being the activity with the earlist deadline, let event $F$ being the firstly scheduled activity in $S$. We may have two cases:
+\begin{itemize}
+    \item $E$ is the same activity as $F$, then the property is proven.
+    \item $E$ is not the same activity as $F$, which means $F$ is scheduled ealier than $E$.
+Now we may form a solution $S'$ by swapping the order of $E$ with any activities scheduled before $E$, until $E$ swaps with $F$ (after such swap $E$ should be the firstly scheduled activity in $S$).
+\end{itemize}
+
+We may safely perform such swap(s) in the latter case due to the fact that such swap will have no effect on the \textit{maximum delay} time.
+For any activity $i$ to be scheduled, let $\Delta_i$ and $\Delta'_i$ represent its delay in solution $S$ and $S'$ respectively.
+The only case that we will have $\Delta'_i > \Delta_i$ is if activity $i$ is scheduled before $E$ in $S$ (thus after swaps, scheduled after $E$ in $S'$, and caused even more delay).
+In such scenario we may have:
+
+\begin{align*}
+    \Delta'_i &= \Delta_i + t_E = f_i - d_i + t_E \\
+    &\leq s_E + t_E - d_i \\
+    &= f_E - d_i \\
+    &\leq f_E - d_e = \Delta_E \\
+    &\Longrightarrow \ \Delta'_i \leq \Delta_E
+\end{align*}
+
+Since we know that the maximum delay in $S$ must be $\geq \Delta_E$ (for either $E$ causing the maximum delay or some other activity), and also since $\Delta'_i$ is calculated from arbitrarily picked $i$ in $S'$, we may conclude that the maximum delay in $S'$ will not be larger than the maximum delay in $S$.
+Consider $S$ is set to be optimal -- meaning its maximum maximum delay cannot get any shorter -- we must be $\Delta S'_{\text{max}} = \Delta S_{\text{max}}$; which means $S'$ is also optimal.
+And since $E$ is the firstly scheduled activity in $S'$, we have proven the greedy choice property to be valid.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

### 2020-04-21 assignment_6/article.tex
🔨 Update Problem 3(b) response with reader-friendly justification.

@@
 
-Assuming we have an optimal solution of $S = <x_o, x_1, x_2, ..., x_k>$, where each $x_i$ respectively represent the amount of $c_i$ coin in the avalivable coin denominations $\{c_1, c_2, ..., c_k\}$ for $1 \leq i \leq k$.
+Assuming we have an optimal solution of $S = <x_o, x_1, x_2, ..., x_k>$, where each $x_i$ respectively represent the amount of $c_i$ coin in the avalivable coin denominations $\{c_1, c_2, ..., c_k\}$ for $1 \leq i \leq k$.\newline
 
-We may observe that there must be $x_i < \frac{c_{i+1}}{c_i}$ for all $1 \leq i \leq k$; as otherwise we may have solution $S' = <x'_o, x'_1, x'_2, ..., x'_k>$ with $x'_i = x_i - \frac{c_{i+1}}{c_i}$ and $x'_{i+1} = x_{i+1} + 1$\footnote{This increment might have to be repeatedly done until the condition of $x_i < \frac{c_{i+1}}{c_i}$ is reached.}.
-Due to the fact that $\frac{c_{i+1}}{c_i}$ is at least $2$, $S'$ will be a more optimal solution than $S'$ and therefore voids the optimal assumption of $S$.
+We may observe that there must be $x_i < \frac{c_{i+1}}{c_i}$\footnote{I wrote it generally, but $\frac{c_{i+1}}{c_i}$ should be a constant $2$ in this problem.} for all $1 \leq i \leq k$; as otherwise we may have solution $S' = <x'_o, x'_1, x'_2, ..., x'_k>$ with $x'_i = x_i - \frac{c_{i+1}}{c_i}$ and $x'_{i+1} = x_{i+1} + 1$\footnote{This increment might have to be repeatedly done until the condition of $x_i < \frac{c_{i+1}}{c_i}$ is reached.}.
+Due to the fact that $\frac{c_{i+1}}{c_i}$ is at least $2$, $S'$ will be a more optimal solution than $S$ and therefore voids the optimal assumption of $S$.
 Thus, the property of $x_i < \frac{c_{i+1}}{c_i}$ must be held in the optimal solution.
+
+This means the optimal solution shall have as much as ``larger coins'' as possible, there will be no scenario that mutiple ``smaller coins'' can be added to a ``larger coin'' under an optimal solution.\newline
 
@@
 Since if we don't pick -- or don't pick the largest amount possible of -- $c_i$ coin(s) at one point, we will have to pick more $c_j$ coins after (for $1 \leq j < i \leq n$), and that will result in a less optimal solution.
+Thus, to achieve the optmal solution, we may just enforce the greedy choice at every step.
 

### 2020-04-27 assignment_7/article.tex
🎉 Add placeholder .tex file for assignment 7.

--- 2020-04-20 assignment_6/article.tex
@@
 
-\title{\textbf{EECS 340: Assignment 6}}
+\title{\textbf{EECS 340: Assignment 7}}
 
 \author{Shaochen (Henry) ZHONG, \ilc{sxz517} \\ Yuhui ZHANG, \ilc{yxz2052}}
-\date{Due and submitted on 04/20/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
+\date{Due and submitted on 04/27/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
 \maketitle
@@
 \section{Problem 1}
-
-Hi Grader! Please note the boxes in following diagrams are merely provided for visualization purposes, they are not propertionaly graphed. Thanks.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(a)}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.4\linewidth]{{fig/fig_1_a.png}}
-    \label{fig:1_a}
-\end{figure}
-
-\begin{itemize}
-    \item Greedy Choice: \ilc{(a1)}
-    \item Optimal Choice: \ilc{(a2, a3)}
-\end{itemize}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(b)}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.4\linewidth]{{fig/fig_1_b.png}}
-    \label{fig:1_a}
-\end{figure}
-
-\begin{itemize}
-    \item Greedy Choice: \ilc{(a1)}
-    \item Optimal Choice: \ilc{(a2, a3)}
-\end{itemize}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(c)}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.4\linewidth]{{fig/fig_1_c.png}}
-    \label{fig:1_a}
-\end{figure}
-
-\begin{itemize}
-    \item Greedy Choice: \ilc{(a1)}
-    \item Optimal Choice: Any combination between one of \ilc{\{a2, a4, a5, a6\}} and one of \ilc{\{a3, a7, a8, a9\}}.
-\end{itemize}
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\section{Problem 3}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(a)}
-
-Assume we have a set of coins with value of $\{\$1, \$5, \$8\}$ and we are looking to exchange $n = 20$.\newline
-
-The greedy chioce will lead to a solution $\{2 \times \$8, 4 \times \$1\}$ for a totle of $6$ coins, however the optimal solution should be $\{4 \times \$5\}$ for total of $4$ coins.
-$4 < 6$ and thus disprove the greedy choice property.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{(b)}
-
-Assuming we have an optimal solution of $S = <x_o, x_1, x_2, ..., x_k>$, where each $x_i$ respectively represent the amount of $c_i$ coin in the avalivable coin denominations $\{c_1, c_2, ..., c_k\}$ for $1 \leq i \leq k$.
-
-We may observe that there must be $x_i < \frac{c_{i+1}}{c_i}$ for all $1 \leq i \leq k$; as otherwise we may have solution $S' = <x'_o, x'_1, x'_2, ..., x'_k>$ with $x'_i = x_i - \frac{c_{i+1}}{c_i}$ and $x'_{i+1} = x_{i+1} + 1$\footnote{This increment might have to be repeatedly done until the condition of $x_i < \frac{c_{i+1}}{c_i}$ is reached.}.
-Due to the fact that $\frac{c_{i+1}}{c_i}$ is at least $2$, $S'$ will be a more optimal solution than $S'$ and therefore voids the optimal assumption of $S$.
-Thus, the property of $x_i < \frac{c_{i+1}}{c_i}$ must be held in the optimal solution.
-
-Knowing this property, we may safely reach the optimal solution $S$ by keep greedily picking the coins with largest $c$ value possible ($c_{\text{max}} \leq n$).
-Since if we don't pick -- or don't pick the largest amount possible of -- $c_i$ coin(s) at one point, we will have to pick more $c_j$ coins after (for $1 \leq j < i \leq n$), and that will result in a less optimal solution.
+\section{Problem 4}
 

### 2020-04-27 assignment_7/article.tex
✨ Add Problem 1(a) response.
✨ Add Problem 1(b) response.

@@
 
+\subsection{(a)}
+
+\begin{algorithm}[H]
+\caption{DFS(G)}
+    \begin{algorithmic}[1]
+        \Procedure{DFS}{G}
+        \For{each $u \in G.V$}:
+            \State $u.color$ = WHITE
+            \State $u.z$ = 0
+        \EndFor
+        \For{each $u \in G.V$}:
+            \If{$u.color$ == WHITE}
+                \State \textsc{DFS-Game-Visit(G, u)}
+            \EndIf
+        \EndFor
+    \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[H]
+\caption{DFS-Game-Visit(G, u)}
+    \begin{algorithmic}[1]
+        \Procedure{DFS-Game-Visit}{G, u}
+        \State $z = NULL$
+        \State $u.color$ = GRAY
+        \For{each $v \in Adj(u)$}:
+            \If{$v.color$ == WHITE}
+                \State $z = v.rank$
+                \State $z = \min(z, \textsc{DFS-Game-Visit(G, v)})$
+            \EndIf
+        \EndFor
+        \State $u.color$ = BLACK
+        \If{$z == NULL$}
+            \State $u.z = 0$
+            \State $z = u.rank$
+        \Else
+            \State $u.z = z$
+        \EndIf
+        \State \Return $z$
+    \end{algorithmic}
+\end{algorithm}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{(b)}
+
+\paragraph{Justification for runtime} The algorithm is $O(m+n)$ as DFS will first traverse every node, which means it will at least be $O(n)$.
+In addition, since the graph $G$ is implemented using adjacency list, for each node we will have to traverse through all its adjacent edges -- where such number can be at most $m$ (total number of edges in $G$) for a single node.
+Thus, the total time complexity is $O(m + n)$.
+
+\paragraph{Justification for correctness} The algorithm basically performs a DFS travesal on the graph $G$ and set the node \ilc{u} with smallest \ilc{rank} value as \ilc{z} to all of node \ilc{u}'s ancestor nodes.
+Due to the nature of DFS, node \ilc{u}'s ancestor nodes can legally have \ilc{u.rank} as their domination factor, as being \ilc{u}'s ancestors imply the fact these teams have won against team \ilc{u}.
+Also in \texsc{DFS-Game-Visit} we will not set a node's \ilc{.z} value unless such node is marked as \ilc{BLACK} (which means all of its decedents have been explored).
+Combine these two observations, each node has explored all of its decendents nodes, and the node's decendent node with the smallest \ilc{rank} will be assigned as all its ancestor nodes' \ilc{.z} value.
+The algorithm is a perfect mimic of the game logic of domination factor and guaranteed to be correct.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

### 2020-04-27 assignment_7/article.tex
🔨 Add graph G setup description for Problem 1(a).
✨ Add Problem 2(a) response.

@@
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \subsection{(a)}
+
+Set the each team as a node (vertex) in graph $G$ and make every node fully connected (representing the fact that all teams have played against each other).
+If one team $A$ beats another team $B$, we will have a directed edge of $A \rightarrow B$ betwen the nodes representing $A$ and $B$.
 
@@
 
+\subsection{(a)}
+
+Disprove with conterexample:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\linewidth]{{fig/fig_2_a.png}}
+\end{figure}
+
+Note the tuple below each node represents their \ilc{(start-time, finish-time)}.
+It is shown that $v.f > u.f$ as $6 > 4$, however there is no circle between $uv$.
+Thus, this conterexample disproves the statement.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

### 2020-04-28 assignment_7/article.tex
✨ Add Problem 2(b) response.
🔨 Add setup description for Problem 2.
✨ Add Henry's response to Problem 4.
✨ Add Yuhui's response to Problem 4.
🐛 Fix incorrect Problem 2(a) due to misread of uv being an edge.

@@
 
+Note the tuple below each node represents their \ilc{(start-time, finish-time)}.
+
 \subsection{(a)}
+
+Proof with cases:
+
+There are two possible cases where we can have a $v.f > u.f$:
+
+\begin{itemize}
+    \item Case 1: $v.d < u.d < u.f < v.f$\newline
+    In this case $u$ is a decent of $v$, which means there must be a path of $v \rightarrow u$; and known that we have $uv \in E$ (from the question instruction), this implies there is a direct connection of $u \rightarrow v$.
+Thus, now we have a path of $v \rightarrow u$ and a path of $u \rightarrow v$, $uv$ is guaranteed to be on a circle.
+    \item Case 2: $u.d < u.f < v.d < v.f$\newline
+    In this case we have $u$ completely discovered before $v$.
+This suggest there shoule be no relationship between $u$ and $v$, as $v$ should not be a decendent nor ancestor of $u$.
+However, it is known from the question that we have $uv \in E$, which implies $v$ must be a decendent of $u$.
+Thus, this case will not be valid under the question restriction and therefore disregarded.
+\end{itemize}
+
+As all legal case(s) shows $uv$ is guaranteed to be on a circle, we may prove the statement to be true.
+
+\subsection{(b)}
 
@@
     \centering
-    \includegraphics[width=0.6\linewidth]{{fig/fig_2_a.png}}
+    \includegraphics[width=0.35\linewidth]{{fig/fig_2_b.png}}
 \end{figure}
 
-Note the tuple below each node represents their \ilc{(start-time, finish-time)}.
-It is shown that $v.f > u.f$ as $6 > 4$, however there is no circle between $uv$.
+It is shown that there is a path from $v$ to $u$ as $v \rightarrow a \rightarrow u$, however $uv$ is still a cross edge as $v.d < v.f < u.d < u.f$ ($2 < 3 < 4 < 5$).
 Thus, this conterexample disproves the statement.
@@
 \section{Problem 4}
+
+\subsection{Shaochen (Henry) ZHONG's proof of course evalution}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.7\linewidth]{{fig/fig_4_a.png}}
+\end{figure}
+
+\subsection{Yuhui ZHANG's proof of course evalution}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.7\linewidth]{{fig/fig_4_b.png}}
+\end{figure}
 

### 2020-04-28 assignment_7/article.tex
🐛 🔨 Fix and update P1 to handle dominated team is BLACK when visited.

@@
 If one team $A$ beats another team $B$, we will have a directed edge of $A \rightarrow B$ betwen the nodes representing $A$ and $B$.
+A team's $z$ is set to be $\infty$ if such team has not won against any other team.
 
@@
             \State $u.color$ = WHITE
-            \State $u.z$ = 0
+            \State $u.z = NULL$
         \EndFor
@@
             \EndIf
+        \EndFor
+        \For{each $u \in G.V$}:
+            \State print $u.team, u.z$
         \EndFor
@@
                 \State $z = \min(z, \textsc{DFS-Game-Visit(G, v)})$
+            \Else
+                \State $z = \min(z, v.z)$
             \EndIf
@@
         \If{$z == NULL$}
-            \State $u.z = 0$
+            \State $u.z = \infty$
             \State $z = u.rank$
         \Else
+            \If{$u.z == NULL$}
                 \State $u.z = z$
+            \Else
+                \State $u.z = \min(u.z, z)$
+            \EndIf
         \EndIf
@@
 
-\paragraph{Justification for correctness} The algorithm basically performs a DFS travesal on the graph $G$ and set the node \ilc{u} with smallest \ilc{rank} value as \ilc{z} to all of node \ilc{u}'s ancestor nodes.
-Due to the nature of DFS, node \ilc{u}'s ancestor nodes can legally have \ilc{u.rank} as their domination factor, as being \ilc{u}'s ancestors imply the fact these teams have won against team \ilc{u}.
-Also in \texsc{DFS-Game-Visit} we will not set a node's \ilc{.z} value unless such node is marked as \ilc{BLACK} (which means all of its decedents have been explored).
-Combine these two observations, each node has explored all of its decendents nodes, and the node's decendent node with the smallest \ilc{rank} will be assigned as all its ancestor nodes' \ilc{.z} value.
-The algorithm is a perfect mimic of the game logic of domination factor and guaranteed to be correct.
+\paragraph{Justification for correctness} The algorithm basically performs a DFS travesal on the graph $G$ and set node \ilc{u} with the smallest \ilc{rank} value as \ilc{.z} to all of node \ilc{u}'s ancestor nodes.
+Due to the nature of DFS, node \ilc{u}'s ancestor nodes can legally have \ilc{u.rank} as their domination factor, as being \ilc{u}'s ancestors imply the fact that these teams have won against team \ilc{u}.
+Since the graph is implemented as $A$ beats $B$ being $A \rightarrow B$, after the DFS tavesal of a root, all nodes within this DFS tree is guaranteed to have the correct \ilc{.z} value, as all teams have been beaten by these nodes have been checked\footnote{Including \ilc{BLACK} nodes, as shown in \textsc{DFS-Game-Visit}'s \ilc{Line 8-9}: if a node is marked as \ilc{BLACK} it means this node's \ilc{.z} value is correct, so that nodes which are reachable to this \ilc{BLACK} node can simply take its \ilc{.z} value without go into the tree of the \ilc{BLACK} node any further}.
+\newline
+Also in \textsc{DFS-Game-Visit} we will not set a node's \ilc{.z} value unless such node is marked as \ilc{BLACK} (which means all of its decedents have been explored, and all of its reachable node -- regardless marked as \ilc{BLACK} or not, are taken into account).
+Combine these two observations, each node has explored all of its reachable nodes, and the node's reachable node \ilc{u} with the smallest \ilc{rank} value will be assigned as the \ilc{.z} value of all nodes which have reached node \ilc{u}.
+The algorithm is a perfect mimic of the game logic of domination factor and guaranteed to be correct.\newline
+
+To speak in a simple way, if we have a node $u$ where $u.rank$ should be the deminate factor of node $x$, we should either have $u$ being a direct decedents of $x$ and therefore promote $u.rank$ as $x.z$ during the DFS travesal from node $x$; or $u$ is explored (marked as \ilc{BLACK}) when $x$ is being traversed, in such case either $u$ or $u$'s ancestor $v$ (marked as \ilc{BLACK} as well) will have the $.z$ value of $u.rank$, and when the travesal of $x$ visits this $u$ or $v$, it will take $u.z$ or $v.z$ directly if it is smaller than its current $z$, and therefore not skiping any beaten team with the lowest \ilc{rank} value.
+As the algorithm works correctly in both scenarios, the algorithem is guaranteed to be correct.
 

### 2020-04-28 assignment_7/article.tex
🗑️ Remove Yuhui ZHANG's credit as finished individually.

@@
 
-\author{Shaochen (Henry) ZHONG, \ilc{sxz517} \\ Yuhui ZHANG, \ilc{yxz2052}}
+\author{Shaochen (Henry) ZHONG, \ilc{sxz517}}
 \date{Due and submitted on 04/27/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
@@
     In this case we have $u$ completely discovered before $v$.
-This suggest there shoule be no relationship between $u$ and $v$, as $v$ should not be a decendent nor ancestor of $u$.
+This suggests there shoule be no relationship between $u$ and $v$, as $v$ should not be a decendent nor ancestor of $u$.
 However, it is known from the question that we have $uv \in E$, which implies $v$ must be a decendent of $u$.
@@
 
-\subsection{Shaochen (Henry) ZHONG's proof of course evalution}
-
 \begin{figure}[H]
@@
     \includegraphics[width=0.7\linewidth]{{fig/fig_4_a.png}}
-\end{figure}
-
-\subsection{Yuhui ZHANG's proof of course evalution}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.7\linewidth]{{fig/fig_4_b.png}}
 \end{figure}

### 2020-04-28 assignment_7/article.tex
🔨 Add comments to P1(a) pseudocode.

@@
 \begin{algorithm}[H]
+\caption{DFS-Game-Visit(G, u)}
+    \begin{algorithmic}[1]
+        \Procedure{DFS-Game-Visit}{G, u}
+        \State $z = NULL$ \Comment{Potential $z$ value for this node, if not end of tree.}
+        \State $u.color$ = GRAY
+        \For{each $v \in Adj(u)$}:
+            \If{$v.color$ == WHITE}
+                \State $z = v.rank$ \Comment{If have decendent, set decedent's $rank$ as current's $z$.}
+                \State $z = \min(z, \textsc{DFS-Game-Visit(G, v)})$ \Comment{Find the lowest $z$ from all decendents.}
+            \Else
+                \State $z = \min(z, v.z)$ \Comment{Check if explored reachable nodes have lower $z$.}
+            \EndIf
+        \EndFor
+        \State $u.color$ = BLACK
+        \If{$z == NULL$} \Comment{If this node is end of tree.}
+            \State $u.z = \infty$ \Comment{Set $z$ to $\infty$ to indicate beats no one.}
+            \State $z = u.rank$ \Comment{For ancestor nodes to read its rank during recursion.}
+        \Else
+            \If{$u.z == NULL$}
+                \State $u.z = z$
+            \Else
+                \State $u.z = \min(u.z, z)$ \Comment{If node have been explored, check if the tree's $z$ is better.}
+            \EndIf
+        \EndIf
+        \State \Return $z$
+    \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[H]
 \caption{DFS(G)}
@@
         \For{each $u \in G.V$}:
-            \State print $u.team, u.z$
+            \State print $u.team, u.z$ \Comment{output all $z_i$.}
         \EndFor
-    \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[H]
-\caption{DFS-Game-Visit(G, u)}
-    \begin{algorithmic}[1]
-        \Procedure{DFS-Game-Visit}{G, u}
-        \State $z = NULL$
-        \State $u.color$ = GRAY
-        \For{each $v \in Adj(u)$}:
-            \If{$v.color$ == WHITE}
-                \State $z = v.rank$
-                \State $z = \min(z, \textsc{DFS-Game-Visit(G, v)})$
-            \Else
-                \State $z = \min(z, v.z)$
-            \EndIf
-        \EndFor
-        \State $u.color$ = BLACK
-        \If{$z == NULL$}
-            \State $u.z = \infty$
-            \State $z = u.rank$
-        \Else
-            \If{$u.z == NULL$}
-                \State $u.z = z$
-            \Else
-                \State $u.z = \min(u.z, z)$
-            \EndIf
-        \EndIf
-        \State \Return $z$
     \end{algorithmic}
